\documentclass[a4paper,12pt,titlepage]{book}
%\documentclass[a4paper,12pt,titlepage]{book}
%\documentclass[a5paper,10pt,titlepage]{book}
\usepackage{url}
\usepackage{eurosym}

\author{Third Edition\\\\by D.J. Barrow}  
\title{The Nerds Survival Guide}
\begin{document}
%\textit{\\}
%\pagebreak
\thispagestyle{empty}
\setcounter{page}{0}
\maketitle
%\textit{\\}
\pagebreak
%\vspace*{30pt}
\textit{\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\}
Published by: Aria Software Ireland Ltd., Scarra, Glantane, Mallow,
Co. Cork, Ireland.\\\\
Printed by: Diggory Press, Three Rivers, Minions, Liskeard, Cornwall, PL14 5LE,England
Copyright (c) 2006 D.J. Barrow\\\\
Cover image: The Majestic Sombrero Galaxy (Messier 104)\\(c) NASA and STScI.
\pagebreak
\paragraph
\noindent
\large \bf
Foreword
\normalsize
\paragraph
\noindent
The biography in this book is up close \& personal, it is that way
to help nerds in distress who may be going or will go through similar
problems that I did. It is also for people who want to understand nerds. 
Why do I think I am qualified to write ``The nerds survival guide'' ?,
well, as Oscar Wilde once said ``Experience is the name people give
to their mistakes'' \& as you'll find out I made many.
Some people may need to experience some of the pitfalls
I went through for themselves, it's part of growing up,
but the more cautious will learn without making the 
mistakes I made.
As a nerd I started young,
I've been programming in machine code since I was 15 \&
have been trying to buy women since I was 7.
After college I got a job as a computer games programmer
on the strength of programming knowledge I gained before
I went to college.
I worked in Apple Computers \& experienced the political
soap opera that is Apple, the place nerds work before
getting a real job, at least it was while I was there.
In IBM I worked on Linux for S/390 \& helped breathe life into
a mainframe, a computer dinosaur \& helped make it a roaring success.
I share the same hero as Bill Gates, Richard Feynman 
a Nobel Prize winning physicist who also wasted a
fortune on strippers who contributed in no small
part towards the invention of the atomic bomb.
As well as computers have a keen interest in
electronics \& quantum physics, I think I qualify.
\paragraph
\noindent
This book is as well as a biography is a means to spread 
my memes ( ideas which spread \& infect much like genes do )
 as Richard Dawkins writer of ``The selfish gene''
calls them. It also is a self help guide for nerds 
written to impart wisdom giving a 
atypical case study of how a nerd can end up in the psychiatric hospital,
if you are asking ``I am a nerd but how can this be relevant to me?'' 
a large percentage of nerds have breakdowns sooner or later \& do
end up in psychiatric hospitals, it's relevant.
It probably would be more popular if it was escapist fantasy,
I am not aiming at this audience.
I didn't become emotionally aware till after my breakdown
unlike women most nerds don't, it's a bit late.
The biography at the start of the book begins rather slowly so
bear with it. This book has turned out to be a bit of ``cri de coeur'' 
( cry of the heart ) a tragic comedy. What little misery
I had in my life was caused in large by my own stupidity \& self inflicted.
Most people in the world have a much harder life than I \& it
only takes a few minutes watching the news every night to
realize how lucky I actually am.
\paragraph
\noindent
Probably the section of the book of most interest to nerds is
the chapter ``Streetlife the only life I know'' this contains
all my hard earned experience on strippers that I learned
from the school of hard knocks.
If you are a psychiatric doctor or interested in quantum physics,
The chapter on 
``Consciousness, madness, science \& spirituality'', section
``Theory of consciousness determining reality''
is the most groundbreaking in the book \& definitely for you.
In this section using generally accepted theories \& principles
of quantum mechanics I provide what I feel is strong evidence that 
individuals going high or mad go into alternate realities rather than it being 
``all in the head'' as most psychiatric doctors would have you believe,
more interestingly it offers evidence that there is a heaven \&
that timetravel is a rare but normal occurrence.
The Science Bit gives a look at what I consider ``hot technologies''
which should become part of tomorrows World.
\paragraph
\noindent
The biography aside, most of the chapters 
in this book should be considered a short essays.
This book covers a diverse range of topics
\& not all of it will please everybody.
If you find a section of the book is not for you
don't drop the book, just give it a skip \&
move onto another topic that grabs your interest.
When you are finished reading it unless
you want to keep it for reference I would greatly
appreciate it if you would pass it on to somebody
else it may interest.
I personally don't like wasting peoples time,
thats why my writing style is compact \&
doesn't elaborate much.
\paragraph
\noindent
Along with this it gives a ``Men are from Mars Women are from Venus''
type account into the nerds psyche a very important insight for
women trying to understand nerds \& people suffering from mental
disorders. For a more complete \& sympathetic view on mental disorders
I strongly recommend Going Mad?.
It can be purchased from \url{http://www.amazon.com}.
\paragraph
\noindent
Feel free on emailing me back at \url{dj_barrow@ariasoft.ie}
with email subject nerds so I can filter the mail
with any thoughts you may have about what you read
so I can improve the book with your bias.
\paragraph
\noindent
Portions of this book are available at
\url{http://www.ariasoft.ie/ebooks.html} feel free to email them on.
I am planning that a portion of the profits of this book, 
if I make any, will be going to GOAL an Irish charity which aids Africa \& 
to Malteser a German charity which helps disaster victims.
\paragraph
\noindent
Dedicated to all my friends who helped me through life.
\tableofcontents
\chapter{Memoirs of madness}
\section{Beginning of the end}
\paragraph
\noindent
 It was April 2004 \& I was 35, in October 1998 I had left my home in Ireland \& had been working for IBM in Germany for most of 
the last 5 years. I no longer appreciated my fantastic job, apartment \& 
the party lifestyle I had in Stuttgart.
I was tired of running around the World chasing good jobs \& wanted
to turn my back on the World sit on my ass \& wait for it to come
back to me, this however wasn't happening, my sphere of influence,
my ability to distort my own reality wasn't strong enough,
I didn't learn to use the force, I simply wasn't good enough 
\& I was out of work as a result.
I was fed up, checkmated, in a cul de sac of life \& saw no way out.
The woman I most loved was marrying somebody else. 
I felt like a hamster on a wheel, going nowhere \& I wanted to get off,
in computer terms I had 
arrived serious irrecoverable situation, a Bus Error!,
It was reevaluation time,
I was spun out, traveling in ever decreasing circles. 
I was immature, self destructive \&
reckless, no longer able to appreciate the 
fantastic nonstop party my lifestyle afforded me, 
women aside I had it all \& I
was about to let all the good bits go, apartment,
enjoyable excellent paying job that I got 
too lazy to mind \& disenchanted with for no good reason, 
I was unglued \& well into 
mental breakdown territory \& about to pop.
\section{My family \& insights into nerddom}
\paragraph
\noindent
Life can be hard, nerds usually believe they have some incurable disease, they
think they are unfixable, in reality the only problem they have
is they need to accept themselves the way they are. 
God is wise if everybody dropped their
problems on the floor \& were asked to pick up somebody elses
problems odds on they would take their own back.
Most of Gods 10 commandments can be distilled to one Buddhist thought,
``find peace within yourself'', nerds you need to follow this advise.
Following ``the artists way'' if you write down your problems like 
I did for this book you will understand yourself better \& be
ones own counsellor,
it also might help to share them with people who need to
understand you. Almost nobody except nerds
understand nerds \& it is my goal in this book to correct this.
\paragraph
\noindent
My insecurities began when I was about 3 years old. My sister Margo, my
sibling rival was a year younger than me, she was real daddies girl,
excellent at dealing with people \& animals, I was the jealous
insecure type who found that at 14 that I had better 
relationships with computers that with people.
No man is an island, but for me sometimes it has felt that way.
My relationship with my brother James as we got older has
it's flaws as well, we don't fully understand each other.
From my perspective my brother James is secretive, fairly 
disorganized, sloppy \& leaves
a lot of stuff lying around the place \& doesn't repair farm
machinery unless it's absolutely necessary, but is very good with
animals \& children. Like my father my sister is excellent
with horses.
\paragraph
\noindent
My father in his youth knew how to work \& knew
how to party, he had no money, but had a talent for enjoying himself,
he used cycle to a lot of dances \&
has a lot of stories about them, my father basically
swept my mother off her feet on the dance floor.
My mother was a nurse before getting married 
\& like myself was a teeth grinding stressbucket.
People are always asking me to relax, I rarely succeed,
I suspect they asked my mother too,
it is very hard to relax when you think your life about to fall apart.
The movie I can most relate to in my early twenties was 
``Falling Down'' starring Michael Douglas I could see a
lot of characteristics of the main character in myself,
anyone interested in understanding mental
breakdowns should watch this movie, it doesn't hold back.
Part of the reason I am a stressbucket is that
I spend a lot of time in a world of my own,
I am absentminded \& have a bad memory.
I have fear of things getting out of control, especially financially.
Recently I thought I was in financial dire straits,
because I forgot about a large sum of money I had in my
company deposit account, the bank didn't send
me out statements \& I forgot about it.
\paragraph
\noindent
Like a lot of parents my mother told my sister from an early age that
she was going to be a star, a star by default?, my sister insists
that I am telling a whopper here but we agree to differ on our
memories of this situation. My sister spent a lot
of her twenties acting, in bands \& stiltwalking but
never quite made it \& being honest I never helped her even
when I could have, shame on me. Being a star is hard work \& demands
a lot of quality of effort which in my opinion my sister never put in, 
I was of the opinion she didn't realize she had to. Being a star also 
requires a lot of promotion there is management \& a marketing
department behind most stars.
A star like Elvis Presley was an immediately recognizable 
brand like McDonald's or Coca Cola,
he is over the top like Barney or the Teletubbies
a two year old can recognize Elvis Presley,
he also was a Karate expert \& extremely
fit this came across especially in his earlier
performances. As I found out writing a biography can
upset some of your family who value privacy, one could only imagine
what it must be like to be a celebrity \& constantly
under the glare of the media.
My sister currently makes a living from stiltwalking promoting
new discos \& the like. Margo currently in her available time
is completing her training to be a yoga teacher. Since having
children she has become certainly more grounded \& realistic
when it comes to her dreams than I am. My sister \& her boyfriend
\& children have great attitudes to life, he lives near the coast \& works
putting up large stages for bands \& spends about 3 days a week
surfing, I could learn a lot from him.
\paragraph
\noindent
My sister used smoke hash in her twenties, if you want to
waste a few years of your life hash is the way
to do it. The most annoying quality my sister
had in her teens \& twenty's was she was late
for everything \& kept people waiting, since having children she
has grown up a lot \& is a lot more selfless
than she once was.
The main piece of advise my mother gave to my sister
in anger which stuck with her was ``Never marry a farmer'',
my mother worked really hard on the farm,
my sister lived by this advise \& was being slave
to no man.
\paragraph
\noindent
Women love Danny Kaye \& Gene Kelly
because they don't have a care in the World, at least on film,
good with children, they don't let their troubles get them down,
they keep things in perspective, while some of these people
have easy lives the others who make it look easy probably cope well under
pressure, think well on their feet \& have plenty of tricks
up their sleeves, a nerd would probably let
his worries get on top of him \& children if they
happen to be around would probably be on the receiving end of this.
Under pressure some people focus, some people fold.
When with a woman you like don't bring your troubles with you,
if you are thinking about yourself you certainly aren't thinking
about the woman you are talking to \& it will show.
Women want somebody who is good with children, most nerds aren't.
Nerds have no time for baby talking to children, 
they believe kids learn nothing from it, maybe toddlers do,
nerds are quite poor at listening to people, especially babies.
I personally find it amazing how good mothers can get inside
the mind of a child to see whats wrong with them.
Women like protective men even if they are selfish \&
given to nepotism, they want a man who will look after their
children.
\paragraph
\noindent
Most nerds are individuals, loners, not necessarily that
they want to be loners, it's just that socializing doesn't
come easily to them, everybody wants to be popular,
however, not everybody is.
Nerds don't have much time for tribal team sports like soccer.
As a nerd I can appreciate the skill of George Best
or Pele but wouldn't sit down to watch 
a whole match. I would however go out of my way
to see Muhammad Ali fight or the Olympics
which basically consists of individuals competing.
The worst nerds of which I admit I am one are the
self absorbed whinger nerds who don't initiate 
a conversation by asking people ``how are you going'',
I hope to correct this.
My father when people call to the house talk a lot about who is related
to who \& the neighbours \& how they are getting on,
I don't, I wonder if this is a trait of 
less self absorbed people, non nerds.
\paragraph
\noindent
Women have far more talent than men when it comes to
accomplishing several tasks simultaneously, looking
after children, cooking, part time job.
Most men \& especially nerds are only only
able to juggle one ball at a time, with nerds
it is computer programming or some other scientific
endeavor \& they are extremely good at it, at the expense
of very basic things like personal hygiene.
People get more set in their ways as the get older,
nerds are very set in their ways to begin with,
this brittleness I would suspect is part of the reason
why nerds have so many breakdowns.
\section{The wonder years}
\paragraph
\noindent
One of my first memories was of my father buying me a
red pedal tractor when he was coming home from the
Dublin Horse Show in the RDS, he was disgusted when I showed far
more interest in the box it came in \& pulled my new box
around the yard absolutely delighted.
\paragraph
\noindent
I also remember getting ready for my first day at school,
I slept in my shirt \& tie so I wouldn't have to
put them on that morning.
Within a few months I was best friends with a guy who will
go for the remainder of this book by the pseudoname Patrick.
Patrick was excellent at Gaelic football \& was a pleasure
to watch weaving in \& out between players \& obstacles
in the national school playground.
By first class we were at a typical male obsession...
comparing the size of our willies.
James my brother was born when I was 7 he used to cry when
people complimented mam on the beautiful girl.
When James was 6 he had a similar obsession with his
balls \& wanted those appendages cut off,
he should be thankful I talked him out of the idea.
\paragraph
\noindent
My sister Margo was quite talented in a sado masochistic way,
once she got some
food dye, put it in water \& told
James she had some lovely lemonade for him.
He proceeded to drink some of the tasteless liquid,
she then told him it was piss.
Another time she made orange ice cubes with mustard
in the middle \& gave them again to James,
she had a glass of clear vinegar on the sink
which she knew James would go for once he chewed
into the icecube, she was bad!
\paragraph
\noindent
My brother James as a child had beautiful goldy locks of hair
\& as a result everybody complimented my mother on
the ``beautiful girl''. Among the first words my
brother learned were ``I am not a girl'' usually
accompanied by indignity \& tears.
When my brother was three he wasn't too fussy about
his diet, he once stripped a butterfly
of it's wings \& ate them.
\paragraph
\noindent
Margo also had a cat called Darkie which
had the habit of shitting under my bed.
Anyway this cat got flying lessons from me,
I threw it down the stairs, she sometimes
landed on her feet, sometimes not. I wrote a song about
``6 shits under the bed Darkie'', but forgot
most of the lyrics.
However bad the cat was I wasn't much better,
frequently while mam had visitors downstairs
I used piss out the window from my room upstairs.
My pee was clearly visible flying down from the
kitchen window below.
\paragraph
\noindent
At school I was a slow starter most people
were lightyears ahead of me.
Ciaran whom I met in St. Stephens could
do algebra at 3; I had problems with it at 14.
My cousin Margret could spell words larger than Cow at 4.
My cousin Anna at two \& a half was asking her
mother to explain the difference between today
\& tomorrow; a philosophical question;
At 5 I was a no hoper at elocution lessons.
My cousin Sarah was cheating at cards at 5.
\paragraph
\noindent
When I was 7 I had a severe tantrum our
workman whom for the rest of the book we will
call Michael at the time was on the receiving end of this,
being impatient Michael went ballistic
\& dragged me up \& down by the legs in the
garden through the nettles. I grew up about
3 years in 30 seconds, thanks.
Michael was a nazi boy racer who had swastikas
on the halogen lights in the front of his Mini Cooper
which he drove like a lunatic while listening to 
Foster \& Allen on his 8 track tape recorder.
\paragraph
\noindent
Another time I decided I tried to kill our
next door neighbour Mickey Bat with
a knitting needle, I ran at him, he
caught the needle \& bent it laughing.
I was disgusted \& ran home crying.
Mickey had a really hard life; his wife
\& son died when his wife was giving birth.
Another time Mickey hid behind the ditch \& threw
a bucket of water at Patrick \& I.
We were disgusted as we heard him laugh ``Haw,Haw,Haw''.
\paragraph
\noindent
By the time I was 8 years old I was obsessed
with making catapults \& crossbows \& drawing spaceships.
I quickly acquired walkie talkies at Chairamee Horse Fair
from tinkers ( Irish gypsies ).
I also got a telescope \& chemistry set I loved trying
to make stink bombs \& was largely successful
in this endeavor.
Now Patrick, myself \& Colm Murphy were ready to form 
KSP Killshannig secret police, Glantanes
answer to the A-Team. Needless to say
we didn't do much.
\paragraph
\noindent
At 10 I was obsessed with making jet engines
out of tin cans, who needs engineering skill
when you had a diagram in a World Book Encyclopedia
showing you a diagram of what the internals 
of a jet engine look like.
Patrick \& I learned all the statistics of the
space race convinced that by learning this we knew
all about science, we had a lot to learn.
Around this time Patrick got a highly intelligent
sheepdog called Brack, who could keep up with
Patrick on his racer going down a steep hill near
home, Patrick was faster than the hound but
only just, Patrick loved that dog.
I suspect he still cries about him.
\paragraph
\noindent
I have been trying to buy women since I was 7;
I tried to buy a pretty girlfriend with my Holy Communion money,
chasing strippers is the next logical progression.
My Karate trainer in Germany whom we will call Raimund
for the remainder of the book 
told me he would sell his girlfriend
for a good guitar, I personally would trade with him anytime,
Raimund is so fond of good handmade classical guitars
that he plays them so softly you would swear he was
afraid to hurt them, you meet plenty of weirdos in Karate.
Karate is great why anyone would play
a Karate computer game like Mortal Kombat
rather than doing it for real is beyond me.  
\paragraph
\noindent
As a child I loved fighting especially when I won; I bullied \& was
bullied, I remember chasing kids with a penknife
when I was 9. Another time when I was 10 I destroyed Majella
Murphy's dress by putting ink on her seat in class, I'm not exactly
proud of that.
When I was 10 I had a fight with Patrick he threw me
on the ground \& fractured my nose. I unfortunately
discovered a side of Patrick I didn't like. 
At that time of my accident,
his only concern was that I didn't tell the headmaster,
he felt no guilt, regret or compassion whatsoever,
he just wanted to save his own ass.
I was to hold this emotionally destructive grudge for a long time 
\& it eventually resulted in us parting as friends in later life.
\section{St. Colmans}
\paragraph
\noindent
St.Colmans boarding school most of the time was not a nice place; 
I was so stupid I volunteered to go there.
It was a place where parents locked up 300 problem
children for three weeks at a time, a place you got to see the
darker side of human nature.
When I was 13 I had a fight with a smaller guy than me,
Richard Tarrant, he quickly got me on the ground \& won
the fight; this loss made me wise up to myself that
I couldn't win all my fights \& I stopped doing it
until I discovered Karate.
\paragraph
\noindent
When I was 15 was where my life turned for the worse, 
I was kicked in the family Jewels by my cousin for calling him 
his nickname ``JEEWWEELLIIIAH!''; on hindsight I should have 
realized I was dealing with a loaded gun pointed at my own head,
I pulled the trigger on myself. I should have demonstrated more self 
control \& kept my mouth shut. Even his sister him
as being vicious as a teenager.I suppose my cousin must have 
had his own problems \& insecurities to make him so short tempered.
This I now believe provoked a varicoseal
( a varicose vein cured by a simple operation ) attached to my left testicle,
a little known
but a quite common ailment in men with tendencies towards varicose veins.
Both of my parents had varicose veins, what were they thinking when
they got married \& mixing up some bad genetics to make me?
It took me till I was 26 and 2 visits to STD clinics \& the humiliation of
being spotted by nosy cousins working there to figure out what
was wrong with me, had I somehow caught
an STD from handling animals at home on the farm?, I was too insecure to
point out my varicoseal to the people in the first clinic resulting
in the need for the second visit.
It took me till I was 26 to actually confirm that my problem was
related to my varicose veins which were starting to pop up at that time.
\paragraph
\noindent
I for a long time kept my problems bottled up, I was ashamed
of them, I had no reason to be, it wasn't my fault, everybody
has their own problems, I had problems which weren't talked
about in ``polite'' conversation, polite conversation is 
stifling, you are well advised to stay away from
pretentious gossips who make too much of it, it wasn't
till I saw that other people were brave enough to talk about
similar problems that the taboo was broken for me, I dealt
with my demons, it was time to get over it \& move on. 
Taboos are barriers to open mindedness.
Since I have overcome this taboo,
I now have a bit of a blind spot for talking about my problems,
it is inappropriate to talk about your problems in polite
company for political reasons there is no point in
headwrecking everybody, some people don't like it.
\paragraph
\noindent
Another of my insecurities was caused by neglect,
my mother had excellent teeth, she never
had to look after them.
My father lost all his teeth from an early age, an aunt who
was teaching him beat him \& knocked some of them out, 
the rest fell out or were pulled out later in life,
my mother never took into account that I had his genetics too.
Mam never got me to brush my teeth as a
child as a result I am missing about 8 molars,
they were removed by dentists, like most people
I hate dentists, one can't help but think their
motivation behind pulling teeth is to make people ugly,
they must be among the most hated people on the planet.
The only thing in my opinion dentists should do to
teeth is clean them.
\paragraph
\noindent
As a result of my fathers beatings in school he left
school early not properly able to read or write, he
like my brother James was slightly dyslexic.
My father a few years back mistakenly got a prescription from
the chemist for another James Barrow who lived nearby,
owing to this cock up at the chemist \& not
being able to read my father probably got
a few years taken off his life. The doctor on
examining the medicine took them quickly off my
father, he was afraid of being sued along with the chemist,
my father isn't an ambulance chaser.
I never liked the way my fathers doctor
feeds my father too much medication \& don't trust him.
Not learning to read can kill you.
\paragraph
\noindent
I don't believe in reincarnation in the traditional sense,
people I believe are reincarnated by sharing memes ( ideas ),
we are reincarnations of our parents, peers, role models,
people that inspire us, heroes \& people who have
similar life experiences to us.
I believe that there are only a small number of junctions 
in peoples life where decisions cause macroscopic life altering experiences.
Similar decisions made at these points may result in people having
similar experiences a partial reincarnation if you like,
history repeating itself.
I believe I had a similar reincarnation life experience to Adolf Hitler 
who probably got  a similar kick in the nuts from a Jew
( Jew sounds like Jewels \& Julia doesn't it ); it
is common knowledge he had problems with his testicles \& this could have
insighted a hatred in poor Adolf to want eradicate Jews from the face 
of the Earth.
\paragraph
\noindent
Around this time Patrick \& I were both extremely interested
in a girl whom for this story we will call
Suzanne who was at the time my sister's best looking friend.
When my sister was out we bugged her room.
This involved putting a microphone behind my sister's bed \& wires
under the carpet leading to a tape recorder in my room.
As suspected she spilled the beans talking to my sister,
it turned out that she was interested in Patrick.
I suppose Patrick was the better entertainer \& 
either had less or was better at dealing with
his insecurities than I was.
\section{Pleasing the opposite sex}
\paragraph
\noindent
Nerds, women love to be entertained, do what pleases
them not what pleases yourself, be selfless while
trying to entertain them, ask yourself would you sing a woman
a Celine Dion or Brian Adams love song to them if they wanted to hear one?
Did you ever give an ``all out'' effort to impress a lady or
were you always holding back because you don't believe the
lady in question deserves of your best, if she doesn't
deserve of your best she isn't worth chasing, is she?, if you give
of your best if you don't succeed with the lady in question
you may also impress other ladies who happen to be watching,
this has happened to me on one or two occasions,
the game might get interesting once jealousy \& female egos
get involved.
\paragraph
\noindent
Women want men with charm who will pounce
\& enjoy the challenge women create like a gladiator, one good
way to pounce is to serenade them while giving a tickle
attack or quietly singing something like Bryan Adams ``everything I
do I do it for you'' into their ear, it's over
the top \& most women love that. Women also love
a sharp dressed man, it's amazing the looks you get
when you are dressed to kill in a suit from women
normally way out of your league, it pays to be the flame
rather than the moth.
\paragraph
\noindent
With women you are familiar with the best icebreaker
is to gently invade her space go inside the 15 inch
barrier gently tap her on the shoulder \& ask a simple 
``how's it going'', listen \& once they respond
ask them ``why?'', they will usually be delighted with you
for being emphatic \& showing sensitivity.
Don't be jealous of another man doing 
stuff like this, try to learn from them.
\paragraph
\noindent
Another common mistake that men make
is that women often don't want fixer men to fix
their problems, they just want to be listened to,
get emotional support, encouragement \& deal with
the problem themselves, women like knowing that their
men acknowledge that a woman can fend for herself.
\paragraph
\noindent
Men sometimes go into their ``cave'' when they want to sort out problems
which cannot be sorted out by anyone other than themselves,
unless the woman is pretty sure she can help her man \& he
wants \& needs help at some level it is generally a bad idea to go 
into the ``cave'' after him, he might growl at her to get out.
\paragraph
\noindent
Men count points by the quantity \& size of the favour,
women usually count only 1 point per favour.
With women it's the little things that count, this has it's advantages
you don't have to be rich to please most women, remember anniversaries,
birthdays, mothers day etc \& be nice.
\paragraph
\noindent
Nerds judge people not by whether they can talk the talk but by
whether they can walk the walk. Women on the other hand unfortunately
judge men mostly by how they say things, if you do something
bad you can coat it velvet with your tongue, you will be regarded by women 
as a villain or a scoundrel but invariably be admired for being audacious,
in my view this is quite sad, thats how Clinton got away with the blowjob.
\section{The nerds beginners kit}
\paragraph
\noindent
In boarding school I first learned to program the Apple II a great machine
\& the Commodore 64 \& my most ambitious program at this time
was writing an interrupt driven music driver which played Axel F 
on the Commodore. I quickly became head of the computer room in Colmans.
When I was 14 I threw a big tantrum \& my mother give in \&
bought me the nerds beginners kit, a Sinclair Spectrum \& 
soon after I got an Amstrad CPC 464. I was a slow
starter on the computer John Rudden was away faster
but I caught up with him \& passed him out after 2 years.
Everybody has their own talents, the trouble is
finding them, some people I suspect spend their
whole life without finding theirs, thankfully I 
found mine at 14 \& have made a good living out of it.
Like anything, to get the best out of
a computer you have to love them \& give them plenty
of attention, if you don't they just fall apart.
\paragraph
\noindent
John changed schools to Davis College in Mallow \&
didn't thrive as well there as he did in Colmans
from an educational standpoint.
Another friend for the remainder of this book
lets call him Barry. Barry was very shy,
I will never forget the day we were walking around
the grounds in St. Colmans \& somebody coming down
the hill at full speed basically drove the front wheel
up Barry's arse, he fell to the ground quite hurt.
John \& I didn't feel as much sympathy as
we should have, when it comes down to it only saints aren't bastards,
the rest of us need to hammer respect into each other.
Barry also got quite good at computers
\& wrote a game of Frogger in machine code.
His brother lets call him Jack was the cocky member of the family
he was the best programmer I knew at the time \&
was able to do the Rubix Cube in around 30 seconds.
He went farming for 10 years after the Enter Cert
before going to college \& getting a Degree in Computers
from UL.
\paragraph
\noindent
At school one evening the group of us working in
the computer room decided it would be good if we could
arrange to doss study hours.
Our way to do this was to short a plug in the computer room in the hope
of blowing the main fusebox \& thus disabling all the lights in the
classrooms, all we succeeded in doing was blowing
the fuse which was connected to the seniors television set.
Needless to say we had to do a lot of fast talking to
prevent us getting the crap clattered out of us.
My other dossing activity was going into the music rooms
to listen to good pianists play during study hours, I loved doing this.
\paragraph
\noindent
The most influential cultural event for me at that
time definitely was Live Aid; I watched it at Patrick's house,
it was absolutely brilliant.
The most interesting bit of body language I saw at
Live8 was John McEnroe the tennis player jumping
out of his skin wanting to play air guitar from
the corner with Slash from Guns'n Roses while Slash
was playing his new band Velvet Revolver.
\section{University (or should I say universities)}
\paragraph
\noindent
After boarding school I went to NIHE in Limerick
allegedly to study electronic engineering.
Thanks to my mother arranging grinds with Bill Shannon
I got an Honour in Maths, this
got me into university. The prior Christmas I
scored 10\% in the honours maths exam.
However, owing to my immaturity \& my newfound freedom from
boarding school, excessively large classes in NIHE, none of the lecturers
got to know me or miss me when I didn't show up for
class. All I studied was video games \& drinking beer.
\paragraph
\noindent
My proudest boast from that time was
I once cycled home from a disco in the centre of Limerick
to the outskirts while drunk without putting my hands
on the handlebars of the bike. I got a new black \& gold racer while
in college \& like my cousin Dave when he was young, who spent half an hour
in the shower testing out his new waterproof jacket
I was over eager to try my new bike out. I cycled
50 miles home in the dark \& pissing rain with no lights on a main road
with a ruck sack and a ghetto blaster inside, what was I thinking?
I was definitely in danger of removing my genes from the gene pool
\& winning a Darwin Award ( \url{http://www.darwinawards.com} for more info
on this topic ).
Anyway the bike being an object of desire was quickly stolen.
\paragraph
\noindent
On another occasion I bought ``shit in a can'' \& ``fart spray'' from a joke
shop \& put it onto an overhead projector in the main lecture
hall in NIHE. The lecturer wasn't too taken with what
looked \& smelled like a cows afterbirth on the projector.
He proceeded in trying to spoon it off with a sheet of
A4 paper, gave up \& called the janitor,
we got a free lecture, I felt guilty
but proud of the experience.
\paragraph
\noindent
As a result of not concentrating on my studies I got kicked 
out of NIHE at the end of first year with a QCA of 1.17 
I needed 2.0 to stay in NIHE.
As well as my partying I did have a few weaknesses,
I wasn't great at Maths despite having a love of the
subject, I am slow to pick up abstract concepts.
I believe I did good in the digital electronics
exam but I only got a pass mark, I asked the lecturer
Dr. McQuaid to recheck it, I suspect he didn't, bastard.
Around this time my mother died of cancer, on the last
week she deteriorated very quickly I personally wasn't
expecting her to die when she did, she had strong faith
\& I suspect could have held on a lot longer if she had
fear of death.
Mum Cogan \& Lena took over the job of making us dinner,
thanks, Mum's plum pudding \& sherry trifle are amazing,
she makes great Christmas dinners.
From there went on to study in the Cork RTC
now known as CIT Cork Institute of Technology, 
there the lecturers
got to know all the personalities in the smaller classes. I was much
happier there \& eventually got my degree in electronic engineering.
My father was feeling a little lost without my mother
\& always was quite dependent on other people to
make dinner \& look after his bookwork, like most
people who get older he was set in his ways \& hoped
my sister would become the ``woman of the house''
my sister was having none of it \& went to work
in England, her most stressful job was working
in British Gas \& owing to the stress customers taking out
problems on my sister as if \& 
she was personally responsible for their problems \& general
bitchiness of other workers there she escaped the ratrace \&
it pretty much put her off work for a couple of years.
She did the hippy thing \& she went to India for 8 months.
\section {Tears Of Joy}
While in college Patrick \& I teamed up with
Aidan O Halloran from Newmarket a singer friend of my cousin
Dave Barrow, John  \& Paul
Rudden also joined up to play in our band ``tears of joy'' largely a U2 cover
band \& owing to the Ruddens influence in the band's direction.
John played drums while Paul played Bass \& Patrick played guitar
rather mediocrily.
\paragraph
\noindent 
I was the keyboard player \& had no sense of rhythm
whatsoever but was very good at getting a good sound out
of my keyboard setup, I personally was realistic \& had
no plans to go professional as a band as I knew I was better
in college, the Ruddens had other ideas however. 
After Patrick \& I left the band at their
peak had Ash play backing to them in Dublin \& played in a tent
in Feile in Thurles around the Summer of 94.
The band practiced every Sunday \& Patrick occasionally 
shifted his new girlfriend, for the remainder of this book
lets call her Mary, in my dad's car. I was extremely jealous of 
him as I found Mary very attractive \& flirtatious which was
an extreme headwreck for a nervous nerd like me.
\paragraph
\noindent
Around this time I asked Patrick's carpenter brother
to make a wooden flight case for my keyboards, I had 3
but I wanted room for 5 digital piano sized keyboards.
I made out the dimensions 50 inches by 35 inches by 25.
Patrick's brother told me this was absolutely huge, I didn't believe him.
Anyway he made the box, it was about the size of a piano
\& weighed in at around 40Kg. At that moment I learned
what the consultants most dangerous weapon was,
``Give the customer exactly what he asks for''.
\paragraph
\noindent
As anybody who ever played in a band
would testify ``practice is hell'' as this is where ego battles regarding 
the material being played \& the bands general direction happened \&
where the storms in a teacup arise.
Aidan being the singer had the biggest ego but wasn't a bitch,
he was easygoing.
Patrick didn't pull his weight in the band \& I had
to collect him every week in my father's car, Patrick often
wasn't ready \& we would arrive late to practice.
Playing on stage if a gig is going well is
far and away the best high you can ever experience,
well at least our single gig in the Hi-Land in Newmarket was. 
if you are a sadistic band member with a sense of humour start playing
bum notes on your instrument watch the rest of the band
wish the ground would swallow them up.
\paragraph
\noindent
As a band we were pretty bad but we won 750 pounds in a local talent
competition I think we were definitely the least talented
band which played. I think our rawness, enthusiasm 
owing to the fact we were jizzed up on adrenalin \& the fact we
were the local heroes won the competition for us.
Another interesting interaction which displayed my position as
a beta male in the group ( or at least the one between myself \& Patrick )
that I will never forget is playing the ``Summer of 69'' in Fitzpatrick's
Patrick kicked me in the ankle when he thought I went wrong,
Patrick was the one playing the bum notes.
Around the time I finished college I picked up guitar,
I still play that instrument occasionally.
\section{The sawdoctor}
\paragraph
\noindent
A few years after Patrick breaking up with Mary
I started calling to her house regularly \&
played piano \& guitar for her trying to impress her,
I knew I didn't play them well but I tried anyway. Mary pretended
to be impressed, but most likely wasn't; she had a boyfriend
with whom she didn't get on too well with \& it wrecked my
head why Mary didn't go for me instead.
``The thoughts \& dreams I had of her would take me six 
months in confession'' \& she knew it.
I prayed that I would be able to ``seduce
her in the future when she was feeling looser''.
After a few months of getting headwrecked dealing
with my own ego \& insecurities I gave Mary a tape of me
bawling my eyes out telling her what a bitch she was
for being a dangerous flirt, she I suspect
watched ``Dangerous Liaisons'' before I did, I had
a lot to learn in the love department, it was my first
minor breakdown \& the shape of things to come.
``I used to love her once long long time ago,
all my loving is gone, gone, gone, gone'', thanks be to God,
enough of that headwreck.
The Sawdoctors knew what they were talking about.
\paragraph
\noindent
Patrick was a firm believer in the shortcut \& not quality
of effort, at least when I really knew him,
we had a lot of storms in our teacups,
he was an intelligent risk taker \& very witty.
Patrick at that time was extremely lazy, he once 
stayed 52 hours in bed because he could.
Patrick was tight with money, a typical interaction which got on my tits was
one time Patrick passed a shop but couldn't be
arsed buying himself groceries,
when he saw me going towards
the shop he asked me to buy them for him \& gave
me the money, I didn't like being Patrick's gopher but
grudgingly agreed. I lost the change \& Patrick
insisted I pay 5 pounds for the privilege of
buying him groceries, it was the interactions
like these that left a sour aftertaste in my mouth.
\section{Employment history}
\paragraph
\noindent
1991 was a bad year to come out of college, 
there were almost no jobs.
My first job I found advertised on the radio, 
I was fired after 6 weeks in MSD Europe in Monaghan,
a business set up by a ex calculator salesman,
they thought I couldn't program thankfully I have
since proved them wrong.
\paragraph
\noindent
After a few months job hunting \& soul searching
I started programming in PCSL Software, 
or as the employees knew it Poxy Cheap Software Ltd..
around April of 1992 in Tallaght, Dublin.
I got my first job as a games programmer 
as a result of the games programming I did before I
went to university on my Amstrad CPC 464.
I really learned to program there from my boss.
My boss's only qualification was as a 
qualified plumber, gas welder \&
a complete nutcase, we were well matched.
While there I programmed my masterpiece,
Boozy the alcoholic horse, a sad reflection of myself,
a Super Mario type platform game supposed to
educate kids about the dangers of alcohol abuse.
Needless to say the managers wised up to themselves
\& didn't even bother marketing the game.
\paragraph
\noindent
Anton Wallace was the ``Aids Avenger'' game writer,
 yes another health education game, who knew my habits, one 
day as a prank when I went to the toilet inserted a bug in my code.
He knew I would go to the jacks again to relax, pee \& think about
what caused my bug \& while there he changed the code
back so I would be left for a few days looking for
a non existent bug.
Antons alcoholic father was a very arrogant
impatient electronic engineer but a good seducer,
he once dated Sinead O'Connors sister, I
suspect the bitches were well matched.
When he gave up alcohol he turned into a fitness
nut like me.
Anton once told me that his father had recently
lost half his fingers to frostbite climbing
some mountain in the Himalayas it took me
5 years to figure out he wasn't bs'ing when
he brought it up again.
Anton is a fierce charmer like
Gerry Ryan \& has some illogical fears
like extreme fear of heights, he won't cross
a bridge,
Anton plays lead guitar like Eddie Van Halen
but can't play Rhythm \& thinks that Joe Satriani
has poor articulation in his picking. He is a great cook
he learned from his mother who teaches home economics
\& a caring friend, thanks, awwwww.
\paragraph
\noindent
Most of Anton's family like my own are quite
self destructive, we get on like a house on fire.
When Anton got married his best man asked him
how long do you think this will last, it lasted
about 1 year, his wife one night refused him sex so
he decided to refuse her from then on.
Anton can be a bitch, he once broke it
off with a girlfriend his excuse was that
he missed masturbating.
Anton had another friend Gavan with whom
Anton stopped hanging around with because
Gavan was too rich for Anton's blood he
must be an almercyful bitch.
Anton \& my father as well as myself are
fond of the drink, probably Anton's worst
moment while drunk was falling down the
stairs backward while drunk, \& injured
his kidneys he got another glass of wine
to dull the pain, my fathers most humiliating
moment was falling asleep drunk in the bathroom
``on the throne'' with the bathroom door open
snoring, I wish I had a camera at the time. 
\paragraph
\noindent
The bosses in PCSL eventually figured out
that developing games based on quiz shows in
Germany was bad idea \& we moved on to
developing route planning software like Microsoft's
Autoroute. This route planning software was quite successful but not
successful enough to make a profit as we had
60 employees employed in entering map data.
Rather than boring you further with details
of my programming exploits my CV is located at
\url{http://www.ariasoft.ie/curriculumvitae.html}.
\paragraph
\noindent
From PCSL I moved on to Apple Computers in Cork,
the experience was pretty uneventful aside
from writing some good code, making a few good friends.
Apple is infamous for its soap operas
it is where people go before joining real companies
read Infinite Loop for more Details \url{http://www.amazon.com}
thankfully the company has got better over the last few years.
\paragraph
\noindent
While in Apple Patrick's wedding in Mexico happened,
I didn't like Patrick much at the time owing to
fallings out we had. I was determined
that Patrick's bad Karma was going to haunt him,
unfortunately my bad Karma 
for never forgiving him \& moving on in this
relationship was going to haunt me too,
I'm a stubborn edjit.
\paragraph
\noindent 
From Apple I moved to IBM in Boeblingen
to develop Linux for S/390 \& LinuxPPC as a contractor.
which was nothing short of brilliant \& I have
to thank the management there for giving me
such an opportunity.
The more interesting hacks we accomplished there were
getting Doom going \& Window 95 running on the PC Emulator Bochs
all running quite well on top of Linux for S/390.
Around August 2001 Patrick's father died,
Patrick had aged quite a bit since the last time I saw him,
when we met he was hacking down a hedge at home,
probably trying to vent frustration \&
because I recently replied to his a email telling him
how self absorbed he was becoming, he wasn't pleased to see me.
I suspect the stresses of Silicon Valley 
were getting to Patrick a bit, despite this
Patrick was the type of guy who would sing
the American national anthem for you.
I had no idea why he was so proud of America.
After the September 11th disaster Patrick sent a
message to just about everybody that he was okay,
he was around 3000 miles away from New York in Silicon Valley.
I suspect Patrick was unglued owing to his father's death \& fearing 
his own mortality, I was to say the least unemphatic,
Patrick in the past was often unemphatic to me too \& had
a nice habit of rubbing crap in, he was unforgiven \& I sent him a
scathing email telling him just what I thought
of his self absorption,
revenge for me at the time was irresistible,
Patrick had walked over me a lot through life,
this put the last few nails on the coffin of our friendship.
I have some shame about this, I should
have had more compassion for the recent loss of his father.
\paragraph
\noindent
I also had a 6 month stint in Galway developing
a firewall product for Asita Technologies aside
from drinking \& making good friends this was 
a pretty uneventful time. 
\chapter{Streetlife the only life I know}
What can I say most men like looking at pretty ladies,
my father is mad about them, so am I, suppose you 
can't beat breeding.
This chapter may challenge some peoples values.
If you are not interested in life on the wild side give
this chapter a skip.
\section{Generalizations about strippers}
\paragraph
\noindent
``I've been the wild rover for many a year \& I spent
all my money on whiskey n beer'' .... \& the ladies.
``I'm the type to kiss n' tell cos I've been seen with Farrah,
it's true I'll hire my body out for pay, wey hey'', 
enough of the singing, firstly the easiest way to get a strippers respect
you is to never go to a stripclub in the first place; 
that said this makes it very hard to meet them.
Contrary to popular belief strippers for the most part
don't bite, except at your wallet of course.
The easiest way to gain their disrespect is to
sit on the front row before the stage ``perverts row''
drooling at them while they are stripping.
Spending large amounts of money foolishly on them
will also put you into their ``sugar daddy'' box,
as soon as they consider you a serious source of income
it becomes quite difficult to earn their respect.
This ``Spongebob Squarepants'' made all these mistakes
chasing his black magic women,
self control \& moderation in spending money is key. 
\paragraph
\noindent
Contrary to popular belief strippers don't earn much
money, typically to buy them a drink costs the customer 
about \euro50 of this they get about 25\% of the price of
the drink into the hand ( about \euro12 ) 
the remainder goes to the drinks manufacturer, 
the club \& taxes, for this
they have to listen to a lot of shit talk from men
\& pretend they like it.
Some sillier clubs don't offer possibilities
of the girls making money by buying them drink.
Strippers usually get most of their takings from private
strip shows; as a result they usually are far more
likely to want to give a show to you rather than
sit down \& have a drink with you, even if the
drink is more expensive for you.
\paragraph
\noindent
Sometimes strippers boast about
the extremely good nights when they pull around
\euro600, but on average they only make around
as much as secretaries.
Some strippers allegedly get horny when you start
taking pictures with them \& acting hot yourself,
``Oh baby show us what you got, thats beautiful baby''
you get the idea, I have never tried this so I 
cannot confirm if it works.
The best nights to visit clubs is from
Monday to Wednesday, these are quiet nights
\& it may be easier to get time with your favourite
girls without much competition from other customers;
they have less reason to rush drinks to move onto the
next customer. Certain girls will only show up
Thursday to Saturday, the busiest nights \& 
some have other jobs for the rest of the week.
Strippers \& nerds are very similar in some ways \& in others 
completely different,  its a case of opposites attract.
Strippers like nerds are immature egomaniacs \& usually
have a self destructive streak \& sometimes abuse alcohol
\& occasionally drugs.
\paragraph
\noindent
If you are going to visit strip bars
regularly budget the amount of money you spend,
if you don't you will regret it later.
If you are paying by credit card find out the
name that will come up on your credit card bill,
if it is something discreet you can use the credit card.
If you are brave you might be able to legitimately claim
it as a company expense if you are entertaining somebody.
\paragraph
\noindent
Unlike nerds strippers are quite empathic \& can read people quite well
they are good talkers \& usually know about 6 languages;
computer programmers in contrast can speak about 6 computer
languages but have trouble with English.
Strippers are fierce flirts they make the chase interesting,
I usually get the crap scared out of me if a woman comes
on strong like I do, I think they must be barking mad,
I come on like a hungry wolf the women even strippers
usually eventually back off.
Strippers are freebirds quite irresponsible \& not punctual, 
if you manage to get their phone
number and arrange a date they will 90\% of the time be too lazy
or unreliable to turn up; 
if this happens don't lose control or abuse them you have noting to gain,
strippers hate immature men.
If you like them a much better bet is to go out for a meal
or a late night bar or restaurant after the show.
Strippers usually sleep till 5pm in the afternoon
\& spend hours washing their hair which is frequently
fake with extensions, filing their nails, going to
a sun studio to enhance their tan \& occasionally to the gym.
The thing which scares me most about strippers
is some of them have perfect bodies but want breast
enlargements, I personally cannot stand large breasts
especially fake ones which look like they are pumped up
to 300 PSI.
\paragraph
\noindent
At the club the girls are usually slow drinking their first drink,
if you buy them more drink easily they will usually take you as insecure,
easy money \& start drinking faster,
if you lose control this way they will usually disrespect you,
at this point stop buying drinks;
they won't suddenly start liking you for buying them more.
If you buy loads of drinks you probably expect something back,
the insecure male ego gets involved \& 
a storm in a teacup starts.
Respect yourself, don't buy a drink for a girl 
you don't really like or who doesn't really like you,
its a complete waste of money \& time, don't be a sucker.
\paragraph
\noindent
It's a common misconception that strippers are loose
they usually aren't if they were they wouldn't be
enough of a challenge to keep men interested.
The problem with loose women is if they let you up on them
they probably would let every other man up on them as well.
I personally don't go for prostitutes, they have too
much mileage on the clock. If you meet a lady you like
try to keep the conversation polite women hate rudeness.
Nothing will wreck a mans head as quickly as a good looking
girlfriend who is loose or a flirt.
\paragraph
\noindent
To the customer the owner of the club is a middleman
who takes a cut of what the girl gets of your money.
You may part with quite a lot of money but once
the club owner, drinks manufacturer \& the taxman
gets hold of it the girls get surprisingly little.
In a battle of loyalty between a customer \&
the club owner the club owner usually wins,
I'd suspect the girls are over a barrel \&
want to hold onto their jobs also unlike
the customer who parts with his money
like a fool the club owner commands respect. 
\paragraph
\noindent
Ladies, you got to be cruel to be kind, 
you may crave male attention but it may
be time to gain some self respect. If you aren't
making as much money as the other girls because
you aren't as talented a dancer or as pretty 
as the rest of the ladies in the club it may
be worth your while reevaluate \& consider a career move
\& leave the girls who are best at the job do it,
consider a career in sales, nursing or 
secretarial work.
\paragraph
\noindent
Guys there are better places than strip clubs
to go looking for pretty girls, namely Karate or
dancing classes. Most of the girls in the club
who want a boyfriend have one if not a few \& they are almost
never customers.
Some of the remainder of the girls
without boyfriends are lesbian,
think about it, if you were a lesbian the
place is Heaven, pretty girls taking off
their clothes all night \& putting on a free sexy
show for you.
\paragraph
\noindent
Sometimes the girls tell you their problems. For example
Nicki from Brno in the Czech Republic was a girl
I really liked \& was one of the very few to actually
show up for a date.
I learned a lot from her about herself \& myself,
hanging around with her was a lesson a minute.
She really enjoyed stripping for men because
she knew how to please them \& I was no exception. 
On the date, I got under the impression she thought
of me as a potential ``sugar daddy'' \& she was 
like some other strippers a bit of a gold digger.
I bought her lunch at a beautiful cafe in Breunninger
shopping centre in Stuttgart one of my seriously
happy places we watched a couple of very good classical musicians.
\paragraph
\noindent
She showed me pictures of herself her father \& her sister.
I got the feeling that she wanted my interest in her Sister,
she started getting impatient.
She frowned at me when I gave some money to a beggar,
I suspect she felt that I should be encouraging him
to work rather than begging.
She then used McDonald's as a free public loo a
use Ronald McDonald never envisaged.
She finished the date quickly I suspect when I didn't offer
to pay for a new jeans for her.
\paragraph
\noindent
Nicki's sister had a computer programming nerd as a boyfriend
\& was one herself.
Nicki didn't understand him, all he thought about was work.
To get to know what kind of man he was I suggested that she either
seduce him or pick a fight with him to find
out whether he would be unfaithful to her sister or would hit a lady.
Nicki worked part time in Dusseldorf
as some form of agent for entertainers.
She got fed up of me when I wouldn't let her take
off my shirt when she was stripping off.
This was really interesting for me as I was more
ashamed of getting overweight from drink than I was
of my varicoseal attached to my left testicle.
My greatest shame now was self inflicted. 
Eventually as with some other strippers I got
under the impression she was getting fed up with
me \& was only using me for money so I started
sending her texts that she was putting on weight
needless to say I gained nothing from my immaturity.  
\section{The places}
\paragraph
\noindent
I started going to stripbars shortly after I first arrived
in Germany in October 1998 I found flyers in local restaurants
\& couldn't resist the lure of the pretty ladies.
My four favourite stripbars in Stuttgart in order
are Winks, Macabu, Tahiti \& Moulin Rouge 
(apparently a franchise of the famous French Club in Paris.)
Most of the girls moved from club to club in Stuttgart
typically moving when they got fed up with their current environment.
\paragraph
\noindent
I was long way from home, welcome to my  PleasureDome,
Winks, definitely was the most chaotic of all the clubs, my voodoo lounge,
the preferred place for me to study my new hobby, stripper social dynamics.
I can only thank Andreas the crazy Greek waiter for making it so chaotic,
he was a serious headwrecker. Andreas had a way of dealing with immature
egomaniac strippers \& made sure that you learned a lesson a minute in there.
Ellen was the first girl I met in Winks, she was very honest for a stripper,
\& in a past life in the Netherlands was an amateur boxer, her mother
was divorced, she had a pretty hard life.
That night Lady Kim came on stage, Ellen wised me up to the show,
typically she would give some poor drunk German ``the crying game
experience'' Lady Kim was no lady but a chick with a dick.
After getting up close \& personal with a drunk customer Lady
Kim would drop his/her knickers the poor German caught on the night
would rush back to their seat headwrecked to sobriety in about
3 seconds. Another night an ``Elvis the pelvis'' character
went up on Stage with Lady Kim, he wasn't intimidated by the
climax of the show \& chased Lady Kim around the stage.
Another time his girlfriend an enthusiastic amateur stripper
did a show she wasn't too impressive the first night,
later that year she did another show it was obvious she had practiced,
professionals like Layla were jealous. 
I was told that Lady Kim was drunk she/it used to proposition
other girls backstage for sex.
\paragraph
\noindent
Another night a distinguished guest came in dressed in a suit
\& looked quite important I assumed he was the boss of some
large corporation later that night around 3am I saw him
dressed in a frilly negligee. I suppose when you have money
all kinky behavior is tolerated in these places.
Unusually enough lesbians \& straight girls used frequent the clubs,
\& there also were a few male strippers these usually were
ballet professionals from Russia \& to be honest put
on a damn good show.
\paragraph
\noindent
It was then I met Ebony, a highly intelligent level headed girl
originally from Surinam in South America who moved
to the Netherlands in later years, she was part Creole.
We became quickly became good friends, I used to love
singing with her, she had a fantastic voice, usually a duet doing 
Celine Dion songs Ivana a beautiful Polish girl used
love listening in at Tahiti \& it was obvious that the duet was taking
her to a happy place, my singing was absolutely
terrible but she used to love the performance. Beauty
is in the eye of the beholder.
Ivana was unusual, she was Polish, a heavy drinker, an animal lover 
\& typically was doing things like fixing birds broken wings, she practiced
a little witchcraft, loved
dancing, Shaina Twain \& Michael Jackson.
\paragraph
\noindent
One time my friend Fergal came over to visit me
in Germany to forget the stress he was under at work.
Fergal is impatient, I told him Tahiti was sometimes boring,
like mass, he didn't believe me, he lasted about
2 minutes in there before he wanted to go out.
\paragraph
\noindent
The most interesting time I ever had in Tahiti was
when the Celtic soccer fans came over from Scotland,
there was a queue of them outside the door.
All considered they were a fairly well behaved group
of noisy lager louts. The body language of the
strippers was amazing all the girls except the ones
from Thailand were terrified, they were well used
to men behaving badly at home, the girls dancing were taking small
intimidated steps on stage rather than bustling around
full of confidence. They were delighted to see me
I was the only ``Gentleman'' pervert in there. 
\paragraph
\noindent
Ebony was nice enough to frequently drop me down Tequila or Pils
from the bar. She later temporarily got a job as a barmaid in the
Monument, an excellent disco frequented by people from
the Baltic states the most memorable band that
used to play there was called Viagra obviously they
chose their name before the drug became popular.
\paragraph
\noindent
Ebony \& I often went to eat at Samson restaurant 
in Stuttgart city centre after the show
\& one evening went next door to Delilah, I was feeling sorry for
myself \& started crying, I think this self absorption
put her off, if a girl asks a nerd how they
are feeling always say ``Great'' because a girl realizes
that this is how much you are enjoying their company,
if you say you are feeling ``Crap'' this means you really
think their company is crap. 
I wasn't really attracted to many
black women... except Olympic sprinters, because
I am a racist pig, Ebony was excellent.
I fell out with Ebony after losing my job at IBM the
first time around December 2001, I lost this job
because I was spun out,
I was a insecure egomaniac edjit fed up of wasting my
hard earned money at Tahiti.
\paragraph
\noindent
Ebony told me an urban legend about one stripper in Winks who
had her privates pierced why anybody would do that is beyond me.
Anyway she used give a particularly aggressive performance on
the stripper pole however as soon as she went backstage
she usually was screaming in agony you can guess why.
\paragraph
\noindent
Anne Marie was the worst female headwrecker I ever met,
she was half Italian \& half Romanian, a dangerous combination.
Her father was an Italian Physicist \& she was studying law.
One night in winks at 3:30am I wasted around \euro200 in about
10 minutes buying her drink \& a tabledance.
Once a fool always a fool, I only behave rationally
when it is absolutely necessary.
She just put her thighs outside mine
\& squeezed my nuts, everybody else was going home \& I was waving
to them like an idiot ``weyhey'', I knew the stripshow was going to be good,
after about 10 seconds she went home herself, I left educated,
it was good. 
\paragraph
\noindent
A girl who shall remain nameless, for the remainder of this book
she will go by the pseudoname Anne, Anne was a stripper from Slovakia
I met in Macabu,
she was typically good natured  until you got on the wrong side of her
( more on that later ). She was easygoing \& didn't go out of her way to
rip off punters for as much money as she could get. I regularly gave her 
leg massages which she enjoyed, after a massage one day claimed she was
going to see a professional to get a much better one when she 
went back to Slovakia, this got on my tits hmmmppphh.
She loved playing games on her Playstation especially Crash Bandikoot,
I told her I was an ex games programmer \& this interested her.
\paragraph
\noindent
As we got to know each other better Anne told me that
she felt her dead fathers presence at several times \& felt that
he was looking after her.
As we got to know each other better Anne started telling me
more personal stuff. 
One day Anne told me about a pain in her neck, I guess this was a cue
for me to be sensitive, caring \& give her a neck massage,
at the time I wasn't going for it \& I suppose this pissed her off.
Another day Anne stripped for me I wasn't too impressed with the performance,
Like a typical nerd I showed her my phone hoping the games
would impress her, they didn't.
I asked Anne for her phone number, she wouldn't give it to me, I probably
didn't ask her nicely enough, from there we both started getting irrational
``a bonfire of the vanities'' was taking place. Anne was quickly
turning into Miss Piggy, she does exist, you don't want to cross her \& 
told me she wanted to look after endangered animals in Africa. 
I told her this was going against
nature \& to let it take its course \& I later suggested in a
letter that she look
after the pink elephants at home \& hoped I had a match made with my
brother James or my cousin Tom, the letter was thoughtless \&
she was having none of it.
My time came to a head with Miss Piggy when I slapped her on the face
in Champain night club \& she punched me on the nose with a powerful jab 
\& ripped my shirt, I went back to Macabu that night \& Esther
repaired the shirt with a paperclip I upset Anne
a lot but that wasn't stopping me from enjoying the rest of my night.
I now regret the fight with Anne, it was an act of desperation
while going mad, I was exploring boundaries I hadn't explored 
as a child, this is what eventually got me locked up.
\paragraph
\noindent
Esther was crazy gymnast from Basil who ran up a 1500 Euro
phone bill calling her MOMMEE, she loved her MOMMEE.
Esther looks surprisingly like a young Barbera Streisand but
cuter,
she had a dog which frequently ate her cigarettes in an attempt to
get her to give them up.
Esther could oversplit to 220 degrees \& stick out her tongue at the same time,
this impressed me no end, she headwrecked me one day by telling me that
she made love with a customer at random after her boyfriend
dumped her, why this customer wasn't me I will never know but
it made me very jealous, I would have rode her like a rampant rabbit.
I was engaged Esther twice ( at least thought I was ) when I was cracking up.
I gave the torn T-shirt Esther fixed as a present to the 
Anne with the words 
``Fuck me I'm Famous, I am MISS PIGGY'', more childishness,
I can only assume this upset her quite a lot, another regret.
I was high as a kite and possibly her dead father was getting really pissed
off with me from beyond the grave at this time more on that later.
Around this time I found the showcentre tahiti's website
\& the guestbook I did a brainfart dump on the website
with all the wisdoms I had accumulated through life for the girls,
along with moronic
taunts like ``Here piggy piggy piggy let me see your muppet puppet''
\& suggested that Ivana had an orgasm the last time she met me.
This was apparently upsetting the sysadmins
on the tahiti website \& it filled up again with baloney
about how beautiful all the girls were, I suspect that
most of the guestbook was rubbish made up by the sysadmins.
I was still trying to set up Anne with my brother
\& to get her to trust me I told her really personal
stuff in a letter from the frightened look I got
from Steve the D.J. \& the bouncer the next time I
went to Tahiti it was obvious they read the letter too,
they knew I lost the plot.
Esther on our alleged engagement was notably impressed by
my suggestion to have amorous adventures with me on a trampoline,
When high I told Esther I was a reincarnated Adolf Hitler,
she told me she was Jewish you can imagine what happened,
on hindsight I should have twigged it from the Jewish nose.
Being honest I am only a Hitler in so far as I am a duck walking
ranter but the damage was done.
\paragraph
\indent
Roxanne from Macabu also got my leg massages, 
Layla from Winks was a mad soprano singer, she sung 
three octaves too high \& who often came close breaking all the glasses 
in the club.
Layla hated the indignation of stripping but put on a strange 
but interesting show nonetheless, she looked like a Bond girl.
I still have a picture of her somewhere.
I will never forget when she did a headstand on a customers
lap it doesn't take much imagination to figure out where
her backside ended up.
These crazy Romanians, Layla \& Roxy led me to the theory that all Romanians 
women flip flopped between loving \&  hating men, 
they had lesbian tendencies while in hate mode.
I am of the opinion people may become gay if they get disenchanted
with the opposite sex, George Michael,
he had his choice of beautiful women \&
apparently got bored with them.
Roxy would always headwreck me by giving a terrible stripshow,
trying to make the best of these situations I occasionally tried to 
bite her ass unfortunately she had eyes on the back of
her head \& I kept missing. Roxy separated from her Romanian
husband at twenty one \& often worried that she might
have to become a prostitute eventually, I don't think she
will have to, she is very resourceful.
 It wasn't unusual for Roxy to
touch herself being in her ``happy place'' while watching other girls dance,
there are a lot of strange places in peoples heads \&
like Madonna the pop star Roxy knew all of them.
I frequently bought her perfume as presents, she bought me teddybears.
One of the funny place Roxy had in her head
was a serious shoe fetish \& I used give her
stripper dollars for the other girls which she folded
up neatly into bows \& put them neatly inside the
straps on other girls shoes delighted like a child.
I invited her once to Cannister Wasen the Stuttgart 
Octoberfest she disappointed me by not showing up. 
\paragraph
\indent
Tahiti was more expensive \& certainly was not as much fun
as Winks, the main Guy in Tahiti keeping the show on the road
was a nice but slightly dishonest conservative pervert who
had cameras behind the mirror in the mens toilets, Steve the D.J.
He spent a lot of time saving the vain girls in Tahiti
from themselves.
The most memorable girls in Tahiti were the two Veronicas
One of them was from the Czech Republic she really impressed me one
night by bending over backwards landing on one hand
\& coming up again, I spent a large part of that night
dancing with her \& showing off how fit I was
\& proceeded to do idiotic things
like a headstand against the wall \& singing Sinatra's
``Fly me to the moon'' while clicking my fingers \&
showing off on the stripper pole.
The other Veronica was from Poland
friendly but very dishonest, a small percentage of the Poles
regard Westerners like the Irish regarded
Yank tourists in the 70's, foolish with money
\& there to be exploited. Western European cars
in Poland are very likely to be stolen for parts
\& the Polish police will do noting about this,
``Westerners are suckers''. Veronica had a married
nearly identical twin sister who was married but replaced her occasionally
during a show to see what stripping was like needless
to say she didn't stay married long \& took up stripping too.
\paragraph
\indent
Macabu was a nice place with a terrible website
\url{http://www.macabu.de}
it would be well worth some nerds time
to fix it up,
the main lady in there was an ex
stripper herself Sybilla Ott, I really enjoyed that place
\& made good friends with her.
One of my strongest memories of Macabu was of a
the Diana 1998 German rhythmic gymnastic champion
originally from Lapland her father was a Truckdriver. She gave a
great show, she was gyrating wildly with her leg
at about 160 degrees against the wall \& I commented
``that must be really hard'' from there she put one leg
on the roof \& kept gyrating, D.J. was in his happy place.
I once was quite drunk \& had a fairly good table dance
from a girl from Hungary, I went in the following night
\& didn't recognize her face, I recognized her backside.
\paragraph
\indent
Moulin Rouge was run by a very nice lady who
had a son whom I reminded her of, she loved dogs.
My favourite girl there was of Katherina from Lithuania.
She reminded me of Patrick's ``tears of joy'' girlfriend 
whom I lusted after after \& I spent DM1500 in two nights
interfering with her in the corner.
She was very easygoing, good company \& loved her family
\& opera, I once met her in town \& she was kind
enough to join me for an informal date.
\paragraph
\indent
The nearest stripclub to home 
is ``The Great Escape'' I met a nice intelligent Polish girl
there called Lucia who recently
invited my Father in, I will bring him there someday
\& his ex nun girlfriend Chrissie, Chrissie can teach them
how to do proper Irish Dancing with the hands
down by their sides unlike Michael Flatley.
\section{Discovering myself from my dealings with strippers}
\paragraph
\noindent
Why does the opposite sex love bs artists?, is the
ability to lie a sign of intelligence, their quick wit,
entertainment value, the way the ego gets involved
when presented with a challenge, a tease, the
safety that one will become disenchanted once
the tease is over, the lack of guilt \& respect after
an interaction because the person involved
in the has been lying to you anyway,
find, f\$\%k, forget.
\paragraph
\noindent
Stripclubs are safe places to express sexuality.
If the women in stripclubs made strong sexual moves
on customers, it probably would go outside the comfort
zone of the customer \& in most cases the customer would back off.
Madonna for instance is kinky but safely so, she doesn't
cross the grotesque line, likewise for most strippers.
Stripclubs are rule governed there are things which are 
allowed \& not allowed. For seriously demented men stripclubs
are selling hope, it's the wrong place to look for women.
As my brother says ``nearly all mens problems can be
traced back to womens arses'', Helen of Troy, the list goes
on \& on, I am no exception to this rule.
My insecure ego was heavily involved with strippers \&
it took me a long time to see clearly see the reality 
that strippers are mostly players or actors, it is their job to satisfy
the fantasies of their customers, for the most part they
have very little emotional involvement with them;
it is not in their interest to gain any, it would mess up their work.
Some strippers are unfortunately liars. For customers it isn't
worth their while to let their egos get involved
in the headwrecking games being played at stripjoints, all women disrespect men
who are not in control \& if you are wasting \euro500 a night
in these kinds of places you are immature \& insecure, you are not in control.
\paragraph
\noindent
Behaving like a jealous hungry wolf unable
to handle other male competition is offputting to women
\& is probably why I was getting nowhere with strippers.
Women love men with self control, however, it is easy
to have self control when you don't want something.
It probably would have been cheaper for me to open my
own strip club \& be the only customer than pump a fortune
into other peoples clubs.
Men often lust after women whom they cannot stand as people,
they want a trophy, satisfy lustful urges,
what happens if there are children? the ego is a dangerous thing.
People don't fall in love with other people they
fall in love with their idealized idea of whom the person is,
so even falling in love is dangerous.
On the few occasions women showed interest back I got
scared \& thought they must be at least as messed
up in the head as I was to want me \& backed off.
Nerds like myself have high ambitions like
winning a Nobel Prize, we don't want to
admit we are ordinary, when we get old we
are old, ordinary \& vain. I had a lot
of growing up to do in the psychiatric hospital.
Maybe I am not ready for a proper relationship.
It is hard not to have a few negative emotions
towards the owners \& bouncers in some clubs,
some can be really ignorant.
\paragraph
\noindent
Like Spongebob Squarepants I lack self control \& am for the most 
part utterly useless with dealing with women who are not related to me.
For instance around early 2000 I met Suzanne my sisters friend
one evening in Chapel Lane the local disco at home,
I was arrogant, I now believed I had better possibilities for women,
my strippers \& acted uninterested, what an deluded asshole I'd become.
I also couldn't understand why women wouldn't do exactly what I wanted,
I could always get a computer to do what I wanted if I asked it
correctly, why weren't women more like computers?, 
I had seen my strippers, I paid for them, 
like Catherine from Macabu run away into bed with guys she met 
in the local gym. In fairness to Catherine she was nice enough
to buy me a Tequila the one night she met me in Perkins Park. 
From this I decided to change from beer to wine \& 3 hours exercise a day 
was the way to go to beat the damn gym posers at their own game.
I hate posers yet I lust after them \& I became one,
all the exercise I did make me lean n'mean unfortunately ate into 
my work hours, I sure as hell wasn't going to let it
affect my insomniac party lifestyle. I was clocking 
80 hours a month at work as opposed to previously usual 160.
I ignored the danger signs that I wasn't pleasing my current boss. 
\paragraph
\noindent
Like Richard Feynman the physicist, my Nobel Prize winning hero
\& the programmers who started Apple Computers who used to go down to 
the Pink Poodle strip club for dinner, I love my strippers.
I have been made jealous, envious, headwrecked \& entertained into 
wasting a fortune over the past 5 years on strippers occasionally 
hoping that if I bought them one more drink they would see I'm a nice guy
\& want me, I can be naive, lack common sense, a sense of
reality, a fool \& his money quickly part, growing up is
about taking responsibility for ones own decisions,
I was deferring the responsibility till later when
I crash landed \& had a mental breakdown, bad idea.
One reason I love strippers is that I probably need a dishonest woman
in my bloodlines, I am too honest.
As my cousin Tom would say ``how many times do you want to
hop your head off a wall'' in my case it was pretty often.
One reason I wasted so much money is that I was spoilt, my
parents never thought me the value of money. Parents who are
working their butts of so that their children will have an
easy start in life are wasting their time, self destructive
people will behave logically only when they have no other choice.
Rich parents you are only giving their children an awful lot of 
rope to hang themselves \& hang themselves they will. 
It took a long time for me to accept that
that strippers were mostly only using me for money.
\chapter{A missed opportunity}
\paragraph
\noindent
Deep down I want to get married \& have a normal lifestyle but in
all my years I had only met 2 or 3 women I fancied who actually fancied
me. I missed the window of opportunity on these occasions.
The one that affected me most was not picking up a tennis
ball dropped by a young female neighbour near home in Glantane
when I was 25, beautiful it's true, a real Charlie's Angel
for the story we will call her the pseudoname Siobhan.
Siobhan was very young \& attractive with her friend
was eager to have an older man as a boyfriend, I personally
was delighted with the attention she \& her friend  was giving me
after mass in Glantane \& reciprocated the attention.
She was far too young for me but it was easy for me to see the potential
when she got older. We used frequently meet ``accidentally on
purpose'' when she was walking her jack Russell dog or similar near
home with her next door neighbour, they both had excellent social
skills at the time but got quite vain as most women do in their
twenties as they are at their peak of their powers when
it comes to attracting men.
She was very eager to grow up \& become a woman I did
my best to treat her as one, however,
I didn't act the gentleman when she tested me, more on that later,
this affected us both deeply, ``hell has no fury like
a woman scorned''. Siobhan as she got older like me got more
self destructive, she apparently couldn't handle being 
disappointed by life very well, there was a part of me that wanted
to save her from herself, I hoped that she would save me
too, we would slow down together \& have a normal life.
Siobhan after my failing as a gentleman didn't waste any
time finding another boyfriend which she stuck with,
I understood but I no longer felt comfortable near her,
I had to move on \& it was part of my motivation to
take the job in Germany.
\paragraph
\noindent 
A few years later Siobhan had grown up \&  
I met her serendipitously one evening in Chapel Lane
disco \& felt it was time to make my move.
She was with a friend, the friend asked me for a smoke,
I went off to buy cigarettes, so far so good.
She started bsing me that she was somebody
else from Ballyclough, I showed her my new mobile
phone she was impressed until I told her it was great
for taking pictures of girls cleavage.
Later I hadn't the nerve to ask her to dance \& 
so I danced by myself, second wrong move, 
\& got pretty drunk, third wrong move,
after the disco she dropped her mascara, I didn't pick it up,
I deluded myself that she dropped it out of
nervousness at running into me, my reality distortion
was on at full tilt, I still wasn't
a gentleman, fourth wrong move. After the disco
she shouted at a girl across the road
``You are nothing but a prostitute!'' I thought
it was quite funny \& we went our separate ways home,
another time she also amused me by singing ``Bob the builder
can we fix it'', in the pub when she probably 
had a little too much vodka, who can't be seduced
by the ``fix it'' song.
\paragraph
\noindent
A few months later I started ringing her, 
Seeing as I was cleaning my act up \&
getting fit to attract the ladies
I wrote a fairly stupid letter suggesting 
to her to give up smoking, heavy
drinking, take up a bit of yoga \& exercise,
another wrong move, do I ever stop.
Siobhan around mid 2003 had
been kind enough to ring me back after I ringing her \&
she told me she got a really expensive engagement ring 
\& was marrying her boyfriend, this was the straw that
broke the camels back as far as my sanity was concerned.
Being rejected by women can lower our self worth \& make
one more self destructive, women have the right to say no.
My experience with Siobhan was one of love, heartbreak \& growth.
Eventually I managed to let go, what choice had I got,
readers, are you holding onto something which is destroying
you? let it go!
\section{Losing the plot}
\paragraph
\noindent
There was more going on here than Siobhan which drove me
mad it was around April 2004, I had lost my job \& other
events were happening in parallel described later in the book.
I was now going mad, when high I wrote two letters to the mailing list
one to say I had jackassed, the other was a desperate
love letter to Siobhan from the highest mountain
a nerd could find ``The Linux Kernel Mailing List''
which has around 10,000 email subscribers, see below.
\\\\
Subject: Linus'es dirty secret \\
To: "Kernel Mailing List"\\\\ 
Linus'es karate secret, his wife \& why linux got so big.\\\\
Want to know what you hole in the heads are doing in front of the 
computer. You are testing your metal, men without self confidence are 
subconsciously the bravest.\\\\
I became a coward.\\\\
Jackasses/Gentlemen come out only when needed \& are utterly illogical \& 
easy to spot,
Hitler never procreated \& the only
reason people looked at that jackass was to see what Jackasses look like.\\\\
When ready you know the way to go do karate in the meantime keep 
slapping the salami.\\\\
Do Karate \& you will never be seduced again you will always make the 
best of the situation
\& do whatever you blithering well please Karateka gain control by 
letting go \& clarity of thought.\\\\
Strippers are the family advertisers...\\\\
Have fun,\\
D.J.\\\\\\
Subject: Love Letter\\\\
To: "Kernel Mailing List"\\\\    
Let me tell you about Siobhan xxxxxxxx the woman that drove me to no 
fear \& the level of creativity I have now.\\\\
She is xxxx xxxxxxxx xxxxxx daughter \& at 13 looked at the most 
headf\$\%;ed 25 year old in the Church in Glantane \& said he needs me.
At 15 the test came, a dropped tennis ball she was nearer \& more in need 
of the exercise \& xxxx xxxx picked it up instead.\\\\
She is getting married very soon,
I am going to have karate sex with her anyway.
I will look after her kids with the least self confidence because I 
know they have her metal.\\\\
Tell her I love her to pieces\\\\
Phone: 00353-xx-xxxxx\\
Address:\\
Siobhan xxxxxxxx,\\
xxxxxxxx,\\
xxxxxxxx,\\
xxxxxx,\\
xxxxxxx,\\
Ireland.\\\\
Call by if in the area \& tell her I was watching her under a 
microscope.\\\\
Tell the boyfriend I'll buy the house if he likes,
pay for the wedding \& engagement ring if he likes,
See if I can hook him up with a stripper, I have been subconsciously
matchmaking lately \& the only close friend I have who I can't
matchmake for is xxx xxxxxxxxxxxx
he could keep typing with Anne Marie from Tahiti the
biggest bitch I know slapping him in the face f\$\#;ing him at the same
time \& drinking Jack Daniels \& coke.\\\\
When that f\#\$;er starts going the women had better be watching.\\\\
Thanks for all your help,\\
D.J.\\
Oddly enough quite a few people got in contact with
Siobhan's family \& upset her parents quite a bit,
please don't make contact with her anymore.
\paragraph
\noindent
When high again I read on page 69 ( position 69 )
of the book Going Mad? an example
where an overprotective mother
was calling Siobhan ( a girl of the same name as my Siobhan ) 
a ``prostitute'' for putting on makeup \& I remembered my Siobhan
a year earlier shouting to another girl after the disco
in Chapel Lane ``You are nothing but a prostitute!''
to another girl across the road,
I took this as an omen.
My sister \& father are afraid that certain things like 
reading the Going Mad? book trigger something which
makes me high, my father doesn't like me watching
certain things on TV in case I see some omenlike
significance in it \& go high again.
The following day I thought
I saw Siobhan outside Blarney Wollen Mills
but the girl spoke to me in German,
she wasn't my Siobhan I took this as another omen,
a German Siobhan. At 3am that night I went down
to Bill Shannon my maths grinds teacher
\& put a Book on Wavelets ( Mathematics ) on his car with a not complaining
that the Author was a ``Walnut'' ( that was the authors
name ) \& that I needed the teddybears version. 
I subsequently dropped
the Going Mad? book down to Siobhan's house
at 3am in the morning it wasn't read
\& was given back to my sister.
I met Siobhan's father out walking a few
weeks later \& he gave me a lift,
thankfully we understood each other
\& all was forgiven.
I have also met Siobhan in a pub recently
bought her a drink \& she said she wants nothing
to do with me. Shortly afterwords I went high,
my sister said that meeting some people with
whom you have a stressful relationship can
cause you to go high, she may be right.
\chapter{Time out}
\section{Hospital \& my varicose veins}
\paragraph
\noindent
Around this time I went to my G.P.
who forwarded me to the surgeon in
Mallow general hospital he recommended that
I get my varicose veins done but not my varicoseal
unless I had problems having children.
My Grandfather I believe he also had a varicoseal, so maybe I
would have got one eventually, it was genetic.
\paragraph
\noindent
I was quite jizzed up going for the operation
I have the height of respect for nurses but
if you think strippers are kinky?,
when I was getting put under by my anesthetic before the 
operation a nurse suspecting I wouldn't remember
took advantage of the situation, she didn't expect me to remember, I did.
\paragraph
\noindent
After the operation I was running around asking when is my
operation happening.
I got staples in my leg instead of stitches,
damn they were painful to remove.
\section{My attempts to crack RSA}
\paragraph
\noindent
RSA was offering upto \$500,000 to crack 2048 bit RSA
This has since dropped to \$200,000, they must be really
confident it can't be done, if it could the consequences
for the banking industry would be catastrophic.
the website is
\url{http://www.rsasecurity.com/rsalabs/challenges/factoring}
The problem is so easy to understand a 10 year old can
understand it, this implies to me that a clever 10 year old could
crack it.
\paragraph
\noindent
A prime number is a number only divisible by 1 \& itself.
RSA relies on the fact that there currently is no quick way to factorize large
numbers. An RSA key is made up of 2 primes multiplied
together typically 2048 bits or around 700 decimal digits long,
using current computers this takes about a guzzilion years to crack.
\paragraph
\noindent
To date I have wasted about 4 months of my spare time trying to crack RSA
\& on several occasions thought I was very close to doing
it. Philosophically the reason I couldn't crack
it that Prime numbers are truly atomic \& unbreakable.
Also I suspect that some Mathematicians \& Bankers
pray that RSA is uncrackable, I hope they stop praying.
DES \& AES are perfectly good encryption techniques
not crackable by a weakness in Maths. I have plenty
of friends who will make a lot of money from banks
once an announcement in security focus goes up that
RSA is cracked banks I suggest you start preparing now.
I put my attempts up on my website
at
\url{http://www.ariasoft.ie/gplcontributions.html}
for public consumption. If someone manages to crack it
based on my attempts please send me a percentage of the prize.
\paragraph
\noindent
If everybody trusted each other \& the world
was a better place there would be no need for
encryption algorithms like RSA.
\paragraph
\noindent
\section{Prague}
\paragraph
\noindent
If reading about people behaving badly is not your thing
skip this chapter you aren't missing much.
During the time I was attempting to Crack RSA I
went on a very enjoyable cheap holiday with Anton Wallace to Prague,
it's a pity the town isn't as cheap as it once was.
Anton \& I had the most fantastic meals we ever had
for around \euro5 in the Pizza Colosseum the name
did not reflect how good the place actually was.
That said our shabby hotel at \euro80 a night was
a complete rip off. 
During this time I was a complete egomaniac convinced
I was days away from cracking RSA.
\paragraph
\noindent
My most enjoyable experience in Prague was completely free
I was walking down Wenslas street \& was being propositioned
by various good looking ladies for sexual favours,
I was convinced that I would be mugged if I went with
any of these ladies, so I declined them all.
I got such an ego boost by the time I was at
the bottom of the street I had to go back up
the street \& decline them all again.
\paragraph
\noindent
Karlovy Lanze near Charles Bridge was definitely
the best disco in Prague one night we were
watching two characters there. An egomaniac
woman \& an army guy. The woman from the way
she was dancing was very sure of how fantastic
she was. Anyway the soldier got out of his clothes
\& danced balls naked in front of her, 
he won, at least in the men behaving badly category.
\paragraph
\noindent
If you are easily rattled I suggest you give this paragraph a skip.
It was in Prague that I had my  most educational
experience with a stripper ever, I went to a club called Goldfingers.
I got a private dance \& feeling hungry I bit the girl on the ass.
After the dance I noticed the front of my shirt
was slightly wet. To this day I don't know 
what happened but the obvious has crossed my mind.
\section{A Russian Romance}
\paragraph
\noindent
Around August/September of 2002, I was considering women
from the eastern block my first experience was
of a girl allegedly known as Evegenia.
I found her on
\url{http://www.kiss.com}
I noticed a lot of advertisements on this website were put
there by men who were mugged as warnings to other
people when they went to visit the alleged girl,
from this experience I would much prefer websites of
this type offered to do background checks of the people on it,
especially the ones in dodgy third world countries for a fee
\& give a safety approval if the people pass the background check.
Some of the advertisements were photographs of a pretty models
with bs life stories put up by a Russian mugger or similar.
Being of naive disposition it took quite a while but eventually
I got suspicious of Evegenia when she wouldn't talk
to me on the phone \& eventually had to call a halt to our communication.
\paragraph
\noindent
I eventually found Nick in the U.K.
whose wife was from Odessa in the Ukraine who
for a fee sent a friend in Odessa to
give the alleged girl flowers to check
was she genuine. My  girl this time
was Olga who I found on
\url{http://www.angelika.net}
I highly recommend this site, another great place
to meet available women however do whatever you can
to make sure the woman you are meeting is genuine.
Unfortunately Nick is no longer providing a 
service to find out if the girls are
genuine.
\paragraph
\noindent
If you are a nerd living in Silicon Valley or similar where there
is a very high ratio of men to women the odds
are stacked against you, online dating agencies
are one of the few avenues open to meet attractive
available women,
Mexico is probably a better bet than Russia, it's nearer,
to meet available women try the following URLs.
\url{http://www.mexicancupid.com}
\url{http://www.colombiansingles.com/women/mexico.htm}
\paragraph
\noindent
Getting a visa from the Ukrainian embassy
I found out the hard way was a complete waste of
time. The only way to go is use a travel
agent who specializes in travel to the Ukraine
\& let them arrange the visa. This I believe
has improved since the Ukraine won the Eurovision
song contest. The officials who check your passports
were at the time I went quite corrupt if you go
take care of your valuables in your bags etc..
\paragraph
\noindent
The Ukraine is very poor, poorer than Russia \& while there
I noticed more people looking for
food out of dumpsters than putting rubbish in.
Also in toilets there were attendants who handed
you a ration of toilet paper for a fee, scary stuff.
I found the people there very friendly \&
the cooperate with each other much more than in
Europe because they have to.
Being picked up while hitchhiking is very common
\& you usually give a tip to the person
giving the lift or negotiate on a price beforehand.
Ireland now that the economy is booming is
getting emotionally cold like Germany in the
70's this is because everybody has enough
money to be independent \& nobody needs friends or
to trust anybody anymore, it is so stupid.
The Polish \& Lithuanian migrant workers
in Ireland are not doing much for the
economy \& it is fair enough, they will
purchase their houses at home because
the houses here are so overpriced.
Most of them have university degrees \&
they are working as farm labourers
\& in shops, very few Irish people will do
these jobs anymore even though
they are less educated, it's a funny old world. 
\paragraph
\noindent
The establishment is very corrupt in the Ukraine,
Some Banks are run by the mafia, frequently claim
bankruptcy \& run away with the money.
Olga's parents got their life savings stolen
from them.
The only way to send money to the Ukraine
is by Western Union \& they charge a huge commission.
If you post money there it will usually be stolen,
this happens in India \& Mexico too.
The Mafia are the nice guys in the Ukraine, the
Police will mug you, likewise the politicians.
\paragraph
\noindent
Olga really likes Russian fables \& took me to
see a lot of statues not unlike ``the little mermaid''
in Copenhagen, she had a lot of stories about them.
One very interesting insight into the Russian psyche
is that Russians don't like Tom \& Jerry or Road Runner,
they are violent cartoons, nobody gets hurt in a Russian
cartoon. Russians have violence
in their daily life \& like to watch things which
help them escape from their troubles. Where
corruption runs rife it becomes blatantly obvious
that it is a dog eat dog World.
I suppose that is why Shirley Temple the picture of innocence
was so popular during the depression \& Norman Wisdom
is so popular in Albania, for these people living
in happy innocence is the fantasy which they most deeply desire.
\paragraph
\noindent
I made good friends with Olga, but there was no spark
of Romance.
We went to excellent restaurants in the Ukraine \& went
to visit Olga's friends \& parents who were excellent
With the exception of Olga's father who was very lazy.
Olga was afraid to leave the Ukraine because
she had to look after her mother.
Olga was manipulated a lot by men \& had
difficulty trusting them.
While there we also went out for a lovely trip on a 
ferry \& a really good funfair which Olga called
``Little Ionappa''.
\paragraph
\noindent
Hotels in Ukraine charge Westerners
about 3 times as much as they charge Russians because they can,
usually are fairly cheap \& tacky, you've been warned.

\chapter{Sigue Sigue Sputnik baby}
\paragraph
\noindent
Perkins Park Stuttgart is where all the serious sexmachines hung out,
it was there I ran into Cosmo ( aka Turkish Elvis ) 
\& Fabio the Hollywood Dancers
\url{http://www.hollywooddancers.net},
these Guys were heavy duty partiers \& probably heading for
the same crashlanding I did.
Cosmo had gained notoriety on Germany's search for
a star TV program for dropping his pants \& showing off his goods.
Fabio turned up for the second round of the competition after
disbelieving he didn't make it past the first round \& cried his eyes out
on German TV, he was told that he couldn't sing to save his life.
\paragraph
\noindent
These Guys were larger than life \& had a serious lust for it,
it was obvious to me they were going to make it big one way or the other,
Cosmo was a natural showman \& expert in social dynamics could make
an edjit out of anyone by jackassing the insecure egomaniac 
that exists in all of us, the people that think they
can't be jackassed are the ones most likely to be wound
up \& left off by Cosmo, you've been warned!
He usually started the circus at Perkins on Sunday night at 2am 
with a taunt like ``you can't dance for shit baby'' 
next thing all the break dancers came out of the woodwork.
One time Ebru a Turkish lady bartender put her hand to her nose 
\& waved Cosmo off
implying that he stinked, next week he was ready for her, he jiggled
his ass \& Magic Johnsoned his underpants off without taking down his pants
\& threw it at her, he either brought a spare one in \& tucked
it inside his pants or took it off in the toilet prior to the
interaction when he saw Ebru.
Another time in Perkins he was making a paper flower
for a girl \& looked like he was doing a good job at it, the girl was pleased,
next thing he turned around \& started eating it \& then walked off, it took
me 20 minutes to figure out it was a joke.
\paragraph
\noindent
Cosmo was fit \& I had been benchmarking my fitness against 
him for the last year.
He had a Russian girlfriend who spurted water from her 
mouth on my chest one evening at
the disco, it showed off my beautiful hairy chest 
\& titties to full effect, I was delighted;
it is amazing the kinds of attention us men shouldn't enjoy which you just do.
\paragraph
\noindent
Psychologically for me things were coming to a head,
I was being seduced down Cosmos merry path.
There was a stripper pole in Perkins \& I was practicing on it.
That Sunday Cosmo \& Fabio were there, Fabio was on the pole,
this was my big chance to perform, I was completely jizzed out
on adrenalin. Jumped on the pole \& screamed ``SHOWTIME'', next thing
I knew I was thinking ``this didn't hurt so much the last time'' \& I
could have sworn I heard my neck cracking, was I dead? was Cosmo
my Grim Reaper?, dear God he sure looked like one. I had no memory
of the rest of that night but I woke up that morning with a
bandage put on by Sali a nice Turkish barman from Perkins \& found
my pants soiled so badly it took 5 washes with a nailbrush to get
the stains out, I'd been jackassed, I broke my hole laughing it was a fantastic
release of the frustration I was having at work \& I was now
completely seduced into becoming a partyboy, blowholed
to my family \& friends about how I had got `
`fit enough to take the fall'' that
could have broken my neck. 
Work was going to take a back seat for a while.
I made it into work the following day at 4PM. 
\paragraph
\noindent
Boa Discotech Stuttgart is the place to be on Monday night all the Stuttgart
bartenders were out on their free night, body builders,
gays, Greek chicks with dicks \& other wazoos who danced in their underpants,
all hung out there, while there I came to the opinion that these extremists
exist to keep the narrowminded out of their family trees.
At that time at least I thought it was fun fun fun.
I didn't realize it at the time but I was partying a little too hard \&
being completely honest discos can be the loneliest places on the planet
especially if they are overcrowded \& there is nobody to talk to there
this is why I like strip clubs, at least Perkins had chatty barstaff.
\paragraph
\noindent
The night after the accident I met Cosmo to Boa \& had a good
talk with him \& we made friends \& I followed him to his show 
at Sinatra Bar in Rotebuhlplatz Stuttgart.
At 4am in the morning Sinatra bar the party continues till 6am,
it frequently is so busy on Monday you can't get in, it is unreal.
That night Cosmo is dancing doing his Emenem gangsta disasta rap
in his Bozo the clowns outfit on the bar, party women were doing their
``coyote ugly'' routine, that night there were Thai girls tearing \&
fighting like terriers
off each end of Cosmos underpants with their teeth 
his ass jiggling all in all it was a ``you can't do that'' 
headwreck, fantastic.
I also was busy making friends with Cosmos sister \& 
behaving badly putting Fabio's
hand on the ass of a stripper I knew, ``shaking baby electricity flowing'',
she wasn't impressed.
\paragraph
\noindent
Around this time my granduncle Jim who is now 92
from Rockhill county Limerick, still sharp minded 
\& so fit in fact I would put him piking bales to me,
told me about how my grandmother
matchmade her sister with him 
( according to my father there was a farm involved,
this may have influenced his decision a bit,
in any case they stayed married \& had a happy life together )
\& I thought this
was a great idea \& how to get the family out
of it's current dilemma in finding good women
for my brother \& cousin.
\section {The Karate kid, wax on, wax off}
\paragraph
\noindent
The following day was my Shokotan Karate class
\url{http://www.ukd-stuttgart.de}
This is where every headwrecked nerd should go to 
get a life instead of wasting their money 
on strippers, the girls are fit, usually good looking \& intelligent
as a bonus some can do the splits as well, as an additional bonus you get 
fit, learn to trust people in freefights \& make good friends
there in a healthy atmosphere. As a bonus you gain some self respect too,
all this for \euro70 a year, amazing!
Don't look a gift horse in the mouth nerds, do the roundup of your
ladies for your wild turkey chicken ranches at Karate
or other self defense classes nearby.
Unfortunately back in Ireland Karate typically costs \euro5 a lesson,
this is because the people fighting don't trust each other 
( insurance \& ambulance chasers ) this is in the wrong place in the head
for good Karate.
\section{Sports \& meeting ladies}
\paragraph
\noindent
Sitting in front of a computer all day obsessing about whatever
program you are writing at the time is psychologically unhealthy,
one needs another pastime to balance ones life out. 
Any team sport is good for nerds, I enjoyed fighting as a child
\& this is why I enjoy Karate, nerds what did you enjoy doing 
as a child, anything?,
if possible relive it. There are other fixers, skydiving
is extremely good for gaining confidence but nerds need sports
which involve other people or animals, like horse riding,
women love horses, it's a great place to meet them.
Nerds tend to drive machines because they are control
freaks \& can control machines fully,
you can't control a horse only cooperate with it, it is completely
different from driving a motorbike \& it's far more interesting.
\paragraph
\noindent
Nerds to meet women in reasonable numbers you need to go into
their World rather than expecting them to come into yours.
Swimming or playing an instrument
are also good pastimes for nerds, if you play in a band you may
get some female fans.
If you are learning to swim don't go into the deep end of the pool 
unless you can breathe properly or you want mouth to mouth from a pretty lifeguard.
\paragraph
\noindent
Dancing classes is the best place to meet women,
there are usually a lot more women than men at these,
my father was an excellent dancer \& as a result
excellent at pulling women, dirty dancing is ``gentle foreplay''
for women, though the probably won't admit it,
it's a mating ritual, most women love being shown off
\& a capable male partner is a very desirable commodity on
the dancefloor for this purpose.
Karate freefighting is my foreplay,  I enjoy women whipping me.
Yoga \& night classes are other possibilities,
cooking \& languages are good bets.
The gym, ice skating, rollerblading can also be
possibilities but if you can meet women there
I suspect you are good at chatting up \&
don't need my help.
\section{Call on me Valerie}
\paragraph
\noindent
My experience got weirder the Tuesday night after
my stripper pole accident, I met 
a female Karate green belt in free fight whom I will call Karin 
for the rest of the book, God she was fantastic.
She obviously had some serious hate for some man in her past
\& decided she was going to redirect her anger at me,
I must have reminded her of that man. 
Like an angry banshee she came at me from
all angles fighting me at full speed \& kicking me quickly but
not hard on the head. I was reversing at full speed whimpering ``OH DEAR GOD''
trying with all my might not to be jackassed into hitting her
a hard clatter back or rugby tackling her.
\paragraph
\noindent
If you think dancing with women is fun you should
try fighting one with some serious issues.
At the end of the fight my brain felt like it had been 
scrambled like an egg, I had a headache, wasted no time
telling Karin about it \& complimenting her.
The fight forced me to go someplace in the head
where I didn't have time to think, just react instinctively
to prevent myself being hit \& potentially killed.
Maybe my brain got force fed with adrenalin laced sensory input \& 
something gave way, from that point till on till I got put into 
the psychiatric hospital I became spontaneous \& never wasted time
pondering what to do just did the first thing that came into my head
instantaneously \& without inhibition, this made me make a lot of
stupid decisions, maybe it's just me making excuses for what happened.
I believed the fight gave me xen buddhist
enlightenment but not so sure now, it affected my outlook
on life \& started off my madness which led me to the psychiatric hospital,
maybe I was just stressed out.
\section{Old ironballs}
\paragraph
\noindent
Bill Shannon the maths teacher who gave me grinds
in maths when I was younger used often get himself
into trouble in pubs by speaking a little too much
of the truth to other people in the pub, he
often came close to blows \& often had to back
off with his tail between his legs. 
Around this time I bought
him a present of a jock strap so that he
could keep giving his ``lessons'' in the pub.
\section{Invite Bin Laden to my wedding}
\paragraph
\noindent
Soon after I started writing emails \& mobile phone texts 
that I was going to be married
soon, I had no idea to whom, all I knew was I absolutely believed
with no doubt in my head that I was going to be married soon.
I didn't realize it at the time but immature desperation
for marriage was getting me seriously unglued, I was in matchmaker mode,
I even asked Sali from Perkins Park to invite Bin Laden to my wedding.
I didn't even consider what a fundamentalist would think of
the hedonist party wedding I was going to have, if he came
we were all likely to be shot.
\paragraph
\noindent
Below is one of the emails I wrote around this time,
the class in Karate were patting me on the back
congratulating me after Raimund received this.\\\\
Subject: you \& your partner are coming to my wedding whenever it happens\\ 
To: Raimund\\\\
Hello there braveheart I am afraid to fight you,
If you have enough money you should start making swords,
be sure to sharpen it there are going to be lots of displayers at my 
wedding whenever it happens.\\\\

Here is another email I sent around the same time.\\\\
Subject: Xen Buddhist event\\
To: My accountants\\\\    
Aug 31st Drommahane my wedding.\\
I am shutting down the company shortly afterwords.
Neil watch my kojak tax collector \& Oliver Duennebier my saving all the 
bitches man.\\\\
www.ukd-stuttgart.de\\
join the party. \\
\paragraph
\noindent
I went out for a drink with a colleague in IBM who
initially trained me in Karate who while having
drinks phoned a girl, Karin on hearing that name
I assumed that it was my Karin who was coming for
a drink, it wasn't, I initially assumed he had some 
hidden agendas like checking was I interested in Karin
by checking did I light up on mention of her name,
I now am sure he hadn't.
\paragraph
\noindent
A few weeks later Karin picked me up on the way to Karate
she started talking about happy hours in her local watering hole
\& I began thinking I would really like happy hours with her.
\paragraph
\noindent
A few weeks later I noticed Karin's name on the my Karate jumpsuit
\& pointed out to the trainer Raimund that I must belong to Karin,
at the time he was impressed by the significance of this \& went with it.
Around this time I sent this email I wanted my trainer Raimund
to move back near my home in Ireland \&
start making guitars, around this time Raimund should
have copped on that I was losing the plot.\\\\
Subject: your my best man at my wedding\\
To: Raimund\\\\
Dear god we hardly need to talk anymore.
You think I am smart, I am such an edjit you wouldn't believe it.
Thanks for saving my life.
You got a third of an acre to build your house at home on my 
fathers farm.
You do the timber work I the bricklaying xxxxxxxx xxxxx will take care 
of the planning permission \& legal mumbo jumbo.
Your girlfriend can work in the cancer hospital in Cork.
\paragraph
\noindent
A few months after our fight once I gained my bearings I tried making dates
with Karin but couldn't, I asked her awkwardly, 
she like most women didn't 
want a man with a lack of self confidence \& unsure of himself,
a man who is unsure of himself is unsure of what he wants,
that is why the quality is so unattractive to women.
Karin was a runaway who evaded me after Karate practice.
I started emailing Karin through the Karate mailing list with
messages for Karin like ``for happy hours call me'' however some of
them were really stupid with subjects like ``Hitler is roaring''
\& I was promptly banned from the mailing list.
\section{April fool}
\paragraph
\noindent
I had lost my job at IBM on April fools day
\& was not feeling like a fool not yet at least.
I was emailing the Linux Kernel mailing list telling them
I had jackassed \& sent another email to the IBM establishment
that they were all jackass sexmachines.
The following is an email where I responded to the suggestion
by one of my IBM colleague friends who was worried was I on drugs.\\\\
Subject: am I on drugs ?\\ 
The jackass sexmachines was just a subconscious message to give more 
self confidence \& dear god giggle juice.
I am not on drugs, just desperate with headf\$\%;ed sex drive.
I have turned into a new species of male, the matchmaker jackass 
computer nerd looking after his friends the best he
can, as fast as he can, do it cos they all have 
their head shoved up their arse in front of the computer screen,
I am a Karateka a co-operator, unselfish,
not a seducer, selfish, I am Casanova playing the other game.
Don't trust any of the girls till they proved their metal.
The girl I'm engaged to hasn't proved any yet so technically we are 
unengaged.\\\\
I have no fear, I just think moment to moment \& cannot plan very much 
just have a priority list.
I suspect they will be more edjits like me emerging from behind the 
computer in a few years
if they start doing Karate xxxxxx looks high on the list, he is even 
more head\$%;ed than me.\\\\
If you need a white jackass to jump up \& down at a meeting with the 
likes of xxxxx xxxx \& kick him in the balls I'm your man.\\\\
Have fun,\\
D.J.\\\\
Around this time I also wrote an email to my ex boss
telling him like Muhammad Ali I was a prize fighter \&
I worked hard \& to save Linux for S/390
\& his ass \& it was his turn to introduce me to the ``bitches''
in his family tree because I was in heat, this definitely
was among the very worst of my emails, surprisingly my
ex boss took another email more seriously when I
was belittling my other ex boss. At this time I was
deluding myself that I didn't need to pay rent to
my landlady as she should realize that she should be
privileged to have a fine man like myself renting a
flat from her.
\paragraph
\noindent
Siobhan was gone \& I desperately needed a woman, 
I felt like I had graduated from the school of
hard knocks with a distinction in broken dreams.
I had completely lost the plot \& 
my stupid email left no doubt in my ex boss's 
head that this was the case.
I always felt that some of my colleagues at work 
\& friends I made through my life were
better friends to me than my family, as I got
more \& more mad I found out the hard way that this
was not the case. My behavior was gradually getting
on the nerves of my work colleagues at IBM \& people
whom I thought were friends, I suppose everybody
moves on. I didn't expect it but
I was personally surprised by how much my family
stood by me while I was having my breakdown especially
my sibling rival sister Margo.
Why are people afraid of madness?,
it's normally is a problem of the soul \& isn't
caused by an infectious disease, I personally believe I was quite
harmless while going mad.
\paragraph
\noindent
Another time I emailed my ex boss \& others in IBM telling
him he was stupid to let me go seeing as he wanted
to rehire me from an agency on the strength of my
resume ( he didn't realize it was my resume ), this
lack of self control cost me what few friends
I had left in IBM. I am too honest, maybe I have
a mild form of Asperger's, I keep telling people
too much of my business, I definitely should
be more calculating \& think before I speak,
``it's better to keep your mouth shut \& remain
the fool than open it \& remove the doubt''.
One trick used by politicians to check
peoples true colours is to make up a story \& judge
peoples immediate reaction to news, maybe I need
to learn a thing or two from these people.
\paragraph
\noindent
At this time I was turning into a classic manic depressive
\& told Cosmo I was the third smartest guy on the planet,
I had done my sums \& I knew this to be the case \&
was about to win a Nobel Prize \& sent
him several texts which apparently got him into a
lot of trouble, more than likely with a woman
I was trying to set him up with in Hermes Restaurant.
Cosmo with his spiderman vest showing off his body
wouldn't have got on too well with the conservative Greek waiters
his last text to me was ``FUCK YOU FOR EVER'',
he always did everything in capitals.
\paragraph
\noindent
A year later when I was high for the third time I tried to
contact Cosmo to get him to sing for my Thin Lizzy
tribute band while in the jacks in Cork I saw an omen,
``Elvis says get a life'', I feel that is what Cosmo
was saying to me at the time when I couldn't contact him.
\paragraph
\noindent
My landlady a few months earlier sent me a prudish letter
that she was worrying about my health \& my lifestyle \&
suggested I see a counsellor. Shortly after losing my job I
suggested to my nice old neighbours the Shopfs downstairs from my
apartment that they should take
up Karate \& even roared at them, when they handed back the
Ginhin Funakoshi ``Karate Do My Way of Life'' book to me about an
89 year old who had
popularized Shokotan Karate in the west if he could practice it
at 89 why couldn't they at a mere 75.
\paragraph
\noindent
I phoned my friend Pio O Connell \& told him that
Padre Pio was a very holy man with very holey hands
\& was driving nails in them every night this blasphemy
is probably why God took me to the psychiatric hospital,
more about that later.
\section{The Buddhaboy}
\paragraph
\noindent
Around this time I went into Leonardo a lovely Italian restaurant
near Schlossplatz, because I was high I was acting like
I knew something special \& the waiters were interested in
my unusual behavior; eventually I spilled the beans that
``I was Buddha \& they made it to Xen Buddhist Heaven'', one of the waiters
bought this line of bs \& because there was a festival
in Stuttgart at the time he went like a lunatic to tell everybody.
\paragraph
\noindent
After spreading the good news I walked out without paying for
the meal, you don't have to pay for anything in Heaven.
A few days later I walked in \& got all of their business
cards \& started dropping them around the Boerse ( the stock exchange )
where I am sure that in a past life as Adolf Hitler I made
a few hothead ranting speeches, at the centre of Schlossplatz there
is an Angel on a high perch \& another omen a piece of modern art
a colourful Broken Arrow B(arrow) pointing at it.
I was dropping the business cards away expecting passers
by to pick them up with the waiters from Leonardo's
waiters following this oddball who felt he never had
to pay for a meal again.
\paragraph
\noindent
Around this time I found a fantastic park up near
Perkins Park disco \& it had a lovely metal tower for
viewing the city there, being a reincarnated Hitler
I thought of this as an Eagles Nest.
There is a place near home called Nadd whose full name in English
is ``The Eagles Nest'' on my reincarnation theme 
one of Hitlers favourite hangouts \& one of mine.
\paragraph
\noindent
I was well \& truly away with the faeries at this time
\& felt it was the role of some people whom I considered
``pigeons'' to lock up ``catwomen'' specially for me ``batman''
in toilets, their role in life was perfectly obvious to me
this is what these people were designed to do.
So I proceeded to check whether some of the waiter ``pigeons''
in the lovely park had locked up Karin my ``catwoman''
Karate girl or similar for me in the ladies toilets in the
park \& had no success. Thankfully I wasn't carted
off to the police station for being a pervert,
I also checked the toilets down at Breunninger 
shopping centre where
I believed Karin would somehow psychically know
that I had meant to meet her there.
\paragraph
\noindent
To let the waiters know I was a Hitler, I took
a glass of apfelschorle meant for someone else
\& drunk it, a well built waiter got upset with me \&
to prove I wasn't somebody to be trifled with
I left a tip of \euro50. Being Hitler
I also expected to be served automatically
with cappuccino when I sat down in Perkins Park disco.
\paragraph
\noindent
Around this time I left Sandro the local hairdresser
who owns Cut Arts near my apartment most of my books
\& told him it was his job to sort out the good
guys from the bad guys in a ``Highway to Heaven'' style.
The bad guys would be
the me me me egomaniacs who liked looking at themselves \& read the yoga
books a lot of which involves self observation. The good
guys would be reading the you you you Karate books because they
observe everybody else while practicing Karate
especially in freefights \& Katas.
Sandro told me he was at one time the heavyweight
champion boxer of the Baden-Wuttenberg area.
I thought that Sandro \& Cosmo would be ideal
to help Saddam Hussein breakout in MTV Jackass style under
observation of the cameras in the court from the
trial being done by George W. Bush in Iraq.
Anyway Cosmo \& Sandro eventually figured out I was
as mad as a hatter \& weren't having much to do with
me after that.
\paragraph
\noindent
After that I went into Biddie Earlie's wearing a Linux for S/390
tee shirt \& explained to them that the S/390 on the back
of the shirt was symbolic of me moving on from programming
Linux for S/390 from IBM \& that I was a white angel.
After getting impatient about
not getting Steve's phone number I jumped behind the bar \&
started writing my I am a reincarnated Hitler rant \&
was kicked in the nuts by some edjits like them \&
they had to get control of all the bouncers in Stuttgart
who kick people in the nuts or Hitler might kill them.
Needless to say after stressing everybody out 
I got barred from Biddies as well.
While exercising in the Local Childrens playground
where I got fit I noticed rats looking at me in disgust.
I took that to be an omen of the rats in Biddies
getting control of the bouncer rats in Stuttgart.
\section{The family matchmaker}
\paragraph
\noindent
Around this time  I showed a barmaid Delilah pub a video of my brother
James I had on my phone \& asked her what she thought she said ``nice'',
I thought I had a match made for my brother. A few days later
in the night I ran into Delilah while jogging in my shorts showing
off what a fine thing I was. I gave the barmaid my weird matchmaking 
letter telling her all about her brother with the long hair 
being a reincarnated Samson working
in Delilah \& that my sister's boyfriend's
last name was Sampson. I went behind the bar to get her attention
but this wigged her out \& I got
barred from Delilah by her bouncer brother.
I used know him from Palais in Schlossplatz a few years earlier 
\& he was quite obliging there, but I suppose I got on his tits.
\paragraph
\noindent
According to my father \& sister I act aggressively when high,
this is probably what barred me, I never
notice this myself even when I am back to normal after going high.
A few weeks before this incident I saw a hallucination,
faeries laughing at me in the reflections off a ballroom 
mirror ball in Delilah, at the time I was quite relaxed watching them.
\paragraph
\noindent
At this time I was making moves on Esther \& going
for my first engagement \& 2 days later my second.
The DJ at Macabu even announced our engagement without
me asking him.
Esther told me all about her Mommee \& her brother
who worked in a Hotel \& was a great breakdancer.
She told me that when she was young used do the
parallel bars \& one time broke her ass after falling
from them. She also told me that slapping a woman
in the tits is like a kick in the family jewels.
This reminded me of an earlier time with a stripper
called Veronica from Poland explaining to me how to massage a woman's
breasts ``Like this D.J. ( softly playing with the nipples )
, not like this ( slapping them together )''.
\paragraph
\noindent
Esther also told me about the time she was jackassed into
breaking her brothers nose by slamming a door into him while
he was chasing her when they were having a fight.
I was telling the family at home I had my brother \& cousin
Tom set up with women, I just wasn't sure with whom yet.
I was in matchmaker mode \& I didn't give a fuck what
happened as long as it was good, it needed to be done
\& nobody else was up to the task. 
Because I was high as a kite I was sleeping about 3 hours \& 
walking around 30 miles a day \& my legs were in agony
from lactic acid. I expected Esther to come back to my flat to massage
them for me, I left the doors open for her, she didn't show up.
\paragraph
\noindent
Around this time my sister \& her friend Grainne came over
to visit me, partially because she was getting concerned
over my being in heat, prolific engagements \& increasingly weird behavior,
I personally couldn't see anything wrong with myself at this stage.
She stayed a few days \& all we had a good time,
but Samson the bouncer wasn't letting me into Delilah.
\section{The white Hitler}
\paragraph
\noindent
A few days after my sister left I was getting worse 
although I didn't notice this myself I put a letter into the door of another
catwoman in the local petshop who obviously loved cats in the window
there were these oriental cats who waved at you.
I put a note under the door that your oriental cats were saluting a white
Hitler ( me ) this letter I believe flew back into my pocket
but maybe I only thought I put down the correct note under the door 
( there always logical explanations for my visions ).
\paragraph
\noindent
Around this time I went into Tahiti where a new girl
from Minsk who was really good looking but couldn't dance
said I had no muscles I proceeded to do around 5 one
armed pushups in around 2 seconds, this impressed her.
She told me her father was an ex coal miner \& was
quite sick with lung problems. I suggested that
we should get engaged \& wrote her a note
about how clean the air is in Ireland \& her father
\& mother should live with us. I made a date
with her to go to the cinema. I had
another date with Veronica earlier that day,
another stripper at Cannister Wasen,
Stuttgart's version of the Oktoberfest surprisingly
she took my phone number the night before \&
she phoned me, I didn't realize it at the time
but she must have been interested to take \& use
my number, however, she called me from a phone
with the number withheld I'd suspect it's a stripper
standard issue.
\paragraph
\noindent
Veronica at least was someway intent in showing up to
meet me at the ``Breakdance'' ride,
she showed up late \& I had moved on to
my date in the cinema to meet with the girl from Minsk,
she never bothered showing up.
I even had a version of Thin Lizzy's Rosalie
with the words specially altered for her 
``From Stuttgart to Minsk all four corners of the world''
``So fantastic shes everybody's favourite stripper girl''
you get the idea, which I was going to play her on the Spanish guitar,
I never got around to impressing her with it.
\paragraph
\noindent
I found another hangout for catwomen
in Hotel Arche which had a slight Bavarian Hitler
theme to it \& it had another of those oriental ceramic
cats which wave at you like the one in the cat shop to 
salute this white Hitler, \&
I had a nice glass of wine there, Hitler was so impressed with the place
I hid a \euro50 tip under the tablecloth.
\paragraph
\noindent
Around the same time I saw Nicki \& Sophie girls from Showcentre Tahiti
around Schlossplatz Stuttgart, I pulled up my t-shirt
to show off my new 6 pack \& said ``my momma always said
women was the devil'' \& walked off, they weren't impressed.
\paragraph
\noindent
I went up to my flat \& being Hitler I always shut my
door, that day somebody banged on my door possibly
the police, believing myself to be Hitler I just let a
roar out of me \& banged the door back \& left them f. off.
There was a poor lady downstairs close to the end of her life
who had care workers call into her to look after her, change her nappies etc.
I recently was listening to a song ``Show me you love me,
tell me who I am'' I took these words literally
\& wrote to the note on her door ``Shit sick of living'',
I really regret that.
\paragraph
\noindent 
Later the same day I tried to buy a coffee for \euro50
\& was quite upset that the lady in the coffeeshop refused
to give me change, I went to a cash machine maybe I
was high \& confused but the ATM was acting completely
irrationally ( computer bug ? maybe ) even the keypad
looked illogical, I went back to the coffeeshop \& got
the coffee with the \euro50.
\paragraph
\noindent
 Later I tried to go
to Boeblingen \& was going to matchmake my ex maths teacher
daughter with a guy whom we will call Peter for the 
remainder of this book. Peter worked in my
office before April, she oddly enough had been Boeblingen too in the past, 
Peter too was a mathematician \& won his national
maths Olympics when he was 17 the match I thought
was ideal. I started texting a friend about this suggestion
next thing the train stopped \& at that same instant picture of 
another female mathematician
appeared on the screen in a speech icon on my Nokia 3650 phone
while the text message that was accidentally getting typed
to a colleague in IBM was noooooooo,
the phone \& possibly my colleague was disagreeing with me 
\& suggested another girl for Peter,
the train then proceeded to pull into the same station that we just
left Schwabstrasse, amazing, was my phone having an argument with
me or was it a software bug which God inserted which was
supposed to occur at that precise time?, was the bug unique
to my phone \& God just created a few bit errors when
the ROM for my phone was made? , it is possible by having my
phone unlocked in my pocket that I could have associated an
image of the girl in question with a particular incoming
phone call \& somehow this icon showed up at the moment
the call came in \& the train stopped.
Was the trains endstop Schwabstrasse?
\& was it pulling back on the other track into Schwabstrasse
I personally went for the miracle answer.
\paragraph
\noindent
Around this time I was giving lifeforce back to everything
by letting my eyes dance on lights \& every time I hummed
a song cars drove along beside me which hummed with me.
\paragraph
\noindent
I proceeded down to Boeblingen \& noticed I was controlling
the weather \& appearance of flowers by the size of my smile, I was high
as a kite, images of becoming ``a Spiderman'' was felling my hypomania,
 next thing I went into IBM Klub \& gave my Greek waiter
friend there a letter saying I was  dead \& had gone to Heaven,
told him that he could bargain the apartment he was trying
to buy down to \euro10,000 if he tried 
\& took a Magnum ice cream from the fridge without paying.
\paragraph
\noindent
A few days later I got a S-Bahn up to Bad Cannistat \& was
texting Anne Marie \& Sophie two strippers whom I got phone
numbers off of \& hoped they would pass on my messages,
however, they were probably calling the police \&
giving them details about where I was living. 
I expected Anne Marie to
meet me at Bad Cannistat, on the way I saw a poster
of a band called Atlantis whose singer on the poster looked just like
Esther, with a wrinkle around the nose, I took that to
mean that Esther had been jackassed into breaking her nose
out of jealousy when she heard I was engaged to another woman.
I saw advertisements for cheap flights to Paris on the way up
to Bad Cannistat, I took this to be an omen \& that 
Esther \& her mother were moving to Paris, I thought
this was a bad idea \& I had to get Anne Marie to help
me stop her. On getting to Bad Cannistat I went to for a rest
on a bench waiting for Anne Marie \& Esther to meet me at Bad Cannistat.
I expected Esther to be crying with regret that I
was engaged to somebody else. I noticed trains were
going back to Stuttgart Hauptbahnhof at unscheduled
times whether there was a special event on or whether
I was seeing hallucinations I don't know; eventually
I gave up on meeting Anne Marie at Bad Cannistat
around 6pm \& took a train back to Hauptbahnhof.
I noticed a girl in the same carriage who was a dead
ringer for the nosy cousin who saw me at the STD
clinic looking depressed when I was younger 
I took this to be another omen. 
\chapter{The angels}
\paragraph
\noindent
A friend a few months earlier was complaining about
the ladies in the canteen working at the tills wouldn't
change a \euro50 note for him, I was now seeing
women at the tills as a biblical reference.
After my Padre Pio blasphemy, my hallucinations
really went into overdrive whole streets started showing
up from nowhere in Stuttgart city centre which I never
saw before \& everyone was behaving completely irrationally,
I was having an ``Alice in Wonderland'' pacmanland like experience,
I asked God was I in Purgatory \& I asked him to slow down,
God eventually did.
\paragraph
\noindent
I was going mad but the alternate reality I was experiencing
was certainly madder than I was.
I even met Charlie's Angels at the cinema 3 young ladies
were flirting with me at the cinema with ``Hauptfilm Lauft'' 
( Main film playing ) on all the information monitors,
next thing as I was walking away they went into the
Charlie's Angels Full Throttle poster pose.
At my craziest my worst texts I sent were to the Karate trainers
\& the strippers telling them I was shagging Princess the stripper outside
my door hoping to make Karin jealous, I was getting really out of hand.
Ladies if I have upset you in this book I am sorry,
please note I never laid a finger on anyone, I was completely
harmless except for sending potentially upsetting emails \&
my one interaction with Anne which I really regret.
\paragraph
\noindent
I checked my mailbox \& I received a note from social workers that they were
in somewhat concerned about my behavior, from my crazy happenings
I took this note to mean that I was dead \& was at
this stage quite comfortable with the idea, I thought
I had been a good guy all my life \& things were
going to be better from here on in, I wasn't expecting
fire \& brimstone for me at least.
\paragraph
\noindent
I went up to my flat \& I believed that the Queen Margot bottle
of liqueur represented my sister Margo's soul, a basket represented
a basketcase ( me ) or else it was my bottle of Vieux Garcon Cognac
\& I was seeing other ``voodoo doll'' references
to souls I knew on my kitchen counter.
That night I went home \& my Nokia 3650 started answering
questions for me one beep for yes no beep for no,
maybe it just was my phone telling me it was fully charged.
I eventually went to sleep \& woke up with 2 policemen \& one policewoman
standing at the end of my bed ( Guards, My Guardian Angels ).
One of them looked just like Mr. Ott a German champion boxer
from near home who recently died this man was a ruggedly built
man about 35 bald with a mustache \& good looking
it also could have been Anne's dead father,
she said she felt his presence before looking after her,
maybe he wanted revenge on me
for upsetting his daughter \& as a result drove me mad.
The policewoman had black shoulder length hair was around 30
also well built \& good looking, the last policeman
didn't interact with me much so I can't remember what he
looked like aside from the fact that he was probably blonde.
\paragraph
\noindent
My angels however could have been psychics possibly from an alternate reality
or just ordinary people who God got to behave oddly.
God lets you see what you need to see, it's unimportant how this happens.
They went through my wallet \& found my Irish voluntary health insurance
\& said this was invalid here, they found my Malteser card this
is a German charity which helps disaster victims,
I started recently sending \euro20 a month to this charity.
I got the idea that this was not going to be a normal night.
\paragraph
\noindent
The most bizarre request of my angels was when 
they asked me to dump my Converse ``All Star'' sneakers, I think this
is because I wouldn't catch Karin even though I was wearing
them, I thought this was an omen \& they also asked me to
dump my Eastpak bag this omen I think was because
I was to go west back to Ireland \& not to travel ``East''
to Germany.
They handcuffed me and led me downstairs \& 
the policeman who looked like Mr. Ott asked me to talk to the policelady,
I was toungetied, how did they know I couldn't chat up women?,
did they notice that I had a snobby deminer?,
did they see my in the corner of a disco night after night
not making any move on what women were there?
They proceeded to show me the kinds of sins I committed through
my life more on those later.
I wished I had the presence of mind to ask them some questions like:
why did they handcuff me?, was I in purgatory?, were they
my gaurdian angels?
\paragraph
\noindent
They carried me through some modest white gates which
I took to be the pearly gates of heaven, which they weren't
\& to see a doctor with one eye which looks one way
another eye which looks the other way a 'Popeye' as I called
them, anyway the message was not to judge people from the
way they looked. From there I went to the Burgerhospital the 
psychiatric hospital where people behaved equally oddly.
There was a girl there like a female cousin of mine \& I think the
message there was not to try to pressure her into getting
married she was perfectly happy the way she was. Another
time I looked over a doctors shoulder to see what he
was writing \& he pulled away the message there was
that I was nosy \& of course they made me give a urine
sample they were ``taking the piss''. I found out
in St. Stephens that this was a normal practice when
patients go high.
\paragraph
\noindent
All of my life had lead me to this moment,
my first judgment day.
It was getting late \& I wanted to go to sleep,
the angels had kept me up long enough \& I wasn't
scared into staying awake, I now regret not having
taken the opportunity of getting the questions that
are nagging me now answered. I am having to do
the postmortem of my religious experience without
the guidance of my guardian angels.
\paragraph
\noindent
Anyway, I woke up the following morning in the psychiatric ward
in Burgerhospital Stuttgart I was diagnosed as having
``hypomanic episodes'' a kind of bipolar disorder,
bipolar means you have swings between being high,
on top of the world \& low, depressed.
This is not how I anticipated things would work out.
Everything happens for a reason,
I believe my religious experience with the Angels taking
me to the psychiatric ward was Gods ``tough love'' way
to get me to give up the drink \& slow down, the logical
answer would be that the people who recognized I was going
mad called the police in order to get me to slow down,
whatever the reason I was supposed to slow down.
The great advantage of not being able to drink is that
I never get drunk \& as a result am always free to drive,
giving up drink has given me freedom.

\section{Repenting for my sins}
\paragraph
\noindent
Sometimes we try to make sense of why God does certain
things to us. The mayor of New Orleans believes that the
hurricane Katherina happened there because
of the US's unjust war in Iraq.
I also have spent a lot of time
trying to make sense of my angels experience.
People who have manic episodes when they go mad
often have religious experiences consistent with the
religions they were brought up in.
God didn't want my experience to be clear cut \& simple,
the few parts of the experience that make sense to me
are:\\\\
I judge people on appearances, this is a real biggie,
if I am not attracted to a woman I won't talk to them
\& will never get to know them, if I am attracted
to a woman I am unable to talk to them \& will never
get to know them, I also have a difficulty in
talking to people with whom I have nothing in common,
thankfully I am beginning to find these people interesting.\\\\
I don't care enough for people with significant disabilities
like people who are retarded, this isn't their fault \& I
should be more emphatic.\\\\
I am nosy.\\\\
I try to help people who really don't want my help, I am interfering.\\\\
Enforcing my opinions on how other people should live their life.\\\\
Obsessively keeping fit for the sake of being a poser
was not going to help me, this is the best interpretation 
I can give to dumping of my converse all star sneakers \& the
bag I carried my Karate gear in.\\\\
Malteser was my health insurance, giving away this \euro20
a month was the main reason my soul could be saved
if it could be saved at all.\\\\
Slow down \& relax.\\\\
All the rest of my religious experience makes no
sense to me at all \& I spent several days in total
high as a kite sometimes seeing visions.

\section{Was I in purgatory?}
\paragraph
\noindent
Two weeks later I was left out, I got a ``jab in the ass'' of some
kind of anti psychotic which was supposed to last a month,
It didn't agree with me \& I was like a heroin junkie who
just came off drugs I was suicidal for 3 days until
I received another drug from from a pharmacy to
counteract the side effects of the ``jab in the ass''.
My friend Ollie came over ( thanks ) \& helped
me move back to Ireland on September the 19th,
I wasn't psychologically fit enough to get home on my own.
\paragraph
\noindent
I haven't ended up much nicer person after the experience,
inside I am still a child \& like pushing my boundaries,
to figure out what is acceptable behavior \& what
is not, maybe I never went mad maybe there is
no such thing, maybe I never tested these boundaries
before \& people thought I was acting strangely
\& locked me up for that reason.
\section{Born again angel}
\paragraph
\noindent
Shortly after getting home I was high as a
kite again an insomniac sleeping about 3 hours a day.
I started dropping guitars down to the house
of friends who had moved away from home leaving the standard
``I am an Angel'' note with them, well if I am an angel
I am a strange one, a queer hawk which doesn't take the chicken.
\paragraph
\noindent
My sister Margo insisted that I go into my local GP,
I told him the brain is a map of the Universe
you travel to wherever you are in the head.
He said I had better go back to psychiatric
hospital I told him to ``fuck himself'' \& charged
out \& started walking home, I was picked up quarter
way up ``Nazareth Hill'' near home I took this as a sign
that I was a reincarnated Jesus \& had more trials to go. 
Before long the GP came to our house with policemen
\& some skididley Scottish square dance music
started up on his phone \& I told him ``You love
dancing don't you'' \& proceeded to do a 
square dance \& to my surprise my sister looked on distressed,
I never in my life got the impression that she gave a
crap about me, I always thought she  had a blind spot 
when I was giving her a cry for help.
\paragraph
\noindent
Sometimes I feel like my sister wants me to be a monk
\& stop craving worldly possessions \& pleasures,
sorry but I've bought into the American dream
like most other people I know, gradually getting away from
``the unless I get what I desire I refuse to be happy''
category.
From there I was escorted by the policemen
to St. Stephens Hospital, Glanmire, Co. Cork.
While going up in the car was talking at
2000 miles an hour telling the policemen
that their thoughts were racing when there
was a lot of traffic coming in the opposite
direction, I viewed it as an omen, they
viewed it as if I was off my trolley.

\section{My experience of psychiatric hospitals}
\paragraph
\noindent
You get institutionalized quickly in psychiatric hospitals,
all your needs are looked after, all you have to
do is clean up in the morning, put on your clothes
\& take medication.
My first psychiatric hospital, Burgerhospital, was in Stuttgart city
centre \& as a result didn't have grounds.
Burgerhospital is how most people imagine psychiatric hospitals
to be, one was basically locked in with very little to do,
the days went very slowly there. I was only in Burgerhospital for two
\& a half weeks, it seemed like an eternity.
After two weeks inside locked up completely
I was left out to wander for about an hour a day,
the food was average.
\paragraph
\noindent
St. Stephens in Glanmire, Co. Cork, Ireland
used be a hospital for patients with TB \& as
a result had large open grounds with excellently
manicured gardens which we were
free to walk around, it was a lot
better than Burgerhospital, even the food was
good.
\paragraph
\noindent
The nurses in St. Stephens were real people persons
\& had amazing memories for names, they knew everybody,
they also had eyes in the back of their heads,
if you misbehaved privileges were quickly taken
off you. I lost my mobile phone several times
for sending inappropriate texts.
St. Stephens was so good that some people I knew
with nothing wrong with them checked themselves
in for free bed \& breakfast. As Christy
an inmate there used say ``all I do every day
is eat, shit \& fart, just like everybody else''.
Admittedly there was one unit, unit 5 which
was where the complete loo lahs were caged up.
\paragraph
\noindent
St. Stephens also had occupational therapy,
this basically consisted of yoga, carpentry lessons,
GROW meetings basically alcoholics anonymous 
for people suffering from mental illness,
where people learn to rebuild their lives
one day at a time,brick by brick
\& music therapy which basically involved
giving each person in the group a xylophone
a bongo drum or some similar percussion instrument
\& attempt to make music which sounded somewhat
reminiscent of a American Indian chant,
``Listen to the rhythm of the beat, AH HA AH HA''.
\paragraph
\noindent
The biggest annoyance with St. Stephens
was meeting the psychiatric doctors, this
generally involved waiting around for ``busy''
doctors for around 3 hours on Monday \& Friday;
it is a very similar experience to normal doctors waiting rooms.
\paragraph
\noindent
St. Stephens in some ways was better than
life outside of hospital, I made a few friends there,
it wasn't stressful like real life, the days went faster there than
in Burgerhospital. Once you accept loss of independence
\& that all decisions are made for you, one could easily 
stay voluntarily in St. Stephens for the rest of ones life. 
\section{My antipsychotic, Zyprexa}
\paragraph
\noindent
After my first 6 weeks in St. Stephens I got out
\& was now on a mood stabilizer called Zyprexa.
after about 6 months I gave it up
because it was making me drowsy, when having
lows on the medication.
I now know that drinking alcohol
causes me to go high as it mixes badly with
Zyprexa \& overrides its breakdown in the liver.
I may be on this Zyprexa \& off alcohol for a long
time if not forever, ``some choices we make, some are made for us''.
Zyprexa costs the taxpayer who foots most of the bill around
\euro250 a month, I suppose the chemical
companies need to recoup the R\&D costs \& make a fat profit.
It works by limiting highs \& lows, it gets converted
in the liver like drink to regulate various hormones
in the brain. At the moment I am also on another
drug which compliments Zyprexa called Lamictal.
My father claims 2 Lemon Bonbons make will him sober 
after drink ( maybe it is the zesty tang combined with the sugar ).
Guess what some variants of Zyprexa taste like, ... Lemon Bonbons.
\paragraph
\noindent
From using the drug Zyprexa doesn't appear to change 
my perception reality, from my perspective it changes 
peoples perception of me, they don't think I'm mad anymore.
I have no idea I am high \& acting odd aside from the
feel good factor which I at the time believe is natural anyway,
except for incidents afterwords if I do 
something that I regret, I am shameless while high.
I also wrote quite a lot of this book while high \& had to edit
most of it out because it was, either fire
\& brimstone bible bashing from the pulpit or complete rubbish.
\paragraph
\noindent
I would really like to see a
video of my behavior when high in the hope that
I might learn how to control my behavior, or
at very least it might reinforce within me the
need to take Zyprexa. People often get shocked
when they see their normal behavior, I suspect
that seeing my behavior when high will be doubly shocking.
I have repeated certain behaviors like giving away guitars
when high \& believed the second time it's entirely 
different to the first time I gave away my guitars,
this leads me to the conclusion that controlling
my behavior is impossible.
\paragraph
\noindent  
Going high usually manifests itself as having feelings
of invincibility \& almost no judgment according
to my cousins \& nurses who have witnessed me high. I
am almost impossible to argue with in this state.
When high every idea that comes into my head is
in my opinion at that time brilliant, although
with 20/20 hindsight I notice that most of them
are absolutely terrible.
This typically results in me doing things like matchmaking people who
don't want matches made for them \& sending texts
from my mobile phone which upset the people who receive them,
or are ordering people around.
\section{Back to work}
\paragraph
\noindent
Around February I got a 6 week job in Skygaurd in England
who were developing a GPS/Mobile phone type device,
which acts as a man down emergency beacon when people get
into trouble. The company was run out of a garden shed
there was really only one serious developer in the
whole company Richard, he did all the hardware
development as well as most of the programming.
To be honest they needed at least 8 good hardware
developers as the cutting edge chips they were
making the hardware with were going obsolete
as quick as they were developing the software \& hardware,
needless to say Richard moved on.
There was an interesting girl there from Iraq,
she gave me the impression that she was happy
to be alive considering what was going on
in Iraq, she had a very interesting perspective in life.
\paragraph
\noindent
I was living there in a Bed \& Breakfast for 6 weeks
it was interesting how far my life had gone backwards
from the party lifestyle I had in Germany just from
a mental breakdown.
I had only one good weekend there, when John Rudden
\& I went to Oxford, now that's a good party town.
\paragraph
\noindent
While there I met an interesting character
Ebrahim a modern day catholic apostle from Iran who changed his
religion from Muslim who was touched by God,
God gave him a Indian head massage one day at mass
while he was lying down which apparently was far
superior to the leg massages I gave to my strippers.
Ebrahim was definitely the type of deliriously happy guy who
would be diagnosed as having hypomanic episodes \& locked
up by my psychiatrist if he could get his hands on him
because he thought with his heart rather than his head.
He had a successful business in Nepal \& gave away all his money to follow
Jesus, Anton Wallace's timetravelling brother tried to do the
same thing \& was locked up for it.
The instant the thought that God wants me to join him
went through my head my Nokia 3650 phone beeped with a calendar alarm
it was exactly 11pm \& I had an appointment possibly with God.
\paragraph
\noindent
About 2 months later I had an interview with Xen
a University company in Cambridge University\& got the impression I would
be out of my depth, I am a very good coder, but I
would have needed to give up the drink to be able
for the job. I recommended that they should consider Samuel
Rydh the developer of Mac On Linux ( MOL ).
\paragraph
\noindent
After that I got a job in Dublin,
I never did an interview for it, this turned out
to be a bad idea, I would have found out that
the place wasn't for me, I didn't get on too well with
the people there. I lasted 9 days in the job.
\paragraph
\noindent
Soon after I got a job in Silicon \& Software Systems
in Cork, after about 7 weeks I was high
as a kite again.
At around 3am in the night I texted my friend Anton that
the only reason the only reason his brother
was locked up for timetravelling was that he blowholed
about it on sending this text I heard a cuckoo implying
I was going cuckoo
The following day I devised a stack castration algorithm
which I put it up on Google Groups for posterity. 
I spent 2 days trying to get a compile which should have taken 20 minutes,
the computer was giving me an abort retry dialog
box, I took this to be a message from God that
I should be doing something else, God wasn't going
to let me make any progress at work.
The subjects of the spam in my bulk email folder appeared 
to have significance for me somewhat akin to a horoscope e.g. 
``You've won a million, God is watching you''.
I had a panic attack my team lead showed me
a headwreckingly long list of bugs she wanted me to fix.
My only answer to her was I was a roundy roundy
she was an uppey downey \& I am a cooperator \& I
can't fix uppey downeys bugs, I told her I was
driving a Mazda 323F Celebration ``a feeling'' \& ran out
out of work when my head went into spincycle.
\section{Off with the faeries again}
\paragraph
\noindent
This experience was slightly
different to my experience in Germany because this instead of
me running away with the faeries they were running away with me,
I was out of control,
I didn't want this to happen to me,
I wanted to look after my job, it just happened.
I left the usual ``I am an Angel''
note with the receptionist.
\paragraph
\noindent
After about 2 days solid driving around the country,
this time the wiper on the back window of my 323F
was answering my questions one wipe for yes \& no wipe
for no, I checked my car \& the back wiper 
had no intermittent setting. 
The songs playing on my tape recorder were
completely indicative of my mood at that moment,
there were songs on the tape I never recorded.
\paragraph
\noindent
My first text which I wrote on the Killarney
road near Mallow was to Mick, Julia's brother
with text like ``Grrr!!! Julia nearly castrated
Hitler, Now Eddie Van Halen is going to castrate Julia
with his razorblade''
\paragraph
\noindent
I was driving around the Kerry/Cork border
\& was listening to Van Halen \& was explaining
to my cousin Dave that I was a momo living from
moment to moment, above the law \& that no Policeman
could catch a momo because we are difficult to predict
because we have no plans.
I suggested that Dave should
buy Singletons tiny cottage near our house at home \&
I was moving into the bungalow next door \& he could
defend me from the police with his pellet gun.
\paragraph
\noindent
Keeping on the Van Halen theme I also asked Dave to ``Jump''
to Baljabunion ( Ballybunion ) with Aidan O'Halloran the singer out
of tears of joy. 
When Van Halen's song ``Panama'' came on the
tape recorder I thought Margo should as the lyrics
of the song go
``Reach down between her legs \& ease the seat back''
\& move into the our next door neighbours newly
refurbished house ``with Panama Jack'' her
boyfriend Ken. Basically our neighbour
is a ``Coochy coo'' type who makes my sisters
skin crawl \& she would really have to ease
the seat back to move in with him.
I got stopped by Gardai around
Castleisland \& I tried to drive off from them,
they took my details when I tried to escape,
From this incident I got a court summons in December 2005 thankfully
the Guard who took me to the psychiatric hospital
is trying to get the summons quashed as I was unable to
call to the Garda station owing to being in hospital.
However, a second summons for not wearing a seat belt is
still outstanding.
\paragraph
\noindent
After this I thought it was a bad idea to go
any further back in Kerry \& thought I had
arranged to meet my cousin Dave at a bar called
``The Rock'' in Newmarket which I took to be
``The crossing'' for me to a better life.
Anyway I saw an advert for Middleton whiskey
on a framed mirror in the bar
\& guessed that Dave was in Middleton having
a whiskey where I met him before. Dave probably
never bothered reading a single text I sent him. 
\paragraph
\noindent
I drove back to Drommahane near home \& pulled
a handbrake turn on the way to Glashabee,
the car started moving from side to side smoothly
on the road this I took to mean that I was supposed
to meet my local mechanic who was having back problems,
seeing as my car had bucket seats I though my car
would be far better on his back than his Fiat.
I left a bag on the mirror of his Fiat that
he should drive a 323F as he can blow any bollix off the
road with it.
\paragraph
\noindent
I then drove on \& gave my Spanish guitar to Patrick's brother 
leaving it outside his house with
a note that Patrick had a job in Cork, the one I just
left working on PSOS when I was high \& I saw significance
in the fact the name of the set top box I was working
on was Humax which I took as an omen for Maximum Human.
The note I wrote to John would be pretty incomprehensible
to any sane person, it went something like
``John, Who are you who who, Scooby Doo or Ziggy Stardust,
I got a PSOS ``see MIPS run'' job for Patrick in Cork,
Utter Madness!''. Around this time I heard thunder
in Blarney woolen mills while sending more stupid
texts to my friends \& cousins, this I now think
was because God was getting angry with me. I felt
at one with the Universe \& U2's beautiful day was
playing for a reason
\paragraph
\noindent
Patrick's first job when he went to Silicon valley
was for ISI as a troubleshooter on an realtime operating system
called PSOS, mostly working on the 68000 \& MIPS processors.
Patrick loved PSOS \& often was blowholing about how good it was,
it's memory footprint the fact that it was hard realtime etc..
An closed mouth catches no flies, Patrick caught a few,
when I learned PSOS at S3 it was easy to see how it could
do meet all these requirements seeing as it had no memory
management, protection between processes or paging. 
\paragraph
\noindent
Patrick's brother was selling his house \& I being high didn't want that,
I saw significance in the fact the real estate agents John
chose was www.myhome.ie, My Home, Patrick's brother's home \& as a result
left stuff like broken guitar pedals \& my brown wolly
coat under the wheel of his car at 3am in the night, beeped
my horn at his house drove off \& came back a few times
\& left skidmarks on the gravel outside his house \&
I vandalized the for sale signs, again am quite embarrassed
about that.
\paragraph
\noindent
One of the causes of my breakdown is the price of houses
in Ireland keep going up \& I have been refusing to buy
one till the prices start dropping, I cannot afford one. As a result
I left a note in the letterbox of a house for sale locally
that I would give a rich neighbour who started with nothing
but exercised self discipline \& restraint all his life
a Spanish guitar organize lessons for him, my father would 
give him riding lessons on our horse Joey \& \euro75,000 
for a house whose asking price was
\euro260,000 needless to say my neighbour didn't take
me up on the offer \& ignored it.
\paragraph
\noindent
Eventually after the two days travelling I calmed
down \& went to ``The Local Bar'' \& was explaining
gibberish to Michael \& the barstaff that the time
on the clock in my car was a temperature gauge.
I went out to my car to start it to go to 
Newmarket to Top Car on Michael's suggestion that
he should trade in his Golf \& buy a Mazda 323F,
my brother anticipated I would drive off \& pulled
the cable off the battery to prevent it starting,
I complained to my cousin Tom that he headfucked
my car \& it wouldn't start.
I found another note in my car it was a ``security notice''
from S3 \& I interpreted this as a note of caution like
the note I got in Germany from the social workers.
I was caught by the policemen again in ``The Local Bar''
near home \& escorted back to St. Stephens.
\paragraph
\noindent
On the way back I was singing with songs
on the radio I thought I was singing like
an angel, however, my beautiful singing didn't 
impress the policemen enough to let me go.
On my first night in there I tried to walk out, 
a few nurses caught up with me \& drove me 
back to unit 3. I got some bs from the nurses
that I needed to fill in a lot of documentation.
A few hours later I tried a ``breakout''
\& was singing the Thin Lizzy song of the same
name to myself, I was going
to run to Cork city \& lay low for a while,
I got out the door other nurses started chasing me,
one middle aged man tried to grab hold of me,
I flung him to the ground. A male nurse, a rugby player,
stopped me \& gave me a look in the eyes ``please stop'',
I went back peacefully.
\paragraph
\noindent
This time got locked up this time for four months.
One time while high \& still locked up
in St. Stephens I wrote the following letter to
my ex boss \& forwarded it to a few colleagues in IBM.
Subject: re job\\
Hi xxxxxx,yyyyyy,\\
Thanks for your kind job offer\\.
However I won't be out of hospital till around the 1st of November.\\
The idea was that the other people who I forwarded
the email to would pester my bosses by asking
them are you really giving D.J. his job back
\& they would eventually be badgered into doing just
this, needless to say it didn't work.
My ex boss promptly responded with the following email
to me \& my ex colleagues at IBM which neutralized it.\\\\
Hi Dj,\\\\
you made a mistake. There is NO job offer neither in Karl's nor in my 
area.\\\\
Best regards\\
xxxx xxxxx\\\\
I was not only high I was desperate.
\paragraph
\noindent
Around this time I also had an idea that a gyroscope
spinning at around 1000,000RPM could be got to 
create an antigravity effect which would get us to the stars at almost
the speed of light, as I believed that bees use the same gyroscopic
effect with their wings flapping to defy the laws of aerodynamics,
I have since been told the aerodynamic correction was owing 
to vortices forming around the hairs on bees backs.
\& I sent an email blowholing about this to my ex colleagues at IBM.
I went high a few times in St. Stephens while on medication but
have since stabilized after giving up drink.
While home one weekend on leave from St. Stephens I noticed 
my cousin Tom had a book 
``The Art Of War'' in his toilet I assumed that the tyrant got me locked
up when I saw it initially in fact the book
is about ``art'', I made a mistake.
\paragraph
\noindent
While in St. Stephens the second time,
I met a guy called Denis
who teaches people like my illiterate father to read.
He can't live with himself because like Michael Jackson
he loves children.

\chapter{Counselling}
\paragraph
\noindent
The date is October 19 2005 I am currently in Unit 3,
St. Stephens Hospital, Glanmire, Cork, Ireland.
A few weeks ago I was introduced to my counsellor Brendan O' Callaghan.
The reason I am telling nerds what I learned from counseling
is that I believe most nerds with similar levels of self discipline
have or will have similar life experiences,
so going into detail \& sharing my hard acquired wisdom
in this section will be useful to nerds who lack self discipline
\& be a wakeup call for them.
\paragraph
\noindent
I believe my ending up in a psychiatric hospital was as a direct
result of the emotional \& physical damage inflicted on me
as a teenager with the kick in the groin. It never
allowed me to gain sexual confidence, it damaged my second
chakra if you like.
It also is quite upsetting as I believe is the case 
not to have the respect of your gaurdian angels, if anything
would make a person give up their pursuit of happiness that would.
They put me back on the rails but from a confidence perspective
the cost has been quite high to me, I no longer feel free to
enjoy life as I please.
\paragraph
\noindent
Ladies if you want to voilate or rape a man who really
deserves to be cut down to size a kick in the groin with
the intent of maiming \& does physical damage is the way to do it, no mercy.
\paragraph
\noindent
I am seldom touched by women \& when being touched flirtatiously
by attractive women, like my dear sawdoctor or one of the trainers
in Karate ``correcting my moves'' I tend to overreact \& wonder
if there is something behind the flirt.
\paragraph
\noindent
Mental breakdowns are caused by being headwrecked to submission by life \&
being unable to see a way out.
Below is an example of a cruel experiment to give a dog 
a mental breakdown carried out in the 1960's which
offers insight into how people get them.
When you shine an ellipse on the floor \& the dog 
moves into the ellipse give the dog a reward,
When you shine a circle on the floor \& the dog
moves into the circle give the dog an electric shock.
Now make the ellipse more \& more like a circle.
When the dog can no longer tell the difference \& is
unable to tell whether it will get a reward or a punishment
the dog will have a mental breakdown, it's that simple.
\paragraph
\noindent
Plants get away with doing nothing all day except breathing 
\& taking in nutrients, they don't overcomplicate life 
needlessly while some humans run around
in a rat race like headless chickens trying to get on.
Stressbuckets overcomplicating things \&
heading for a breakdown should ask themselves is
life really this complicated or am I making it this complicated
for myself. Prior to having a breakdown one is usually
running at an awful pace from something unbearable one
eventually has to stop or hits a brick wall flying.
\paragraph
\noindent
I'll be honest having a mental breakdown \& losing the plot
knocks your self confidence for six, there
is a belief that ``my actions are futile'', one is helpless
\& your lust for life goes.
Depression occurs when ones ``game plan'' lets us down.
When you are high you feel you can do no wrong
\& you do a lot of stupid things that you regret
when you come down, when you are low you have
difficulty facing into the world especially getting
up in the morning \& living with regrets of things you
did while high, the one bit of advise I can
give you is to get out of bed, one will stay depressed
while in it \& you will still have to do everything
anyway when you get up.
You can annoy people a lot asking people what they would do in
your situation \& you often end up asking the same person repeatedly
in case they have came up with something new.
The only good advise I have received to date is 
``stop feeling sorry for yourself \& drive on''.
One only needs to watch wildlife documentaries
or documentaries about the third world to realize
that it can be a dog eat dog World out there.
Count your blessings your life is probably much
easier than 98\% of the other people on the planet,
don't give up on it \& let life beat you.
\paragraph
\noindent
Since meeting my angels \& having my breakdown 
I have become a firm believer in God.
God does everything for a reason.
Many people lose faith \& ask why me? when something bad
happens in their life, life was not meant to be one
long laugh, life eventually cuts everyone down to size,
People are tested through life, when something
bad happens God expects people to have the self discipline
to get over it \& drive on.
One is here for a good time not for a long time,
if you can do it without a sex, drugs \& rock \& roll
lifestyle or being selfish live every day like it's
your last because day you'll be right.
\paragraph
\noindent
Since my mental breakdown the most important advise
I can give to anyone is to exercise restraint, self control
\& respect for yourself \& others in your life, I didn't \& that is how
I ended up in the psychiatric hospital.
Life is a test \& like a rat in a labyrinth God
will open some doors for you easily \& not others
no matter how hard you knock. Without really trying I have another 
job possibility in Stuttgart, the same woman who got me the 
job the first time in 1998 is
working in the new agency \& my original landlord
has a flat available,
a girl at the agency also knows my landlord through
basketball, either the World is extremely small or God is involved.
\paragraph
\noindent
The counsellor \& I worked out that the part of my
problem is that I never accept what happens to me \& move
on from it, I always regret things that go wrong,
there is no point being a slave to your past
one must look forward.
I also at the moment have a tendency to predict
bad fortune in the future even though it hasn't happened
yet, one can waste way too much time worrying about what might
happen, this is a really stupid destructive habit.
I am pessimistic about my future, frequently
view my glass as half empty because I am worried
about how I can get a job abroad \& have to deal with
my prescriptions in Ireland. I don't want to
be shelling out around \euro400 per month for my drugs abroad
owing to not having health board coverage for most
of the expense like I have in Ireland.
\paragraph
\noindent
The main problem I feel which drove me to a breakdown
is a lack of self discipline especially when
relating to drink \& strippers, I wasn't addicted to
drink however, I abused it.
I did a lot stupid things on an urge without realizing the
the consequences of my actions are self destructive, things I would
regret later like sending stupid texts to people while high.
I also overspecialized in my work, I learned a lot
of money \& wasted it. From my own experience having money
without self restraint \& self respect is like giving a 3 year 
old matches to play with, an accident is bound to happen,
mine was my breakdown.
I should have taken a more modest job near home which pays well.
As psychologist Carl Jung said ``Never ask a man what he
does but how he does it'', never measure a person including
yourself by their occupation or education,
the nerds opening question ``What do you do for a living?'' is indirectly
a way of measuring yourself against somebody else \&
should be avoided as an conversation
opener when you meet a person for the first time,
it creates a pretentious first impression, I've
been doing this for years because I believed
a choice of career path told me something about the person.
\paragraph
\noindent
I should have started building a house around 1998, house prices
in Ireland have gone up around 300\% in the last
decade \& it is now almost impossible to get into
the property market, I made a lot of mistakes,
maybe bad luck was involved but I am now regretting them,
owing your own house is a very strong urge in the 
psyche of Irish people, it is wrong,
wanting to own my own house is destroying me,
I'd better let it go for the moment until prices
become more reasonable \& ignore it if they don't. 
Every experience we have in life has a function \&
as hard as my life has been in some ways I wouldn't
trade my life with anybody, I made my own decisions
\& am proud in some ways of what I have done with my life.
Lets hope life really begins at 40.
\paragraph
\noindent
I personally am searching for stability \& went in an 
extremely stupid direction in looking for it in stripclubs.
Part of me was also a learning process trying to
understand the funny places in peoples heads,
stripper social dynamics as I called it.
Since I got used to private table dances I was
going to strip clubs more for company than to
satisfy sexual urges, I should have gone someplace cheaper.
My counsellor satisfies this urge through his
job maybe I should take up counselling.
\paragraph
\noindent
A colleague with whom I worked with in IBM believes my problem 
was the rut I got myself into in Stuttgart \& he suggested at
all costs to avoid the place \& that any life that I
may restart in Stuttgart will only result 
in a similar end, that I never socialized with anyone,
just drank and stared at strippers. That I need to avoid
weaknesses in my character that places in
as Stuttgart brought out.
I don't think Stuttgart was the problem it was just
the culture of places where I was trying to meet women since
being a teenager that got me into drinking heavily \&
contributed to my breakdown.
My colleague isn't completely wrong,
however after making the mistake of going off
the medication I got locked up at home in Ireland too for 4 months,
Stuttgart wasn't the whole problem.
As of January 2006 Stuttgart is my best chance
of a new job, his second point which I wholeheartedly
agree with is that it would be better if I could
stay near family in Ireland so they could deal with me
if I go off the rails again.
\paragraph
\noindent
My sister pointed out that everybody makes mistakes \& have to live
with them, when I was 6 when I was obviously completely wrong 
about something I said to my sister that I never made mistakes,
nerds tend to believe the never make mistakes, they do,
it's this rigidness in nerds belief \& value systems which
drive them mad.
People going mad cannot handle reality anymore \& want
an alternate reality so badly they succeed in creating one.
\paragraph
\noindent
My counsellor \& cousin think I overanalyse people \& situations,
to try to figure out exactly why people react certain ways.
I told my cousin that when I was high I was as spontaneous
as him, when he remembered the bad decisions I was making
when high I think he realized I'd better stay the way I am.
Maybe people have too many unknown parameters controlling
their behavior to be analyzed so maybe I should relax
\& not try to understand everything.
\paragraph
\noindent
The most successful people in life are the people who can get on with life
without dwelling on mistakes, dwelling on mistakes is a complete waste of time
just try to learn from them quickly.
If you find your mind looping with regrets like ``I should have done 
such \& such'',
change your thinking to ``I could have but chose not to at the time'',
\& learn from your mistake stop doing the ``poor me'' dwelling on it.
Sometimes though if you have enough patience \& God may eventually give
you an answer to your problem when you relax \& stand back from it
if the problem demands you to move on taking by taking a far less 
attractive option stay away from the less attractive option \&
get on with the other parts of your life until it is absolutely
necessary to take the less attractive option.
Sometimes one is so focused on achieving particular goal in life 
which may be difficult to attain that they ignore fantastic
easy opportunities presenting themselves at this moment which
may become difficult to attain later on.
\paragraph
\noindent
There is a woman I know for the story lets call her Mary.
Mary used spend upto 19 hours a day working
for a manipulative headwrecker, she prided herself on making
beautiful meals for celebrities.
Mary like myself was another overspecialized prima donna ``artiste'',
like the nerd she equated her sad idea of success with happiness,
like myself she didn't find balance.
Mary would only do what she was enthusiastic about \& go to any
lengths to do this at the expense of other parts of her life.
Mary too ended up in a psychiatric hospital \& used
mutilate her hands so she could not cook, it can happen to anyone.
\paragraph
\noindent
Life wouldn't be interesting for our psychiatrists, if they locked
up ``sane'' people.
Why did nobody lock up Hitler?
The answer given to me by my psychiatric doctor
was ``You don't have to be mad to be bad''. 
Unlike me Hitler had a lot of people protecting him,
I have since found out that he was diagnosed
by a military doctor as ``Dangerously Psychotic''.
My friend Klaus knew a Hitler's chauffeur
\& he told Klaus that he was a nice quiet amiable guy.
Don't get me wrong Hitler wasn't nice,
I believe Hitler had one serious problem he could never quite
forgive some Jews for doing something bad to him,
I suspect he went around uttering the same words
over \& over again ``I hate Jews'',
Hitlers monster henchmen just took him a bit too
literally \& gave Hitler his revenge.
\paragraph
\noindent
Some madmen think that they get locked up because they are too
intelligent \& nobody understands them, this is generally
not the case, it sometimes like in my case because they are being
stupid \& challenging everybody elses values. 
As my cousin said,
``It is not what you think it is how you act gets you locked up''.
\paragraph
\noindent
I keep giving away to people
things that they don't ask for, 
I just assume they want them \& they usually don't.
I was doing this especially when I was high.
With books it's usually that it the book is beyond me
\& I don't have the time to get to grips with the subject
\& know that the other person would be more suited to reading
the book \& might give me grinds, the remainder of the books I give away
when I have read them to people whom I think may be interested
in the subject but they usually aren't.
When high I give away guitars when I am trying to mend bridges
usually ones I have nuked, I should stop giving people things
unless I am sure they want them \& they ask for them especially advise.
Rather than give people what I think they want I should
look for people who want what I have to give.
\paragraph
\noindent
The long term goals I wish to achieve from my current
starting point in the psychiatric ward on drugs which
I don't like are the following.\\\\
My own house near home.\\\\
A wife or girlfriend, a friend first, who could help me running my
business \& potentially help me expand it. I am a loner
because I am alone, I would like to be able to depend
on someone, I want someone who can compliment
me not a servant.\\\\
A business with a future which is enjoyable.\\\\
\paragraph
\noindent
My Emotional Assets to help me achieve my
goals are... I can be quite Emphatic when I have
some time to think what cause people to react in a 
particular way \& I have definite realistic goals.
\paragraph
\noindent
I have identified quite a few barriers which
I need to recognize \& deal with which if I neglect may prevent
me reaching the goals I set out for myself.
Barriers are often functional they keep us safe
\& help define how we act in certain situations,
they also create blind spots to thinking out of the box 
\& behaving differently when it is advantageous for us to do so,
the familiar is comfortable even if we sometimes 
moan about it, acting on emotions in our
comfort zone without thinking \& restraint can
be very destructive, it is much easier
to get angry than to exercise tolerance.
Barriers are responses to situations which are
automatic \& learned during previous situations
where mistakes are made \& one says to ones self
I am never doing that again \& the behavior
becomes habitual. We don't think about what we are doing
when we are acting on a barrier maybe the reason
for the barrier has gone away \& it needs to be torn down. 
It is worth ones while analyze why ones barriers exist
\& decide which barriers should be got rid of.
I think these barriers I have may be common to most nerds.
\paragraph
\noindent
I will go to the bar \& order another drink at a disco
rather than go outside my comfort zone \& chat up a lady,
I am introverted \& stay invisible. The reasons behind this barrier
is that by chatting up the lady I may make a boyfriend
nearby jealous or get upset when the lady refuses my advances,
I believe that making the advance isn't worth my while.\\\\
Some people in bars I have noticed have a barrier
that rather than keep quiet when they have nothing
to do will sing a tribal rabble rousing song with friends
even if they can't sing well. This behavior also has
a function may in that it may be an extroverts means to get attention
\& make oneself visible.\\\\
Another barrier I have is once when a girl insulted me
in a manner she thought was funny I stuck my hand down
inside her pants, I got thrown out of Perkins Park for this,
it was easier for me to behave like a creep rather than 
take the insult on the chin.\\\\ 
My stubbornness \& unwillingness to challenge my own values
with respect to what it means for me to be a success,
as one gets older one needs to go out of their way to keep trying
new things so as not to get too set in their ways.\\\\
I am not spontaneous \& too slow to move when an opportunity
arises e.g. chatting up an available good looking woman,
the early bird catches the worm.\\\\
I am a nerd \& as such poor at dealing with people,
I need to become better at dealing with social situations.\\\\
Rather than respecting myself I am a self destructive
attention seeker.
I am hoping to get the attention of a potential partner
who will take up the job of fixing me. As a result
of having a partner I hope to gain high self worth
\& finish with my self destructive habits \&
turn myself into a more respectable person.\\\\
I hate failure \& am unwilling to take risks.\\\\
I try to give people orders, especially when high
rather than cooperate with people in order to achieve goals.
\paragraph
\noindent
The other things that came out in counselling was that I am
very unidirectional  \& obsessive compulsive in my search to
fulfill my wants \& needs, mainly women. 
I have a real fear of failure I am doing the search ``my way'' \&
for me I believed there was no alternative, of course there is, I needed to
reevaluate my options \& values. 
I have been running around disco's since
I was 17 going as often as possible to meet women \& used
freak out when going to a disco impossible even for one night,
I was impatient, always thinking there was some place better
to go \& often went to multiple discos on the same night
searching for women, I never learned to relax \& enjoy
the moment. 
What was interesting about this is the only disco I ever
actually enjoyed even if I didn't meet a woman was
Perkins Park in Stuttgart. I made friends with nearly
all the people working there, if you visit there tell
Tony, Sonya, Ebru \& Sali I was asking for them.
\paragraph
\noindent
This search naturally progressed to stripclubs once
that option became open to me in my life. This search
for me was a like a ``headless chicken'' search for lost
keys, there are always other options if you relax.\\\\
Not bothering looking \& just waiting till you run
into the keys, this is a far easier way to meet women
if you can be spontaneous chatting them up.
However, I always get toungetied when it come's
to chatting up women.\\\\ 
The other option is to sit
down \& retrace the steps in your head where you
might have left them. This is equivalent to
thinking about what options as potential girlfriends
you might have \& asking them out for a date.
If you keep running around chasing things
you won't notice what you need which may be sitting right
before your eyes. Another common mistake is focusing
too much on chasing only one woman especially if
she isn't interested, don't let your ego get involved.
A far wiser approach is to  keep a list of several women
you would like to date \& if you happen to be lucky enough
to run into them \& they are available make your move
don't take a rejection personally just move on quickly.
If the woman gets jealous all the better, that's how
my father operated, he also was an excellent dancer.
\paragraph
\noindent
My counsellor also thought there was a lot of
pathos or black humour in my book which he quite enjoyed.
He found it interesting that I managed to form
good relationships with what he considered
``shady'' characters like strippers \& I could see the
humanity within them, I personally find them
as complete as any normal person just occasionally
complete headwrecks which I enjoy in a sado masochistic way,
I learn a lot about myself from them,
the experience has been worthwhile.
\paragraph
\noindent
I have also noticed in myself when I get fed up
with people I have a tendency of nuking bridges
rather than just burning them. I get a buzz
out of nuking bridges with people who really
deserve it, this is self destructive, in the long
run I have regretted nuking these bridges but I
suspect I would have regretted leaving them 
standing too, I could have struck a better balance.
It is a lot politically wiser to just back
off from these people when you need to,
if you are dealing with fair weathered friends
become a friendliest fair weathered friend 
on the planet for them
too. You may never know when you may need them
\& get a chance to use them back.
\chapter{The realities of being a contractor}
\section{Living out of a suitcase}
\paragraph
\noindent
Being a computer contractor \& running around the world
chasing money \& finding jobs that the computer programming
``artiste'' in me was willing to do \& not compromising
on this was in a lot of ways very stupid, I have a lot of regrets,
I never managed to settle down.
\paragraph
\noindent
With every new contract I am back to square one,
living in a hotel for a few months before I find a
flat, opening bank accounts, getting electricity
\& a phone connected, moving furniture
\& when the contract ends I have to undo this \&
move all the rubbish I accumulated over the contract 
back to my father's house where it fills up a room in boxes 
\& usually ends up staying there.
On top of all this money management headaches,
see the next section, no wonder I 
had a breakdown with the worry I
had about money.
\paragraph
\noindent
Hurt has many facets,
physical, emotional, spiritual, worrying about money
mine was spiritual.
A word of advise from one nerd to another
recognize if you ``have it made'', a good job which
you can settle into for many
years, can afford a house \& have a nice lifestyle hold onto it.
Unless you are really dissatisfied with your current
situation don't go contracting, but if you find a good
contract in a nice location 
with all you available self discipline
hold onto it as long as you can
for all it's worth, keep your boss happy,
the chopping \& changing is a killer,
part of what caused my breakdown was the complexity
of money management, I was afraid if I forgot
about anything it would go out of control.
If I haven't talked you out of being
a computer contractor the best websites for
looking for contract work are:
\url{http://www.jobserve.com} in the UK \& Europe,
\url{http://www.dice.com} in the US,
\url{http://www.monster.com} Worldwide.
\section{Managing money}
\paragraph
\noindent
After the gather comes the scatter.
If you haven't noticed already I have
earned a lot of money ( the gather )
\& been very wasteful with it ( the scatter ).
Being self employed with your own company like myself
one can easily be lulled into thinking that because
you are paying no tax on expenses that they cost you
no money \& have a tendency to be wasteful with the money,
however, unlike expenses from an employer when
you are not self employed this is not the case.
One of the symptoms of hypomanic episodes is overspending,
I've been wasteful with money, I also haven't control of my receipts
either, as a result I am now having severe headaches
with my tax returns \& after having considering claiming
bankruptcy closed the company down.
Owning my own company initially was
a manifestation of my own identity it
was my own little ship, if you are considering
starting your own company for that reason
you are in the wrong place in the head, I was.
If like me you may have grandiose notions
of owning your own limited company, before
doing this ask yourself do you need
the extra hassle of having fines
or your company stricken from the registrar
of companies if accounts aren't ready on time,
you will invariably
be nagging accountants a lot of
the time to get them ready. Being
a sole trader is less stressful
\& your accounts are cheaper to do
unless you are planning on empire building
stick to being a sole trader, you can change
afterwords if you want.
\paragraph
\noindent
Like any job, nobody is better at doing your accounts than yourself
when you put your mind to it, if you have the time
want to be aggressive with your money,
management find out what accounting
packages your accountant is using \& use
similar, Microsoft Excel may be all they use,
if you do this properly \& give it to your
accountant fully prepared you should save a lot
on your accountants fees.
If you have a company personal accounting packages
aren't good enough, you need one that
is good enough to handle company accounts.
Quicken, Microsoft Money \& Gnucash
which is free are popular choices,
Unlike Excel or Openoffice Calc I personally could never get these
packages to do what I wanted.
\paragraph
\noindent
If you want to keep life simple with
regard to accounting headaches consider
working for an umbrella company ( a company
which acts as a single company entity for 
groups of freelance contractors ) in the
country your are working in, this
will mean you won't have to prepare your
own accounts, but it also will probably
mean that you will be able to claim fewer
expenses like buying computer hardware, however life
is much simpler, you just post your expenses in
every month no book keeping \& get your expenses back as soon
as they are processed, unless you are really on top
of things with your own limited company
you only know what your financial situation was
like around 12 months ago \& it take quite a while
to wind a company up whereas you can leave an
umbrella company with the same ease as you
change employers as you are effectively
an employee of the umbrella company.
Like most things in life dogs, family, house, wife,
children a limited company is an anchor if you
enjoy your freedom don't tie yourself down with one,
one is a slave to their anchors \& commitments so choose carefully
ones you like it is nice not to have too many responsibilities,
you will need to visit your accountant a few times a year
to sort matters out which can be a real pain in the butt
if you are working in another country.
If you work in a few different
countries \& contracts a year you almost
have to use umbrella companies otherwise
you will have a nightmare with accountants \&
taxation in several countries.
\paragraph
\noindent
If you are working away from your native
country like I did you may need to
pay personal tax in both
countries \& get a refund eventually
from your native country for the
days you were out of the country,
this kind of taxation between two
countries is called a double tax agreement .
This is advantageous in that you
can usually claim rent, flight \& food
expenses as you are working away from
your head office, this of course
means you need to keep receipts for
every expense.
In my years working as a contractor
the biggest gotcha I encountered with double tax
is that I didn't reclaim the refund
from my native country every year,
I left it accumulate each year I was
abroad, this meant I had to pay myself more personal
income each year to pay more double tax
( tax in the second country was been taken as
part of my net income ).
If you are paying double tax reclaim
your double tax refund asap, this improves your cash flow,
your accountant may be lazy about doing this,
if he or she is kick them into action.
You can save a lot of money on expenses 
by taking advantage of double
tax agreements but if you \& your accountant aren't going to keep
a tight ship bookkeeping wise it isn't worth the effort
just get taxed in one country without being
able to reclaim so many expenses \& get it over with.
In Ireland, my native country, they put
a cap on how much double tax they
would pay back for each accounting year,
as my income went over this threshold
this stung me, I lost a
lot of money \& it might sting you.
\paragraph
\noindent
IR35 in England is another serious tax gotcha if you are working
in a company with less than 15 employees
the taxman is going to sting you.
If you are freelance the best way
to avoid this is work for an umbrella
company with more that 15 employees,
the revenue commissioners in England 
are making this practice a bit awkward.
useful links on IR35,
\url{http://www.pcgroup.org.uk/}
\url{http://www.inlandrevenue.gov.uk/ir35/}
\section{Money doesn't buy happiness}
\paragraph
\noindent
Happiness \& success are states of mind,
some tramps living on the side of the street are perfectly happy 
\& as a result are successful.
Pleasure is not happiness, pleasure exhausts itself
in the enjoying what is pleasurable, at some time
it may soon give rise to indifference, then to
displeasure \& suffering.
Studies show that having more money doesn't make you any happier in
the long run, the elation period after winning
the lotto is approximately 2 years.
\paragraph
\noindent
A question which is a nobrainer but I'll bet some
people will hesitate, greed?, lack of trust maybe,
``would you give away all your worldly wealth to be truly happy?''
\paragraph
\noindent
Why was money ever invented?, if everybody just helped each other out
there would be no need for it, no taxmen, accountants, tax advisers,
legal profession.
\section{Getting contracts}
\paragraph
\noindent
The first bit of advise I have to give
is don't think you've got the contract until
you actually see money going into your account
from the contract. I have once been in the situation where I
was within minutes of giving my old boss
the finger when I was told that the new
contract wasn't happening \& the department
that was about to hire me was being shut down.
Never give your ex boss the finger, you may
need him for a reference or to hire you back
if something goes wrong, keep the head.
\paragraph
\noindent
I recently traveled to Germany for an interview only to find out
that the job wasn't starting for a few months,
I was lucky I managed to keep the head \& didn't
blow up on them, again, always keep the head.
Anything a few months away may never happen,
before going to an interview find out when
the job is expected to start if it is more
than a month away do a phone interview first,
save travelling expenses \& time.
\paragraph
\noindent
If you are getting your contract through
an agency before taking the job try to make
the best deal you can for yourself, find out
what the agency's cut is, ask them politely
but directly. On my first contract there
were pretty ladies involved \& the question
never crossed my mind or my bosses, the agency took 1DM for
every 2DM I earned, surely better terms
than this can be negotiated. The best
deal I ever got with an agency was 9\%.
If the agency are taking a reasonable percentage
get them to do the job of looking for an apartment
for you, furnished if you want it that way.
If you are young free \& single there is little
point in getting a flat in a quiet village make
sure the flat is where you want it, city centre?
If the flats they are finding for you are too small, dirty
or in the wrong part of town complain otherwise
you will be living in a dump until you get pissed
off enough to do something about it, I did.
\paragraph
\noindent
Find out if the town you are going to be working
in is really expensive, if it is you are going
to need a lot more money.
\paragraph
\noindent
Find out if it is possible to work directly for
the company \& cut out the middleman.
I succeeded doing this in one of my contracts,
I found the advertisement for the job on a website
\& from the content of the advert \& using google
I figured out who the company must be.
I then proceeded to find out the name
of the CTO by phoning the company directly
\& guessed his email address by
looking at the format of email addresses on
the website, persistence pays.
Other tips for landing jobs which are not advertised
can be found at \url{http://jobstar.org/hidden/index.htm}.
\paragraph
\noindent
Some companies like IBM have preferred
suppliers \& they hire a contractor in the
same way as they buy chairs, through the purchasing
department, they will only buy things from certain
preferred companies \& similarly only use certain preferred agencies.
This makes it politically difficult for an
individual to work directly for some large corporations,
but if you manage to get through this you can
become a recruitment agency for other contractors.
\paragraph
\noindent
Before accepting the job if you get a chance
talk to other people working in the company
as them are they happy with the place, is
there a lot of company politics \& soap operas
going on, do your research, look for the guys
in the corner with the ``peaky caps'' dying to spill the beans.
\paragraph
\noindent
When in the interview it should be obvious if
the contract has the potential to go on a lot
longer than initially stated in the contract,
if this is the case \& you like the place
try to do a good job so that they will keep you on.
\paragraph
\noindent
Does the job offer you something new \& interesting
to learn? will it improve your resume, if not
ask for more money. Never say you can do something
you know very little about. Most programmers
think Java is easy \& as a result think J2EE
( Java two enterprise edition ) is a walk in the
park, it isn't, there is a one to two year learning curve
for it, don't be naive you will only get fired
quickly \& lose a potentially good reference.
\paragraph
\noindent
At one interview for a games company they showed
me pictures of bunk beds in the office they
obviously expected their programmers to do
very long hours, the company will reveal a
lot about itself in the interview. How
much documentation you will be expected
to produce before you write a line of code.
Some programmers like doing documentation,
I don't, find a place which suits you.
\section{Luck}
\paragraph
\noindent
Some people are just lucky, Oilbarons like Rockefeller
who struck oil while others didn't, people in the right place
at the right time, Bill Gates meeting IBM when they
wanted an operating system for their new machine IBM PC,
Michael Moore publishing Stupid White Men
just in time for September 11th 2001.
There are about 50 open source
operating systems all written by nerdy developers
each trying to become the next Linus Torvalds,
the free operating system market is gone to Linux.
One is very unlikely to become a success by trying to emulate
someone who has already became a success.
How many musicians are there in the world
that are better than the Beatles technically?
Part of the reason Donald Trump is rich is
because he is a celebrity.
God chooses the ``lucky'', one has much more
to learn from people who made mistakes than
those who get lucky. Admittedly sometimes
people make their own luck Michael Flatley
performing Riverdance \& stealing the thunder
of the Eurovision winners that year who remembers them,
Michael was brilliant it's easy to see how he made his
own luck, he was an overnight success at 35 after
working his butt off all his life to be one.
Michael also is a hard act to follow,
Irish dance troupes beware. Copycats are wasting their
time, if you are original you can get away with
being crude the Wright brothers plane only flew
for 12 seconds, look at what your average plane
can do today every aviation engineer in the world
today is better than the Wright brothers. It also
is easier to be a success while being mediocre when you
are original, being a musician I shave no idea what
people can see in The Beatles.

\chapter{Evaluation of my experience with my angels}
\paragraph
\noindent
I wonder how different the mathematician John Nash
``A beautiful mind's'' experience was from my own.
The some of the immortal faeries he saw could have been
his guardian angels.
Almost definitely the demons or whatever it was 
which possessed my mobile phone \& car were not
answering questions too intelligently, they appear
to me to have no purpose other than to indicate
to me that I was going mad \& torment me somewhat.
I would suspect that John Nash's faeries behaved similarly.
The only experience I had which was unambiguous
was the meeting I had with my gaurdian angels
\& being honest they were a fire \& brimstone lot,
I believe they had to be this way for me because
I am undisciplined \& I needed some discipline.
I have had to give up beer \& wine because it
reacts badly with the medication I am on \&
I go mad if I drink alcohol, this is more
evidence that God is disciplining me
\& forcing me to give up my self destructive behavior,
drink damages the brain \& the liver
so I suppose this is a good thing.
\section{Demons possessing inanimate objects}
\paragraph
\noindent
Earlier in the book I described how I had an argument
with my mobile phone \& it won.
There are at least five possibilities of what happened in the
reality I was witnessing:\\
1) The phone was temporarily possessed by a demon or angel.\\
2) God intervenes directly.\\
3) Machines themselves have feelings.\\
4) It was all in the head ( I don't believe this ).\\
5) Consciousness permeates everything in the Universe.
\paragraph
\noindent
Nothing physical exists in our brains to indicate that
it holds the seat of consciousness, maybe free consciousnesses
can float around and inhabit anything they like or
consciousness permeates everything in the Universe.
Machines are in our reality just rule following idiots
this is why we think they don't have feelings.
They may be conscious in an ``Alice in Wonderland'' reality.
Maybe the reason the pioneer spacecraft is
40,000 KM off course is not because of a new law of
physics but because it is bored \& lonely,
the notion that machines have no
feelings is beaten out of children as they get older. 
My Nokia 3250 had a picture of Richard Feynman on
the front of it, could it have been possessed by him?
\paragraph
\noindent
I have since found out how a thumbnail picture
of the female mathematician could have appeared
on my Nokia 3650, if you in the contacts menu
in ``Options'' menu select ``New Contact'' now select
``Add Thumbnail'' a small picture can be associated
with a contact which will show up when a contact
rings. It is possible that the phone could have
been accidentally programmed to do this while
jiggling around in my pocket unlocked \& a
phonecall with an associated thumbnail
could have came in at the same instant as the
train stopped, however, the thumbnail doesn't
appear in a speech icon if this is done.
I also have found that my Nokia 3650
with predictive text on is something of
an Ouija board, so far without really
trying I've found a few examples
these should work with most modern
phones which use the Symbian operating system.\\\\
Type mmmmmmmmm you get nonmomo?
From earlier in the book I described a momo
as someone who lives moment to moment,
I found this one out when I didn't realize
predictive text was on \& I made an attempt
to type Mike the name of a friend
who gave me a loan of a book on Buddhism
in the local pub, he is very thoughtful
\& doesn't live moment to moment.\\\\
Try to type Margo ( my sisters name ) as
if predictive text is off you get Mass?
my sister doesn't go to mass.\\\\
Try to type my name using predictive text 
you get El Barrow.\\\\
Try to type James Barrow using predictive text
you get Lands Barrow my brother is a farmer
who likes Land.\\\\
\section{Omens \& the dangers of taking them too seriously}
\paragraph
\noindent
I notice omens especially when high,
when I am high I believe this is my little gift,
I shouldn't waste time with them but I do especially when high.
When high I believe omens are symbolic reminders left lying 
around by God e.g. music which
inspires me, muses, they get the mind to think of what
they remind me of, when high I believe they are full of original ideas on
what to do next, but they usually are not.
So far hardly a single omen I have interpreted has come true,
this is the danger of them, maybe they work for some psychics
\& mystics but they have been for me nonsense!
I personally didn't go out searching for omens, I just noticed
them \& I found meaning where there most likely is 
no meaning.
With omens one has to accept that coincidences occur.
I believe the writings of Nostradamus are nonsense \&
vague enough so that you can make events match the prophecy's
with 20 20 hindsight.
That said it is very unlikely but possible that I just haven't been
patient enough for mine to come true, maybe they are part
of a self fulfilling prophesy which I being master of
my own destiny will make happen. 
\paragraph
\noindent
Sample omens\\
Some Chardonnay wines have ``Vin d`Pays d`oc'' on the label 
describing the region that the wine comes from,
I interpreted this as  ``wine that pays the doctor'',
that's how good my French is, 
I believed it was my relaxer,
unfortunately it currently interferes with my medication \&
causes me to go high as a kite,
I have to give it up for good, so much for that omen.
Guinness is good for you, 
Beamish Stout makes you .... Beamish.
Lidl for lidl people,
Justin Timberlakes personality is just tin,
Madonna is a mad prima donna,
If you believe in omens you believe most things do exactly what 
they say on the tin, if you take omens too seriously
you get into trouble like I did with my Chardonnay omen.
\paragraph
\noindent
Below is a collection of some of the illogical linked omens
that I was looking for significance in while high \& found some,
admittedly one can find coincidences anywhere when one looks hard 
enough for them.
\paragraph
\noindent
I love Perkins Park \& the people working there it
is my favourite disco in Stuttgart.
When I was 7 I pretend married Perky the cat at home in 
front of the dishwasher my sister did the ceremony. 
The farm at home was another Perkins Park
it had Massey Ferguson tractors with Perkins engines.
\paragraph
\noindent
I noticed this omen when I was high, it must be a subconscious thing.
When PCSL were writing computer games it was a case of the
games copying reality, you probably would want to see the
games \& the people involved to find this humorous.
I was the Boozy the alcoholic horse, Dorothy the graphic artist
was Wild Bill Hiccup the one riding me,
she was dressed in drag, the big
backside \& the small shoulders was the giveaway.
Anton Wallace was the Aids Avenger dressed in the
Robocop outfit walking upto people \& talking crap to everyone.
Michael Murphy was the scuba diver in his treasure game.
One of the artists Barry Meade was Bronchi the dinosaur with asthma.
Kevin O'Sullivan was the teeth cleaner with the shiny teeth.
\paragraph
\noindent
When I was younger I broke all the Windows in a nearby house with
a pellet gun while working on Linux I was doing the exact same thing
breaking ( competing with ) Windows. 
\paragraph
\noindent
A Michael Moore from AMD interviewed me around Oct 1 2005,
I once emailed Michael Moore of Stupid white men fame to ask him to
whisper ``a sweet noting'' into George Bushes ear while going mad. 
\paragraph
\noindent
Anton Wallace's house is full of clutter so is mine 
they are real headwrecks
\& part of the reason I went mad is because of the clutter at home \& cleaning
up after untidy members of my family,
While in St. Stephens psychiatric hospital I saw a DJ Wallace interior
decorators van.
\paragraph
\noindent
While I was in St. Stephens psychiatric hospital there were
several million crows flying overhead some nights
I interpret this as an omen of people talking.
A white owl flew though the veranda at St. Stephens while
I was there, an omen? I also got the scent of perfume on occasions
with nobody woman in sight likely to be wearing it,
some people believe these are angel experiences, my mother
always wore perfume when she went out.
Pigeons almost hitting me in the forehead while walking
down Koenigstrasse in Stuttgart I think is an omen
of someone else in the cosmic consciousness having a brilliant idea,
cats are strong omens for me too.
\paragraph
\noindent
I saw an add during the all Ireland hurling champions,
it was an Irish independent add of penguins carrying hurleys.
I interpreted this an an omen of Linux ( penguins are Linux'es mascot )
coming to Ireland to visit me, D.J. Karey the caring Irish Independent.

\chapter{Conclusion of biography}
\paragraph
\noindent
On November 20th 2005 I was supposed to visit Fr. Bill
the Indian priest faith healer on a 6 day retreat 
in Newry Co. Down with Mary,
Mary was 3 times suicidal \& Jesus through Fr. Bill
cured her from depression. 
I didn't go \& am now regretting this decision.
My experience started with a religious experience,
meeting my guardian angels it should have
finished with one meeting t Fr. Bill.
Mary thought me was short \& sweet prayer
Praise you Jesus, Thank you Jesus,
the Rosary is a bit repetitive for me
everyone to their own.
I went to visit Eddie Stone another faith
healer in Cork on the 4 February 2006 with my aunt,
I didn't have any religious experience,
however my aunt fell over when Eddie laid
his hands on her \& she was touched by
the Holy Spirit. When Eddie laid his hands
on me he said I have a problem with my glands
he may be right.
I intend to meet Fr. Bill in Knock,Ireland 
around March 19th 2006 for his 6 day retreat.

\chapter{I'm a nerd what's wrong with me?}
\paragraph
\noindent
Nerds have a lot wrong with them,
extreme nerds sometimes prefer interacting other nerds over
the internet than talking to the people sitting next
to them.
Nerds should try to avoid marrying other nerds if possible
they unfortunately sometimes have autistic children see\\
\url{http://www.wired.com/wired/archive/9.12/aspergers_pr.html}\\
for more info, it's a big problem in Silicon Valley.
\paragraph
\noindent
My sister did a bit of research on Asperger syndrome
\& what she found fit me even if my psychiatric
doctors disagreed with her diagnosis.
If the symptoms below sound like something you may
have \& this is troubling you go to a psychiatric doctor 
who may be able to diagnose the problem correctly.
\paragraph
\noindent
I personally consider autism an unusual
personality rather than an illness.
There are two common mild forms of autism
which are so similar that you would need to
split hairs on your diagnosis to actually
decide whether a person has one or the other,
like most psychiatric illnesses they are only
labels used to distinguish an illness from
a spectrum of symptoms. The two mild
forms of autism are called Kanners early
infantile autism \& Asperger Syndrome the
one we will concentrate on as it appears
to be most applicable to nerds \& is
most prevalent in boys.
\paragraph
\noindent
The symptoms of Asperger's syndrome are:\\\\
Bad coordination especially in childhood,
learning to talk before you can walk.\\\\
Inability to read non verbal social cues,
unusual eye contact in social interactions,
these problems can be minimized by being
``thought'' correct way to respond to
social cues while young.\\\\
Shyness, usually making unpleasant interactions
with other people \& chance of failure in 
these interactions may cause Asperger sufferer
not to bother.\\\\
Good points: as with all autistics,
honesty, faithfulness, lack of hidden agendas,
In the long run nobody fools nobody so why lie, 
one possible measure of lack of autism a measure of how compulsive \&
imaginative a liar you are, not necessarily qualities I want.\\\\
Bad points: selfishness \& lack of empathy.
From my own personal experience I argue that
normal people being on average less honest may be able to fake
these qualities easier \& would have the social
cop on to do it, on the empathic side people
with Asperger's owing to having little talent socially
will usually be loners who not many
people aside from family actually care about \& the lack of empathy
may be a case of, ``if you don't care about me then
I don't care about you''. 
We begin with ourselves when we learn to care about people,
maybe people with Asperger's need to care about themselves.\\\\
Some Asperger sufferers never have dated anyone
\& inept at forming relationships with the opposite sex.\\\\
Adults are prone to getting bipolar disorder or schizophrenia.\\\\
Tendency to have chosen topics of conversation \& keep rambling
on about them even to uninterested partys.\\\\

\chapter{Exercises for nerds}
\paragraph
\noindent
If you are unfit go to a doctor before starting
these exercises.
Getting fit won't do miracles for you chatting up women
but it may help your self esteem.
Three hours exercise a day is too much, I recommend
a trying one hour a day rotating exercises, gyms are
for posers \& the equipment there won't get you really fit,
bench presses on a machine won't develop muscle coordination,
free weights are much better.
Flexibility I find is harder to gain than strength
so be patient with yourself.
Here is a list of the equipment you need.
\paragraph
\noindent
Books:\\
The beginners guide to Shokotan Karate by John Van Weenen.\\
Light on yoga by BKS Evingar\\
available from \url{http://www.amazon.com}\\\\
Equipment:\\
A yoga mat.\\
2 Dumbells \& about 40kg of weights.\\
A children's playground nearby, watch kids
exercise you will get loads of ideas how to Jackie
Chan yourself fit, children's climbing frames are
great for chin ups \& inclined sit ups, the
best time to exercise is at 2am in the morning
when things are quiet.\\
A Karate jumpsuit.\\
A schoolbag sized rucksack.\\
A free solid wall in your house.\\
Togs runners \& T-shirts.
\paragraph
\noindent
The first exercise I recommend I call spidermen.
\paragraph
\noindent
Lie flat put your toes pointing downwards next to a wall,
straighten your arms like you would do if you were doing
a push up.
Now walk up \& down the wall keeping your back straight
\& at the top of the walk your nose should be touching
the wall, repeat 10 times.
\paragraph
\noindent
Lay the yoga mat flat near the wall folded over twice
in case you fall on your head attempting this exercise.
Stand up straight about 18 inches away from the wall
with your back facing the wall.
Bend over backwards \& attempt to walk down the wall
with your hands till they hit the floor.
From this position attempt to do 100 push ups away
from the wall, walk with your hands back up the
wall \& your finished
\paragraph
\noindent
When you get good at push ups try doing them with
1 leg raised off the ground \& finally proper one armed
press-ups to gain finger strength try reducing the number
of fingers you are using.
\paragraph
\noindent
Back bridges or crabs, lie on your yoga mat with your
heels as close as possible to your butt.
Put your hands with your palms of your hands
flat beside your ears, lift \& try to
get your forehead touching the ground, \& rock
backwards \& forwards, try to touch your nose
off the floor to do a crab push down with your
hands \& try to get your stomach as high as you can.
\paragraph
\noindent
To do sit-ups use the bottom of the bed to hold your feet
to stop them flying up into the air 
to secure your feet use a pillow if necessary,
or improvise with something else.
As a contrast to these try lying on your stomach on the ground
place your hands behind your back your palms near your butt
now try to lift your belly \& head as high as possible off the
ground without using your hands repeat 150 times.
\paragraph
\noindent
Try handstand push-ups against the wall, this requires getting into the
headstand position to do this push with your hands when
your head is on the ground, if you can't push up to a
handstand from the ground try getting into a handstand position
initially \& only dropping a small bit towards the headstand position.
Use a folded yoga mat under your head for safety \& comfort.
\paragraph
\noindent
Neck Strengthening exercise, this exercise sounds more dangerous
than it actually is
Again put the yoga mat under your head for safety \& comfort.
Do a headstand from there try to touch your two ears,
your forehead \& the back of your head off the mat.
Repeat 10 times.
\paragraph
\noindent
Leg strengthening exercise
Stand upright now put one leg straight out in front of yourself
while lowering yourself on the other leg,
get down as low as your can.
Now repeat with the opposite leg.
Repeat 10 times.
When you do this fast it turns into Cossack Dancing.
Enjoy.
\paragraph
\noindent
BackBends, kneel down in upright position,
try to bend over backwards to get your
head to touch the ground, come back up to upright position,
repeat 10 times.
\paragraph
\noindent
For a benchpress use your bed with a continental
quilt folded along the middle lie on the continental quilt
with your Dumbells on the bed. John Van Weenens Karate book
has plenty of exercises with weights.
\paragraph
\noindent
The books I recommended above have plenty of
more exercises for you to try.
\paragraph
\noindent
Most Karate classes are held in gyms so
there is probably plenty of equipment around
to practice Gymnastics, Somersaults on Trampolines,
Breakdancing or Capoiera....
\paragraph
\noindent
Swimming \& jogging a few miles once
or twice a week with uphill sprints also doesn't do any harm
\paragraph
\noindent
Enjoy

\chapter{Consciousness, madness, science \& spirituality}
\section{Theory of consciousness determining reality}
\paragraph
\noindent
Every good idea begins with a blasphemy, believed
by a majority of one, the person who came up with it,
this theory fits at least the second part of this criteria
at the moment. 
I was driven to come up with this theory to make
sense of my own experiences, they were real to me.
This theory is both spiritual \& scientific,
there is ``God in the gaps'', however, I believe
I put God in a very logical gap. I have been computer
programming for over 20 years \& strongly believe that
consciousness cannot be explained scientifically.
The latest version of this theory can be downloaded from
\url{http://www.ariasoft.ie/ebooks/theoryofcdr.pdf}
\paragraph
\noindent
In the following few paragraphs using known \& generally
accepted principles \& theories of quantum mechanics \&
one small addition of my own
I provide what I feel is strong evidence that there is a Heaven
\& that timetravel is a rare but normal occurrence.
If you cannot understand the arguments I present below
I suggest researching further on
\url{http://www.google.com} or alternatively buying\\
Introducing quantum Theory by J.P Mc Evoy \& Oscar Zarate \&\\
Q is for quantum by John Gribbin from\\
\url{http://www.amazon.com} or similar.
\paragraph
\noindent
Just because drugs can induce hallucinations \&
there is an area of the mind devoted to fantasy
doesn't mean to me that hallucinations are ``in the mind'.
If you are sure hallucinations are just ``in the mind'
you need to learn quantum physics.
I am about to show that everybody in the world may have equal
right to believe their own perspective of reality even the madman.
The madman may just be viewing a different equally physical Universe to
that perceived by sane people.
\paragraph
\noindent
The role of a conscious observer is of very real importance 
to what we know as reality.
As far as quantum physics is concerned \& to understand it
you need to unlearn all the Newtonian physics you have learned
since you were 3 years old \& re philosophize.
\paragraph
\noindent
The Schroedinger Cat thought experiment was originally thought up
by the Austrian physicist Erwin Schroedinger in 1926 to 
highlight the ridiculousness of quantum physics,
it now is being used as an example to describe how
quantum physics really is.
In the thought experiment a cat is locked into a closed box with a radioactive
substance which ejects a radioactive particle at
random intervals, there is also a radiation detector in the box 
which will detect this radioactive particle if it is ejected,
if a radioactive particle is detected a gun goes
off which kills the cat. The box is soundproof \& all
the walls are opaque so the only way of telling
if the cat is dead is by opening the box.
The rules of quantum physics dictate that the cat is in a
superposition of states, both alive \& dead
until the box is opened \& observed by a conscious
observer, this conscious observer by observing causes
a ``crystallizing of reality'' which
in quantum physics is called the ``collapse of the wave function'.
This superposition of states is the cornerstone to the
``many worlds'' theory.
\paragraph
\noindent
The strong anthropic principle states that 
the Universe must have those properties which allow life to 
develop within it at some stage in its history.
In other words the a Universe cannot form unless
there are conscious observers to watch it at some
stage in its history.
\paragraph
\noindent
Whenever a sub atomic event with multiple possible outcomes
occurs all of these outcomes become real and form
a series of parallel Universes that have a separate
existence \& development. Our consciousness
inhabits just one of them, the reality we experience. 
This is the ``many worlds'' theory as initially proposed
by American Physicist Hugh Everett, these many worlds
coexisting is another building block in my argument.
\paragraph
\noindent
I am now about to give you the most important idea in this argument.
Because the conscious mind is of central importance to what
one perceives as reality, I believe that altering the brain's state 
e.g. by giving the victim drugs, alters the 
reality the victim experiences to one of the other ``many worlds''
different to the one 
experienced by the rest of us who don't 
have our brain state altered, this is somewhat akin
to the victim tuning into a different television channel to
the one that sane people watch. Clarification is needed here,
by consciousness determining reality I mean that
altering the victim's brain state determines the flavour
of the reality being experienced by the victim, 
the victim I believe cannot influence the direction of his
or hers experience by choice.
There are other ways of altering our brain state
besides Drugs e.g. a strong electromagnetic
field may alter the way synapses in the brain fire, a victim
having a brain hormone imbalance \& going mad will cause
the victim to experience an alternate reality.
\paragraph
\noindent
Altering the brain's state while the victim is alive 
is equivalent to altering the victims conscious state.
We are spiritual beings, God made us flawed ``machines'
completely understandable to ourselves from a science
perspective so we would be able to learn to repair ourselves
except for our consciousness, this is our soul.
Daniel C. Dennett of ``Consciousness Expained'' fame
interesting arguments trying to explain away
consciousness by saying it doesn't exist, but wrong.
The brain is only a physical manifestation where
consciousness takes place while the victim is alive.
Doctors may talk about scientific things like brain
hormones \& can find out when we are dreaming by 
measuring brainwaves \& have a basic map of
what part of the brain does what from
measuring brain activity using EEG's \& studying braindamaged
victims, but to be honest they don't have a clue how
brains work, this alteration of brain state has to be
accepted as being spiritual. Science might one day
be able to explain the brain as a consciousless
zombie computer which has neural net algorithms
deciding what to do next, but I wouldn't expect
it anytime soon.
\paragraph
\noindent
I myself personally believe that God normally only 
crystallizes the reality of one Universe for normal people 
\& then creates others temporarily when observers need 
to witness an alternate Universe, some variant of the anthropic
principle may apply to this alternate Universe.
\paragraph
\noindent
People witnessing the virgin Mary in Lourdes or similar 
are multiple people seeing the same hallucination,
this is how Mary does her work, like most women
she is chatty \& likes talking to people, nice woman.
Surely Occam's razor should apply here,
the simplest explanation is the most likely,
it is much easier for God to create one
alternate reality for these people to tune into
than give them all ``in the head'' experiences. 
The only difference between these visions \& the hallucination
of a madman's that nobody else witnesses the madman's hallucination
so he has nobody to back him up.
\paragraph
\noindent
Rarely after a lot of drink people believe they
are being chased by Rats \& attempt to climb walls etc.
to avoid them. This commonly happens to people suffering
from Delirium Tremens DT's. This I think is not
a figment of peoples imagination but a very real experience
in an alternate reality, I believe this is God's way to 
scare the crap out of self destructive drunks to get them
give up drink.
\paragraph
\noindent
For conscious entities time is just a measure of rhythmic
machine ``ticks'', sometimes it moves fast, sometimes it moves
slow, ``A watched kettle never boils'', in life \& death
situations an altered state of consciousness occurs where
time moves very slowly of victims so 
they get time to react, for some people their entire
life flashes before them in a moment, some people report
only seeing things in black \& white because the brain
doesn't have the time to process colour images.
Large doses of adrenalin causes an altered state
of consciousness which slows down time for the victim.
If slowing down time for conscious beings is possible why not timetravel?,
Some people in who get put into psychiatric hospitals
experience timetravel, these grandiose thoughts can be caused
by a lot of psychotic disorders but are generally caused
by a serotonine \& dopamine hormone imbalance.
In the book ``Breaking the time barrier'' by Jenny Randles,
several people have claimed to timetravel including
the inventor of AC electricity Nikola Tesla.
The ``time machines'' these people use typically
generate an electromagnetic field around the brain
which the inventors claim generates an
``alternate state of consciousness'' whether
these inventions work is questionable but their
operation is consistent with my theory.
\paragraph
\noindent
God has been providing people with glimpses \& hints
of Heaven at least since man first walked the earth.
Outer body experiences or OBE's 
are usually near death experiences when the 
soul or consciousness temporarily leaves the body
\& floats above it, from this perspective the person
having the OBE can see things which would be impossible
to see if the consciousness remained in the body.
It is caused I believe by a lack of oxygen to the brain.
When the person is brain dead I believe the consciousness 
is fully released from the body \&
allowed to rejoin the cosmic consciousness or
even go to what I believe is Heaven that 
``bright light, happy place'' that some good OBE victims experience.
I'd suspect Heaven is where all the good souls become one \& hell
is where all the bad people get locked up in  isolated from everybody else
\& lost from God.
\paragraph
\noindent
LSD \& Magic Mushrooms I believe can take drug abusers 
to ``Alice in Wonderland'
alternate realities, these realities can be places where the World
is flat \& the planets are carried around by angels, Galileo I suspect was
only correct about our reality. Terence a friend said he once after
taking LSD saw policemen as ``pigs on wheels''.

\subsection{Maya, the beauty that hides the reality}
One physicist who took potshots at my theory of consciousness 
determining reality asked
me to go off \& live in one of my alternate realities
if it is so real. People do this all the time \&
pay for it through the nose by taking drink \& drugs. I like a lot
of other people throughout my life personally
have wasted a fortune on drink, I lived in the alternate
reality where the bed flys around the room,
throwing up in the toilet \& generally behaving badly,
it wasn't all that great, certainly not worth the money
I paid for the experience. I personally haven't been in the
``Beer, helping ugly people have sex since 1862'' category
but I know plenty who have \& regret it. As for drugs LSD isn't
all that great, plenty of people have bad trips \&
some even end up vegetables after it.
People escape to alternate realities all the time,
why the taboo about going mad? If I was having
amorous adventures with Charlies Angels I strongly
suspect they would be ``even better than the real thing'', even
if in a ``cloud cuckooland'' alternate reality, I would love 
to be locked up in a psychiatric hospital
with my angels having all my other needs looked after.
\paragraph
\noindent
Skeptics investigate psychics all the time with little
positive results. According to ``Breaking the time barrier''
one in ten people report being able to timetravel using
the machines which surround the brain of the victim with
electromagnetic radiation \& there has been even some
success in tests by skeptics. I personally would
like it if more research is done on people
who claim to be able to timetravel either by being
mad or via machines. I personally feel it would be
a lot more productive than investigating psychics.

\section{The Cosmic Consciousness} 
\paragraph
\noindent
The Cosmic Consciousness is the sum total of all the individual
consciousnesses in the Universe \& is a small part of the
mind of God, we are all part of it.
\paragraph
\indent
Ideas may fly in \& out of conscious beings from one person
to another like pigeons flying in \& out of pigeonholes.
The best eureka ideas often fly so fast between people
they almost hit them at the same time, this often happens
in science.
The cosmic consciousness may only have a set number
of memes ( ideas ) \& these may all have been exhausted
billions of years ago by more advanced civilizations than us in
the Universe.
Conscious beings are vessels for carrying memes in the cosmic
consciousness.

\section{What is the Universe theory}
\paragraph
\noindent
This theory may not be completely original as I heard of
the Universe being described as a process before by quantum physicists.
\paragraph
\noindent
There is a concept in quantum mechanics which Einstein
referred to as ``Spooky action at a distance'' or the EPR paradox.
This happens when a pair of particles e.g. electrons 
interact with each other \& are set up to have a quantum
property e.g. total spin to be 0.
The electrons then fly apart not interacting with anything else
till the experimenter decides to look at them while the
particles are travelling apart across the Universe,
they are both in a superposition of spin states, both up \& down.
When the experimenter decides to measure the spin property
of one electron owing to the ``collapse of the wavefunction''
described in the previous section.
the spin property of the other electron
is instantaneously equal but opposite, i.e one
electron spin up the other has spin down, this
shows that non-locality is indeed a property of
the quantum world. 
How can the Universe be considered 3 dimensional
in the Newtonian sense if interactions can
happen across its entire width instantaneously.
The Universe is not really a ``thing'
as you would expect in Newtonian physics,
it is a process in Gods mind which is brought
into reality by conscious observers like ourselves observing it.
Newtonian physics allowed instantaneous action at a distance
too, with gravity, but made no attempt to explain it.
\paragraph
\noindent
God could make everything in this Universal process happen instantaneously
but doesn't, he makes most things travel below the speed of light,
the reason for this is that if he made everything happen
instantaneously the Universe would be over in an instant
rather than have a big bang the Universe would be more
like a big instantaneous impulse.
\paragraph
\noindent
Most people think that Einsteins theory of relativity
states that nothing can travel faster than light,
this is probably not the case, there are theoretical particles
called tachyons which travel at slowest a tiny bit faster
than light upto infinite speed.
The fact a tachyon if it exists is able to go at infinite speed 
is more evidence that the Universe is a process in Gods mind.
\paragraph
\noindent
Einstein once said ``are we thereby to suppose that
the Moon ceases to exist if we stop watching it?'', 
I personally believe this is the case even if it 
is unimportant to my argument, why would God
expend energy in creating a Universe that nobody is looking at,
this would be akin to writing an inefficient computer algorithm,
anybody who has ever written a raytracer knows the importance
of optimization.
I believe God only creates as much of the Universe as
conscious observers need to see observing it from moment to moment.
As such I believe there is no real end to the Universe, God will just
keep creating vacuum as conscious entities are travelling
through it. Beyond the furthermost planets from the
centre of the Big Bang the Universe is very boring.

\section{Mixing science with religion}
\paragraph
\noindent
Science will allow us eventually to live till our
Universe collapses to the big antibang or our Universe
dies of ``Heat Death'', we might be able to prolong
this agony somewhat by travelling back in time 
if technology permits it.
God gave us a fear of death to sort out the good ones
from the bad greedy ones, nobody can survive the end
of the Universe, science won't let it.
\paragraph
\noindent
The entropy ( disorder ) of the Universe is constantly increasing \&
to create a lot of order in one place to make
a device like a silicon chip you need to create a
lot of disorder elsewhere by using a lot of
energy \& chemicals, putting a china cup back together is
a lot harder than breaking it. The only way to
decrease disorder would be to make time go backwards.
\paragraph
\noindent
Living longer only means living with more misery
later in life when our bodies let us down \& suffer
from old age, cancer, heart disease \& failure
of our brains. I personally don't want to spend
the last ten years of my life fighting cancer.
Live fast die young \& leave a great set of photos.
Who wants to live forever when you can be a nice guy
die a peaceful death \& go to Heaven, it's easier.
\subsection{String Theory}
\paragraph
\noindent
String theory is the heir apparent to quantum theory.
This is bound to raise a quack alert in the science
community, go to
\url{http://quasar.as.utexas.edu/BillInfo/Quack.html}
if you want to categorize me,
but I have a hunch that string theory may be about music,
There are twelve notes in an octave, seven in a scale,
could the dimensionless constant
\begin{math} 
2^{1/12} = 1.059463094
\end{math}
the multiplier between the frequencies of semitones
be of significance?
\section{Spirituality}
\paragraph
\noindent
If you had to ask God questions what would they be?
Who created you? This question is invalid, 
God wasn't created, God always existed.
Why does God exist? So that we could exist.
Who do a lot of people not believe in God?, arrogance.
Did God create the World in 7 days \& just
leave remnants like fossils, dinosaur bones \& cosmic background
radiation around to fool scientists that it is much older?,
it's extremely unlikely but he could have.
Which parts of the Bible are truth \& which
are a fable that the Pope just happens to like?
\paragraph
\noindent
Loving something brings it to life either literally
or metaphorically babies, performers,
I'd suspect anything can come alive when you go mad,
mathematics, physics, music, art, machines did for me.
In Breunninger at Christmas they are jazz musicians dressed 
as Santa Claus who can bring a simple tune like Jingle Bells
to life for me.
\paragraph
\noindent
Statistics have nothing to do with luck when God is involved.
\paragraph
\noindent
If one died every time one went to sleep, which one
might in alternate realities \& a new clone got all ones
ideas \& life experiences transferred would it matter?,
I suspect not much.
\paragraph
\noindent
Most of the worlds peaceful major religions are relatively compatible,
well at least Christianity, Hinduism \& Buddhism.
However the commandment ``I am the lord your God
\& you shall not put strange Gods before me'' means
Christianity \& Judaism win out on the choice of God,
however I suspect what God primarily meant were strange Gods
like money \& power.

\subsection{Dabblings in Buddhism}
\paragraph
\noindent
Buddhism is more a philosophy to live by 
than a religion. You can be Buddhist \& 
still be a Christian, though you may get some
resistance from Christians who don't understand
what Buddhism actually is.
Buddah is not a God which is worshiped,
it's an ideal which all Buddhists strive to be.
Buddhism is primarily about finding peace 
\& compassion within ones self.
The seven deadly sins in Buddhism are the
three destructive emotions
craving, anger \& delusion.
One aim of Buddhist practice is to 
reduce the power of destructive emotions in
our lives. Buddhism provides a mental emotional
compass whose purpose is to guide you in the
right direction through life.
Buddhism is the only major philosophy/religion I know which
studies psychology especially when
it comes to handling emotions, Christianity could learn
a lot from this, I personally have gained very little psychological 
emotional guidance from Christianity \& probably
would have learned to prevent my breakdown had Catholicism
religion provided me guidance in this regard.
\paragraph
\noindent
The fourteenth Dali Lama is quite
a science buff \& for a holy man
of peace is quite interested in weapons
of war. Buddhism \& science's goals
are differing approaches to the same
end seeking the truth.
Buddhism is very open to adaption,
it uses findings in science to progress 
\& rewrite it's teachings.
The Dali Lama is interested in all science except
what he calls the dry theories of computer science,
he obviously hasn't much time for computer nerds.
\paragraph
\noindent
I personally don't see much distinction between
meditation \& relaxing, monks are just very talented
at it. I have very little talent at meditation
apparently it is a skill like playing a musical
instrument it needs to be practiced \& probably
is something most effectively learned when
young when the brain is most malleable.
\paragraph
\noindent
Buddhists believe death is a transition to
another state of existence, this agrees with
Christianity \& my own personal beliefs.
\paragraph
\noindent
I haven't read many Buddhist books but
the ones by the Dali Lama are generally
narrated by authors who run around with
him \& have a tendency to tape every utterance out of his
mouth as if it was insightful \& commit it to paper, 
parts of these books are good, parts bad however I suspect
there are more insightful books on Buddhism than these,
ask someone who knows.

\section{Opinions on madness}
\paragraph
\noindent
Anorexia is probably form of madness, skinny people who think they are
fat, maybe this form of madness is curable by 
anti psychotic drugs or hypnosis.
\paragraph
\noindent
People who hear voices or have split personalities
I believe are genuinely possessed, they appear to be inhabited 
by 2 consciousnesses,
drugs only cure the symptoms not the problem. 
I personally think they need to see a priest
to exorcise their demons permanently.
I have met tramps who live on the streets say
things to me they should have no knowledge of,
I believe they were possessed.
\paragraph
\noindent
In Burgerhospital I believe I was in a room with somebody
who was so out of their mind they were in mine,
he knew what I was thinking \& verbalizing it with his groans.
I admit this however may have just be a feeling like deja vu \&
when I was high driving my car around while high I
felt that the songs on the tape recorder 
\& radio were exactly indicative of
my mood, maybe my mood while high just followed 
the songs on the tape recorder \& radio.

\chapter{The Science Bit}
\section{Where science fact is at compared to science fiction}
\paragraph
\noindent
The Internet is the greatest accelerator in the progression of
individuals acquiring knowledge since the invention of the printing press 
yet it was never envisaged by popular science fiction writers.
Sooner or later school will become obsolete \& people
will be acquiring \& distributing all their knowledge via the Internet.
The biggest problem won't be quantity of knowledge available
it will be quality. It will be interesting to see how
``google answers'' progresses.\\\\
No science fiction writer could have even conceived the 
atomic bomb in the 1920's one can only begin to
imagine what fruits of science God or the Devil will
put mans way in the future.
The communications satellite has wildly exceeded
Arthur C. Clarke's 1948 groundbreaking expectations owing 
to miniaturization in electronics \& this occurred only
16 years after his initial prediction of it.\\\\
My Nokia 3650 mobile phone is nearly 3 years old \& has more
features than a Star Trek communicator.\\\\
Phasers with stun settings from Star Trek exist, 
soldiers will soon be guarding
nuclear power installations in the U.S. have them see\\
\url{http://www.vnunet.com/vnunet/news/2139292/aims-star-trek-ray-}\\
\url{guns-nuclear}
for more info.\\\
Lasers which can shoot missiles out of the sky exist see
\url{http://www.smh.com.au/articles/2003/02/14/1044927802198.html}
for more info.\\\\
Universal translators like on Star Trek exist,
I can read the online version of the Stuttgarter Zeitung paper 
in English with them, have a look at 
\url{http://www.av.com} translate, otherwise known
as babelfish, google has a similar translator.\\\\
Common PC's now have speech recognition capabilities.
\paragraph
\noindent
Space travel is where we are falling way behind
Star Trek so here is where I wish to push the boundaries,
I am not an expert in rocket science.
Maybe the current space travel technologies have matured
\& a quantum leap in technology, something better
than rocket propulsion is needed for things to
progress further. Maybe space travel is not getting any better in the same
way as Moores law has stopped applying to increasing computer speeds
which are no longer doubling every 18 months.
Rocket propulsion technology progression has may have flatlined in
the same way as steam powered locomotive technology flatlined in the 1900's.
Assuming this is not the case I present the following proposal.

\section{Going to Mars, the future of space travel}
\paragraph
\noindent
Space Travel \& Aviation is where we aren't keeping up
with science fiction \& most definitely not improved much
in the last 40 years.
Everybody thinks going to Mars \& back is much harder than going to the Moon.
There is one critical difference which makes it in some ways easier, Mars
has an atmosphere, jet engines will work there.
The downside is that the gravity on Mars is higher than the Moon's
the Moons gravity is about 16\% of Earth's, Martian
gravity is around 38\% that of Earths \& its escape velocity is
about 45\% that of Earth's at 11250 miles an hour.
The little Eagle Module was
enough to get off the Moon probably a 2 stage rocket
would be needed to get off Mars, this would be nearly
impossible to land on Mars \& this kind of payload
would require something larger than a Saturn V to
carry it to Mars \& it probably is impossible
to make using liquid propulsion.  
\paragraph
\noindent
Feynman first introduced the Rodger Ramjet idea of using an atomic powered
jet plane high in the Earth's atmosphere where it is very thin
to reach escape velocity \& slingshot to the planets.
Atomic rockets are not new, during the Rover/NERVA 
(Nuclear Engine for Rocket Vehicle Application ) nuclear
rocket programs from 1955 until the program was stopped in 1973 a total
of 20 rocket reactors were built \& tested underground.
Currently the best chemical scramjets like NASA's X-43A Scramjet
\url{http://www.nasa.gov/missions/research/x43_schedule.html}
can do Mach 9.8, or 7,000MPH, this is already quite close
to Mars's escape velocity \& fly to about 110,000 feet.
To go to the planets by scramjet we need a craft that will reach Earths
escape velocity, around 25,000MPH, to do this I suggest a hybrid 
atomic scramjet/rocket engine. When the
engine starts going initially it is a rocket \& it gradually
changes from a rocket to a scramjet as it picks up speed,
for the remainder of the document I am going to use
the term scramjet to mean a rocket/scramjet hybrid.
The great thing about an atomic scramjet is that it has almost
no theoretical upper speed limit except for the speed of light 
( I researched this fact quite a lot ) \& design
limitations because it has to carry no propellant with it
while in jet mode.
The atomic jet idea was dumped because of it's environmental fallout
in the atmosphere not to mention in the crew compartment when it was
realized that atomic energy causes cancer.
Hopefully fear of environmental fallout 
will change when curing cancer will become easier in
the near future, see Cures for cancer topic below.
The radiation in the crew compartment is the greatest
risk of all, this can be minimized by
moving the crew compartment as far away from the radioactive
core as possible \& putting a ``shadow'' shield as near
as possible to the core which creates a radiation ``shadow''
around the crew compartment which prevents neutrons, gamma rays
\& other radiation from entering the crew compartment from the
reactor core, This shadow shield will add a lot of weight
to the craft putting the propellant tank in the way also
will reduce the radiation risk to the crew further.
Because it probably would be a huge lump of lead,
I personally hate the idea of a shadow shield
\& if anyone has a more innovative idea I am all ears.
Ideally the scramjet should be using fusion as this
is environmentally friendly but this probably will be
impossible for another 50 years.
\paragraph
\noindent
The ``Greenpeace friendly'' \& technically easier but more expensive
approach would be to use
a Saturn V to carry the atomic scramjet to Mars
( this of course is only environmentally cleaner if the Saturn V 
doesn't explode so for safety it would be best to choose some
remote desert like the Sahara ),
seeing as the atomic scramjet would now only have to work in Mars's
atmosphere \& not have to work in Earth's it would be easier to design.
If Greenpeace allows a halfway house \& allows the atomic
scramjet operate high in the earths atmosphere it could
be piggybacked up by either
the American U2 spy plane, a B52 or something bigger but similar to
scaled composites/Virgin Galactic's
Spaceship One launch vehicle provided it is powerful enough.
According to TM-1998-208834-REV1.pdf ( see below )
A small nuclear thermal rocket or NTR ( \& therefore a scramjet ) 
would only use up around 10g of
enriched U-235 to leave the Earths atmosphere at 25,000MPH, seeing that
an atomic bomb like the one that exploded in Hiroshima
used around 11Kg of enriched U-235, the amount of
fallout generated by an atomic scramjet would only be
less that 0.1\% of the fallout generated by an atomic
bomb. If the plane can only go at 25,000MPH it will 8 weeks to go to Mars,
anyone locked up in a tin can for this period of time would
go obviously go insane, therefore I believe the realistic speed/sanity
sweet spot is at 100,000MPH, obviously a lot of work needs
to be done on scramjets to achieve this goal.
Maybe submarine crew would be able
to shift this sweet spot a little as they would be used
to being locked up in a confined space.
Going at 100,000MPH would use
16 times more fuel or 160g of U-235 
in the Earths atmosphere because
\begin{math} 
Energy=Mass x Velocity^{2} 
\end{math}
of course a chemical rocket if it could go that fast
would also have to burn 16 times as much fuel, but I believe
it can't go that fast anyway.
\paragraph
\noindent
To take off in the Martian atmosphere would be more difficult
that Earth's because the atmospheric pressure is ~6.1MB
( about 1/150th that of Earth ).
This means a lot of speed would need to be picked up before
the scramjet in jet mode \& aerodynamics work.
Maybe aerodynamic surfaces like wings should be avoided altogether
on some crafts if the weight impact isn't offset by the usefulness of them.
I would suspect that the scramjet would need
to reach somewhere between 5,000 \& 15,000 miles
an hour before it can switch fully from rocket mode
to scramjet mode. Because the Martian atmosphere is so thin
an adjustable funnel which can open very wide at low
speeds might be useful so that the scramjet can
operate in jet mode at lower speeds.
The great thing about an atomic 
scramjet is it needs to carry no propellant except for the 
bit of propellant to operate start off while in rocket mode.
It should be easy to get a unmanned small manless scramjet 
Mars for initial testing, an average sized rocket should do.
\paragraph
\noindent
A very sensitive long range radar \& an autopilot with
the ability to make minute course adjustments
under computer control may be needed to avoid
space debris which would be lethal at such high speeds,
\paragraph
\noindent
I would like the ship to be made as much as possible from
one solid piece of material \& be flexible enough change shape naturally
as aerodynamic stresses are applied to it. 
I personally don't like things that vibrate
vibrations typically cause things to break, for moving parts I like
things that go round \& round like turbines, they don't break much.
\paragraph
\noindent
For manless space probes hopefully no or not much of a shadow shield will be
needed provided the electronics are fault tolerant to radiation.
This opens the possibility of a space probe going to Mars first,
then slingshotting inside the Martian atmosphere where the
environmentalists won't be giving out about fallout to a large
percentage of the speed of light \& heading off to Alpha
Centuari, this is possible with an atomic scramjet engine.
The difficult bit which I haven't figured out
is how to slow down the probe from the speed of light 
once it gets there if there are no planets with atmosphere's 
nearby of which
there are none around Alpha Centuari, The atomic core
could power a powerful radio transmitter which
would send back data to earth 4.31 years after arriving there.
If a probe cannot transmit receivable data over that
great distance maybe the scramjet plane could
get close enough into the edge of Alpha Centurai's atmosphere to
slingshot around the star \& return to the
solar system without burning up.
A test flight around the Sun could be done first
to check if the idea works.
\paragraph
\noindent
Videos of Alien abductions is the place to look for ideas for spaceships.
The more observant people will describe their experiences
accurately. An interesting concept from a video I watched
points the future for materials science, the materials
blended into each other without joints.
Anybody who watch ``Das boot'' knows that rivets pop
in World War II U-Boats at 250 meters \& glued Space
Shuttle heat shield tiles keep falling off not to mention O rings
which caused the 1984 Challenger space shuttle disaster,
Joints are from an engineering point of view are bad ideas.
\paragraph
\noindent
Dynamic blends of material need to be made, blending smoothly
into each other, I suggest making alloys/dynamic blends of
titanium, carbon fiber, plastic, glass, fiberglass \& the ceramics
in space shuttle heat shields.
\paragraph
\noindent
To prevent loss of life the initial prototypes will be radio
controlled \& I hope John Mc Carmac would be interested in
writing the autopilot software to land the spaceship on Mars.
Owing to fifteen minute delays caused by radio waves getting to Mars \& back
the distance from Earth would be too far to land by remote control 
I also would hope that Scaled Composites could be made interested. 
\paragraph
\noindent
More propellant can be accumulated in the propellant tank
while flying by taking in some from the air intake of the
scramjet before leaving the atmosphere or else if this is impossible
fill the scramjet with propellant while on the ground,
if travelling fast enough there may be enough gas in the vacuum
of space to keep the scramjet going in jet mode at
least some of the time, I've read that there is only
1 atom per cubic centimeter in interstellar space, this
isn't going to be much good to us, hopefully there is
more in the solar system.
\paragraph
\noindent
If some of the scramjet is made in Russia
maybe the Uranium 235 or Plutonium in some of the decommissioned
nuclear warheads can be used as fuel for the scramjets.
A parachute would make a good airbrake I would suggest
making the parachute in the scramjet
plane out of a strong metal capable of standing high
temperatures \& possibly with hinges
so it naturally packs away neatly,
but maybe a metal fabric is better.
An alternate method of braking in space would
be to turn the plane around 180 degrees \& fire
the rocket this could slow the ship down by
around 10,000 miles an hour but not more as the
rocket will run out of propellant,
this also cannot be done in the atmosphere
because the flames would be blown onto the
ship \& destroy it.
The ship I believe would need a protective magnetic 
field to prevent cosmic rays once we get outside
the Val Allen Belt.
\paragraph
\noindent
This is the end of my proposal, if it is possible
the trip to Mars should only cost only a tiny
fraction of the trip to the Moon.
My scramjet to Mars idea got a reality check from
Bryan an atomic rocket scientist from NASA with whom
I had contact via email, I owe you a pint, thanks to Bryan I got to
my research into going to Mars further than I could have
ever done myself.
\paragraph
\noindent
Firstly the most interesting shootdowns of my ideas
by Bryan:\\
Using the scramjet to reach the stars \& even Mars.
If you fly at high speed (beyond orbital velocities) in an atmosphere, 
aircraft tend to melt, unless they use extreme measures for thermal 
protection.  The temperatures of the aircraft skin can reach amazing 
levels. :)  Hence we use ablative heat shield when spaceship return 
from the Moon, etc.  Those vehicles have with initial velocities entering 
the atmosphere of 25,000 MPH, and due to drag, they slow down quickly.
So, travelling at VERY high speed in the atmosphere, let alone the 
speed of light, is rather impractical.  :)  This is a BIG understatement.
\paragraph
\noindent
I have since found out that the Concorde at just Mach 2
heats up to 260 Fahrenheit ( hotter than boiling water ) \&
it also expands a couple of feet in length.
A doubling of speed at the same height
above sea level will cause a fourfold increase in temperature
in the hull of the craft, to avoid this as we pick up speed 
we will go higher.
Because the relative concentration of gases vary as
we go up in height doing an accurate calculation on
the density of gases a little involved e.g. hydrogen
is nearly as dense in the atmosphere at 80km as it
is on the Earth's surface while oxygen is practically
non existent at 80km. 
Using Boltzmann's law \& simplifying greatly by assuming 
the atmosphere is pure oxygen, for every 20km in height we go up
we get about a fourfold decrease in the density of oxygen.
So ideally we would need to gain around 20km in height 
for every doubling in speed so that only quarter of the amount
of gas will be hitting the planes hull \& so equalizing
the quadrupling in heat at the same height.
How high the scramjet can go \& keep increasing in speed
will dictate the feasibility of going to Mars.
Nerds, here are the topics Bryan recommends you study to get
around these limitations: Hypersonic Aerodynamics,High Speed Gas Dynamics 
\& Reentry Flow Physics.
\paragraph
\noindent
Here is Bryan's second shootdown.
We cannot get humans to Mars or to the nearest star with existing technology.
The NTR work will require many years of development.
I personally am not too interested in an nuclear thermal rockets 
I want an atomic scramjet.
\paragraph
\noindent
Here is Bryan's third shootdown which to me from my reading 
going to Mars is possible by scramjet if:\\
1) The plane could reach escape velocity without burning up,
hopefully some aerodynamics genius can figure out this problem,
it's a biggie unless we can get the plane to
operate efficiently very high in the atmosphere.\\
2) Can be made to operate in both atmospheres \& equipment on the
plane needed to scoop up the propellant \& store it in a compact form
could be made, this doesn't sound impossible to me.\\\\
3) The shadow shield can be made a realistic weight.\\\\
Your suggested ideas really need a LOT more refinement...  The ramjet 
idea will fly in the atmosphere of Earth or Mars, but you still need to have 
propellants to get to Mars, and that is a LOT of propellant....  Please 
see the papers on NTR for a general idea...\\\\
Scooping all of that propellant out of the atmosphere and processing it 
into something usable for the interplanetary flight requires a pretty 
massive and complex system...\\\\
It is much simpler using a "traditional" NTR.\\\\
Below are similar NASA proposals Bryan pointed me at.
They are detailed \& interesting.\\\\
Proposal Title Exploration of Jovian Atmosphere Using Nuclear Ramjet Flyer\\
Principal Investigator Maise, George\\
\url{http://www.niac.usra.edu/studies/study.jsp?id=510&cpnum=00-01&}\\
\url{phase=II&last=Maise&first=George&middle=&title=Exploration%20o}\\
\url{f%20Jovian%20Atmosphere%20Using%20Nuclear%20Ramjet%20Flyer&org}\\
\url{anization=Plus%20Ultra%20Technologies,%20Inc.&begin_date=2001-}\\
\url{03-01%2000:00:00.0&end_date=2003-01-31%2000:00:00.0}\\\\
The Mars nuclear airplane is discussed here:\\
Principal Investigator Powell, James\\
\url{http://www.niac.usra.edu/studies/study.jsp?id=424&cpnum=99-03&}\\
\url{phase=I&last=Powell&first=James&middle=&title=Development%20of}\\
\url{%20Self-Sustaining%20Mars%20Colonies%20Utilizing%20the%20North}\\
\url{%20Polar%20Cap%20and%20the%20Martian%20Atmosphere&organization}\\
\url{=Plus%20Ultra%20Technologies,%20Inc.&begin_date=2000-05-01%200}\\
\url{0:00:00.0&end_date=2000-10-31%2000:00:00.0}\\\\
These two links can be got to by going to
\url{http://www.niac.usra.edu} \& searching using the authors name.
Vehicle and Mission Design Options for the Human Exploration of Mars/Phobos\\
Using "Bimodal" NTR and LANTR Propulsion\\
AUTHOR(S): Stanley K. Borowski, Leonard A. Dudzinski, and Melissa L. McGuire\\
\url{http://gltrs.grc.nasa.gov/reports/2002/TM-1998-208834-REV1.pdf}\\\\
High Power Nuclear Electric Propulsion (NEP) for Cargo and Propellant Transfer Missions in Cislunar Space\\
AUTHOR(S)Robert D. Falck and Stanley K. Borowski\\
\url{http://gltrs.grc.nasa.gov/reports/2003/TM-2003-212227.pdf}
Here is Buzz Aldrin's roadmap to Mars\\
\url{http://www.popularmechanics.com/science/space/2076326.html}
\paragraph
\noindent
Below are some links to project Daedalus 
A 50,000 ton interstellar vehicle that is built in orbit about Jupiter, 
and fueled from it's atmosphere.\\\\
\url{http://www.daviddarling.info/encyclopedia/D/Daedalus.html}\\\\
\url{http://www.geocities.com/TelevisionCity/2049/DAEDALUS.HTM}\\\\
\paragraph
\noindent
Here is Bryan's reply with respect to how
big a shadow shield needs to be.\\
The NTR papers discuss the mass of the shield for human crews. :)  It 
is about the same for robotic missions.  Robotic missions still need 
shielding to protect the science instruments and other subsystems 
and the shield prevents the instruments from picking up radiation 
created by the spacecraft that might interfere with sensitive
measurements in outer space.\\\\
Shield mass scaling.\\
\url{http://www.fas.org/nuke/space/c07sei_2.htm}
\paragraph
\noindent
The reason the space race to the Moon happened was 
that John F. Kennedy suggested it \&
he had the clout to throw tons of money at the idea
national pride, fear of them damn commies \& space supremacy 
got involved to generate the space race,
However I assume he never would have set such a bold goal without
talking to a few rocket scientists who told him it was a realistic goal,
then again maybe he was a prize bs artist who got away with it.
The reply I received from Virgin Galactic about going to Mars is below.\\\\
Subject: RE: Any interest in going to Mars?\\
Date: Mon, 21 Nov 2005 17:11:03 -0000\\
From:virgingalactic@virgin.com\\
Dear DJ\\\\
Thanks for your email.\\\\
We're still at the early stages of the project and very much focusing
all of our resources on getting it off the ground, so at this stage Mars
is a long way off.\\\\
Thanks so much for thinking of us and who knows, one day ...\\\\
Kind regards\\\\
The Team\\
Virgin Galactic\\\\
\paragraph
\noindent
By the time Virgin Galactic starts operating commercially
it will be 50 years since the first man Yuri Gagarin went into space
\& they won't even be going as high. They certainly
are not boldly going where no man has gone before
even commercially, they are doing nothing new except
making a hop to the edge of space relatively cheap,
or a very expensive rollercoaster ride which accomplishes
nothing whatever way you look at it, a weather balloon
can go nearly as high.
Richard Branson, Burt Rutan \& the rest of the Virgin
Galactic team should dream harder \& try to live up to
their name. A private company that is dreaming harder
is Blue Origin \url{www.blueorigin.com} which wants
to put space stations in orbit, Jeff Bezos the
owner of Amazon the online bookstore is the main
man behind it \& they are looking for people
\url{jobs@blueorigin.com}. 
\paragraph
\noindent
From reading Bryan's expert reply I think that getting to
Mars by scramjet or something else is possible in a 3 to 5 years 
if we put our mind to it \& the environmentalists don't kick up
, if it was a wartime situation it could be done even quicker,
nothing progresses technologies like war, one of it's very few benefits.
I personally would like to see a leg of Live Aid 2 held on Mars,
it would be a ``one great leap for Mankind'' cultural event.
I personally suggest that you email \url{virgingalactic@virgin.com}
\& sweetalk them until Richard Branson, Burt Rutan \& the
others start listening to give serious consideration about going to
Mars using my suggestions \& the better researched suggestions in the 
the proposals provided by NASA \& others to make this happen.
Exploration of space needs to continue \& it might
be necessary for private enterprise to take over
from government agencies. There are a lot of
small private enterprise companies trying
for space they need to start working together if 
they plan to accomplish anything serious.
\paragraph
\noindent
Rockets have their limitations, the alternative of riding
the shockwaves created by small atomic explosions as put forward 
in Project Daedalus \& Project Orion is technically awkward \&
to me has suggests that ``if the only tool you have is a hammer
everything looks like a nail''
The only clean quantum leap that I can see in the distant future
in terms of technology if it exists \& proves suitable is
to harness dark energy, even scientists don't really know
what it is so my ideas here are pure conjecture.
Dark energy is the hypothetical energy source
with anti gravity characteristics which is believed to be causing the
expansion of the Universe. This I suspect would be very hard
to extract from the Universe so a means to manufacture it
would probably need to be devised.
Dark matter would compliment rocket propulsion not replace
it, hopefully it would reduce a ships inertial mass
as well as it's gravitational mass making the ship
easier to accelerate.
\paragraph
\noindent
If the Russians were enterprising enough to take a space tourist
up they will gladly go with this project if they get funding.
Other people who would be able to help make Live Aid 2 from Mars
a reality, Bob Geldof, Bono, Eddie Jordan handling Advertising,
Michael O' Leary handling Financing.  

\section{Space elevators}
\paragraph
\noindent
A space elevator is an elevator whose cable
is in geostationary orbit around the planet
when it is built which may be as soon as 25 years
time it will be a cheap way of launching objects into space.
Obviously there are some severe technical hurdles
to overcome like making the cable strong enough,
carbon nanotubes are one possibility.
What happens if some small fast moving projectile
in outer space collides with the cable of the
space elevator ?, here is my suggestion.
Make the elevator cable flexible \& put small retrorockets
every kilometer on them to move the cables out of
the way if some space debris is on a collision course
with them.
I think the space elevator would only be good for launching
probes \& satellites nobody wants a 22,000 mile
trip on a ``Greyhound bus'' going at 60 miles an
hour, is it really possible to make a space
elevator go much faster than this?, I'd suspect
Arthur C. Clarke wants the elevators to do
around 2000 miles an hour.
The space elevator also should have 2 tracks 1 up
1 down \& the carriages switch over on the
track when they go to the top or the bottom,
this would allow loads of carriages to
go up \& down simultaneously.

\section{Matter antimatter energy}
If you think Nuclear Energy is powerful,
compared to matter antimatter energy it
is very inefficient. Matter antimatter energy
makes 100\% efficent use of Einstiens
\begin{math} 
E=mc^{2} 
\end{math}
equation.
At present it is very difficult to get
ones hands on antimatter because it reacts
instantaneously with matter; we can only
generate about few thousand atomic sized antimatter particles
at a time in Particle accelerators like the
ones in CERN at the Swiss French Border.
We would need to go to a very special place
in the Universe to find this stuff existing 
in abundance.
An antimatter bomb would have 0Kg critical mass,
it would probably be undetectable, no radiation.

\section{Making an atomic bomb}
This is very difficult to do even if you can
get your hands on 11kg of Uranium (it's critical mass).
The difficult bit is as you try to push 11kg of
Uranium together it tries to blow apart as it is
beginning to explode.
The most likely weapon a terrorist would try to
make is a dirty bomb, a normal bomb wrapped
in a dirty radioactive material which the blows
the radioactive material over an area.

\section{SNAP batteries}
I did a bit of research to find out why they still use
heavy primitive technologies like lead acid batteries 
in electric cars \& those awful over complications of 
hybrid cars like the Toyota Prius. Why not SNAP
( Space Nuclear Auxiliary Power ) batteries.
These are atomic batteries typically used to power satellites,
they work by converting the heat generated when a radioactive
substance decays into heat.
They are so safe they can even be used in heart pacemakers.
They can generate 30 Watts per KG this means the battery
for a 10 horsepower car would be 250Kg,  damn I thought
it would be much better than that, it's nearly
is as bad as a lead acid battery but I've got an idea,
you only need a lot of power when going up a hill
or accelerating this is at most only for a few minutes,
1 horsepower is quite adequate most of the time,
this reduces the battery weight to 25Kg \&
the SNAP battery can charge up a high wattage lithium
ion battery or a capacitor for when extra power is needed.
The main advantage of SNAP batteries lasts 
around 150 years before it got half discharged.
Also Plutonium 238 need to make the batteries 
costs around \$700 a gram... expensive.
To make an ideal SNAP battery for high power usage
we need a source of alpha particles with a shorter 
half life than 150 years which doesn't decay into
anything too dirty  ( 10 years is my idea of an ideal
figure, longer if this generates too much heat ).
The hard part is if it's half
life if its only 10 years it will be very rare naturally so
it will need to be made artificially, in a nuclear reactor possibly
\& ideally can be made cheaply which it probably can't.

\section{Walking on water}
It should be possible to walk on water like Jesus
did or more precisely run on water. Lizards do
it all the time. All thats needed is some
fluid dynamics engineer to design flippers 
to do this feat, I suspect it will be the biggest
fad since the Rubik cube.

\section{Opencyc \& the future of robotics}
\paragraph
\noindent
This is a project to give computers common sense
\url{http://www.opencyc.org} in my opinion this project
shouldn't be using plain English. It should be
using a hybrid language based on
Latin ( an old very ``mathematical'' language )
\& Esperanto ( it takes two hours to learn the grammar ),
to enhance understanding no words should have multiple
meanings, nothing irregular or special cases
\& all words should sound different to
enhance speech recognition. Also
objects should be described physically \& unambiguously.
Having a unambiguous language will mean Politicians
can no longer twist words \& corny jokes will
be eradicated from the face of the Earth.
\paragraph
\noindent
Opencyc should also be programmed with a knowledge
of physics \& chemistry \& able to simulate real life events
in software so it can make more intelligent
judgments than people, it should know various things
like the periodic table of elements,
formulae for the boiling points of various
substances at various pressures, melting points,
half lifes of radioactive substances \& how they
decay all the way down to less important statistics
like the watts generated per KG of various radioactive elements.
If you think this is hard have a look at various
maths packages like Derive from Texas Instruments
\& Mathematica these are better at Maths than most of
the Mathematicians I know though they wouldn't like
to admit it. I think that Opencyc
will never make it to having full common sense \& probably
will be a perpetual work in progress. 
\paragraph
\noindent
I think it would be much better off as a tracked robot,
I hate robots that walk, it is human egomania \&
vanity that nature is able to do better control
engineering balancing an unstable object than engineers,
people also have the advantage of common sense so they
know when they have to be careful,
the only reason we got legs instead of tracks is that you can't
grow skin over tracks.
\paragraph
\noindent
Robots will at least not in the near future be
able to negotiate in the real world using image processing
alone. Humans can do it because of familiarity with
objects \& common sense, robots at the moment should be considered
in the same league as 8 month old children when
it comes common sense \& getting around.
Robots will need all the help they can get,
using normal or a ultrasonic radar as well as 
image processing will help.
It also would be useful if a mechanism for detecting
the difference between solid \& liquids could be
devised so that accidents like going into water
\& sinking can be avoided, maybe the robot should
be made amphibious too so that this is less of a problem.
Detailed maps of places where the robot is allowed
to visit including hazards should be given to
the robot as a 3D vector map, the robot can be
tought to recognize objects like chairs
which can be moved so the robot can cope with
small changes in its environment.
Nature designs creatures so that they themselves survive
\& the species themselves survive, eyes
are optimized to see light of wavelengths
most useful to the creature which has them.
The robot's design has to be such that it survives,
it should be easily upgradeable \& repairable.
It should also be able to back up all that it
has learned \& be able to download it to new robots.
Everything the robot learns well should be kept
in a single archive so that the most useful software
can be downloaded to new robots, this is equivalent
to humans going to school except much faster.
\paragraph
\noindent
Highly directional microphones will help
improve speech recognition in noisy environments.
\paragraph
\noindent
Owing to having a more hard wired brain Animals have 
a severe head start on us at a conscious
level when they are born, it is called instinct,
humans catch up when they reach about two years old.
This suggests to me in the long run the robot
would be expected to learn more than is programmed
into it if it is to become competitive with a human
when it comes to intelligence.  
\paragraph
\noindent
Has Opencyc tried Turing test to see if it behaves
lifelike? 
What would neural nets be most useful for in the Opencyc robot?
\paragraph
\noindent
Interoperability between modules ( i.e. speech recognition, speech
generation, Opencyc, Mathematica, derive
image processing ) is very important
I don't like Corba but it is necessary to hitch up
the all these software packages.
\paragraph
\noindent
Wisdoms from writing Opencyc should be
written down in a book, what you did
right what you did wrong, what are opencyc's weaknesses \& why
\& distributed like my book so the next generation attempt
can be started by some other enthusiastic lot.
\paragraph
\noindent
How about GPS based route planning software
be used so it can travel independently
between different places.
When Galileo the European alternative
of GPS comes into operation the robot
will be able to locate itself to the
nearest centimeter, this will make
travelling around for the robot much
easier even in constrained areas,
it would even be able to travel on a
road or a footpath blind provided
no obstacles are moved into it's path.
I suspect GPS will be forced to
become more accurate owing to
competition from Galileo.
\paragraph
\noindent
A CD/DVD jukebox would be a good idea.
There are a few good Japanese developers
making robots that try to mimic
humans a bit too much, get the ones
doing potentially useful things.
The robot I am considering
doesn't have a smiley or surprised face
yet \& if it does it is only
software that renders on a computer
monitor when absolutely needed,
this screen will be of a lot of use
for other things too a picture
can tell 1000 words.
\paragraph
\noindent
The machine will be able to run
For the moment Linux,MacOSX \& Windows simultaneously
probably have 3 processors.
I want every bit of useful best of breed software
on the planet able to run on it \& all the programmers
on the project can play to their strengths rather than 
having to learn a new operating system.
\paragraph
\noindent
Theorem provers will be useful,
so will wifi, Ethernet \& dial up phone jacks.
The computer will have full email \& web access,
any question the operator asks that the computer 
doesn't know the answers for the Opencyc robot
will put a reward chosen by the person asking the question
on google answers for it \& have its own credit card \& paypal account.
\paragraph
\noindent
There is an interesting piece of software called Alice.
\url{http://www.alicebot.org} which
is a piece of software which makes
humanlike smalltalk, this may be useful
to give Opencyc a personality.
\paragraph
\noindent

A robot in my opinion will never gain understanding
however computer proofs are becoming 
I also believe humans can make very few discoveries
completely independently of other humans. Even Einstein
based his work on that of Planck, Maxwell \& Lorentz.
Bohr also acted as a devils advocate for him.
Computers gradually will help scientists make
new discoveries \& should be credited for them.
\paragraph
\noindent
Opencyc should use the babelfish language translation
engine or similar including webpage translation
\& a new simplified English,Esperanto,Latin which will
be Opencyc's native tongue. We will get
MS Words Grammar Engine developer \& tap
him for his wisdoms on language development
also the developers of babelfish for advise
on simplified English.
Web access from www.weather.com \& map24.com
will be useful.
Facial Recognition \& face emotion 
\& body language recognition software
will also be important so the
software can work out if something is wrong
with people.
My project fundamental should also
be part of Opencyc.

\section{The tower of Babel}
The proliferation of languages overcomplicated everything  \&
held up the development of science
from the Greek heydays around 500BC till the
medieval ages \& the printing press got going.
The Greek philosophers, scientists \& mathematicians all had it easy 
they all just spoke... Greek, they had to waste no time \& energy
learning extra languages. Another serious
setback which stopped progress in science was the burning of the library
in Alexandria around 700AD, this probably removed
half the body of knowledge in the world at the time,
as any good computer engineer knows always make backups.
The poor philosophers, scientists \& mathematicians in
the medieval days needed around 5 languages, the poor
philosopher, scientist or mathematician who had no aptitude
for languages could get nowhere as he couldn't
understand the books. I personally despite having an
electronics degree find modern mathematical
documentation hieroglyphic \& nearly impossible to understand,
has anybody ever thought of doing away with some of it.
Or at least do two versions of every book one concise one
for people who can deal with mathematic hieroglyphs one
for people who can't or else somebody invest some energy
to make maths easier for people with problems with languages.
\paragraph
\noindent 
People interested in science \& mathematics should have the option of opting
out of learning languages beyond internationally agreed basics \& people 
interested in Culture should have the option of
opting out of Science \& Mathematics except for the basics.
Why do school curriculums insist on ramming stuff down students throats
that they have no interest in?, let the kids do what they want.
If everybody in the world learned this simple Latin/Esperanto
hybrid language we could all communicate with each other \& with 
the Opencyc robot machine.

\section{Is Maths beautiful enough as it is?}
Maths is beautiful enough, I like
hypotheses, they are right most of the
time \& this is good enough,
they should be put into Mathematics software
\& checks put in so they can be automatically
dealt with when they go wrong. Physics
\& programmers have been dealing with
an inexact science for years mathematicians
should do likewise.
Godel's undecidability theorem basically states that
not all things true in mathematics can
be proved using mathematics,
it is like a bishop on a chessboard not being
able to get to all the squares.
Hypotheses which have passed the
test of time \& not been proven
false have to be assumed as more
or less correct, stop wasting
time \& start going with them
mathematicians.
\paragraph
\noindent
The Andrew Wiles who cracked Fermat's last
theorem wasted
a lot of time on something that
everybody in their right mind knew
was true for 500 years. If he didn't
invent new maths for his efforts
they would have been wasted.

\section{Nanotechnology}
Nanotechnology is Biology, God invented it
billions of years ago, stop reinventing the wheel,
Integrated circuits aside Richard Feynman made a
blooper on his ``visionary speech'' when he started this ball rolling.

\section{Cures for cancer}
Some cancers can be cured by a virus, see
\url{http://www.oncolyticsbio}\\
\url{tech.com} for more info,
research on this has been ongoing since 1998 so it is
hard to know if it will ever replace chemotherapy fully
but I hope so.
Surely this is the way to go as opposed to chemotherapy.
How about some preventative medicine imagine if children
were immunized against cancer before they got it or
even having the virus put into the foodchain atomic
power would become quite safe.
Radiation causes more damage than just cancer the question I ask is this
damage acceptable. It would also be worth
researchers while to figure out why the animals
living near Chernobyl are surviving \& make use of
the information.

\section{The future of dentistry}
I hate Dentists that pull teeth they are only
trying to make you ugly, however getting your
teeth cleaned by a dentist is great.
Stem cell research is going places
In two years time approximately you will be able
to get teeth grown from stem cells which
are implanted in your gums, see
\url{http://news.bbc.co.uk/2/hi/health/3679313.stm}
\url{http://www.odontis.co.uk/} for more info.

\section{Liquid breathing}
Did you know that in some cases it is possible
to breathe liquids without drowning?
Newborn puppies can survive 54 minutes underwater
while newborn rats can survive 40 minutes without
ill effects. Petroflurochemicals (PFC's)
can support fully grown mice \& has been
even used to treat human patient suffering from
acute respiratory distress syndrome (ARDS).
Surely more uses can be found for this technology.
For more info have a look at the following websites.
\url{http://www.crabbsac.org.uk/articles/A001.htm} \&
\url{http://www.ahsc.arizona.edu/opa/horizons/2000/fall/pg10.htm}

\section{Environmental issues}
If dumping is tidied up German style,
landfills each specializing in one type of substance
are the mines of the future, specialized dumps
can be made environmentally friendly because
there are only a few risks associated with
each substance which can be overcome properly.
An international web based freely accessible archive needs to be kept of 
what is dumped where \& needs to be kept for future generations.
Even the depleted nuclear waste from nuclear reactors like Sellafield
kept under the Irish Sea may be of use to someone
creative enough even now.
\paragraph
\noindent
Most Environmentalists think wave energy being completely safe 
\& environmentally friendly, however, as pointed out on 
slashdot recently this takes potential energy from the Moon which
will eventually collide with Earth which might happen before the
Sun runs out of fuel. I personally feel that environmentalists
should go away \& study science to at least the same degree 
as the scientists who they frequently rally against
so they can at least argue their case intelligently,
they are frequently overly conservative
\& don't trust the ability of the scientists who are 
trying their best to make a better world for everyone.
Environmentalists, everybody fears the dark, if you
are scared of the dark, what scientists are doing,
learn what they are actually doing, get enlightened.
\paragraph
\noindent
I personally am not into the prevention of rare species 
going extinct, I believe in survival of the fittest \& see no
problem as new species will come into existence to
take the place of the old species that go extinct,
its called evolution.
An interesting argument made to me is that we humans are responsible
for species going extinct as a result it is our responsibility
to try to keep at least some of them alive, I personally still
am not a conservationist at heart.

\section{Getting rid of nuclear waste}
Stop dropping nuclear waste at the bottom of the sea,
why not drop it into volcanoes?,
Nuclear waste is much denser than lava or magma
\& should sink to the centre of the earth where
it is completely safe.
I came across this idea in the BBC's Focus magazine of October 2005.
But it was pointed out that this idea is dangerous.
Who are they fooling?, what happens in 10,000 years
when the cases no holding nuclear deposits at the bottom
of the sea erode.
I think the idea hasn't been tested \& what
we are dealing with here is fear of the unknown \&
like fear of the dark should be overcome by
people in power to make these decisions.
If people don't want to live near a volcano which
is being used as a nuclear waste dump why are
you living near a volcano in the first case,
you are defying God anyway by never expecting the thing
to blow, move to a safer place, live away from volcanoes.
Likewise people who live near any other potential disaster zone
wise up \& stop defying God, he really doesn't want you living there.
Mother Nature doesn't like being fought against \& usually wins.
Biodegradable plastic bags are terrible they fall to millions of bits
if you use them to hold stuff in them for a few years \& 
the mess they make needs to be vacuumed up,
to be environmentally friendly things need
to be made of high quality \& as reusable as possible not
the other way around. I would suspect however as soon
as we finished dumping most of the nuclear waste into
volcanoes we will find a very important use for it.

\section{Can science explain everything?}
I honestly believe it can't, but here are a few attempts
to explain things scientifically which get swept under 
the carpet of science or dismissed completely by it as quackery
because it usually fails when tested scientifically,
maybe God just makes some things that way.
God may be as much behind the illogical as well
as the logical, if the World isn't logical then
science is lost. God could have made the Universe
obey any laws of physics he liked, he just allowed 
Galileo, Newton, Einstein \& Feynman to be nearly right
with their guesses about how the Universe really is at the moment.
\paragraph
\noindent
Science can only explain things to a certain level, to
every question you will always end up at a cul de sac if
you keep asking why, let me give you an example.\\
Interrogator: Why did the woman fall on the ice?\\
Scientist: because it was slippy?\\
Interrogator: Why was it slippy?
Scientist: Because near zero celsius when ice
is compressed the top layer turns to water.
After one or two more questions like this the
scientist will run out of answers.
\paragraph
\noindent
Science is currently looking for a ``Theory Of Everything'',
a single law which will explain the four fundamental forces,
weak, strong, electromagnetic, gravitation. Consciousness
is a fundamental part of quantum physics \& the Universe,
in my opinion a Theory Of Everything is incomplete unless
it explains consciousness.

\subsection{My theory of how a bioenergy healing trick works}
A friend of mine has an aunt who did some hocus pocus
on him which gave him an almercyful pain in his stomach.
My guess on how this works is the following.
She charged up with static electricity by rubbing her feet on
the floor. After doing this for a while she generated
a few low frequency photons, an electromagnetic shockwave
by pushing her hands quickly forward.
This hit nerves on his skin near his stomach giving
him an electric shock.

\subsection{My theory of how water divining works}
My brother James successfully did some water divining
using a welding rod for a broken water mains.
This I guess worked by dipoles in the water molecules
being aligned \& spiralling outwards at the leak,
the copper pipe acted as a electromagnetic shield preventing
water inside the pipe generating a magnetic field.
The leak spiralling thus acted as a electromagnet attracting the
welding rod with the magnetic field.
Water spiralling inside a pipe which isn't shielded
should be detectable, I cannot explain 
how water divining works with a rod made of
wooden as this isn't attracted to magnetic fields.

\subsection{Psychics}
\paragraph
\noindent
A psychic predicted to my mother that my grandmother
would die within a year, I sincerely hope this
wasn't a self fulfilling prophesy \& my mother
didn't tell my grandmother to scare her into
having reduced resistance to cancer \& giving
up on life too easily.
\paragraph
\noindent
Unfortunately most psychics are charlatans or
people suffering from delusions about their powers.
People go to them to be reassured that their
future is rosy, they are selling hope.
\paragraph
\noindent
God I suspect doesn't let psychics perform under the
pressure of scientific skeptics, he wants
people to have faith, God only gives psychic
talents to modest people who don't blowhole about
it \& not to publicity seekers, most psychics
can't tell their own fortunes.
Uri Geller bends spoons which have metal fatigue
from being strained before he goes on stage or similar
with his fingers ( it's miraculous sure Uri ),
he starts watches for a few percent of people 
who phone up whatever
T.V. talkshow he is on by peoples hands heating up old dried up oil
in the watches clockwork mechanism, this makes the oil less viscous 
\& the watches start going again temporarily.
Uri is popular because he is a handsome likable guy \& a celebrity
that annoys everybody, I believe he is a fake \& bs artist,
he just makes talkshows interesting, even I like him.
\paragraph
\noindent
One time when testing my own
psychic ability I correctly guessed Barry \& Jack's
birthdays, I had approximately a 1 in 365x365
chance of doing this, however it
is possible that Barry was bs'ing me that I
got his \& Jack's birthday correct, Barry may
possibly have told me his birthday previously \& my
subconscious recalled it, but I think this is unlikely.

\chapter{The nerds Bookshelf \& web bookmarks}
\paragraph
\noindent
Feynman's Lectures on physics,
These were published in 1965 \& are the physics
books that will be used in the leaving cert in Ireland, high school in the US,
A levels in England when Star Trek is a reality.
Hopefully people in charge of school curriculum will take my advise
\& make this a reality now, they should be used when the students
are 14 till they are 19 as a subject taught an hour a day
they take about 3 years to learn in school.
I was 30 when I discovered these books,
if I discovered them at 10 I would have been a child prodigy,
the value of them cannot be overestimated.
Feynman's books were so good because he was unselfish
with his knowledge \& made sure that he wasn't trying to
baffle anyone with BS.
You can buy them at
\url{http://www.amazon.com}
For anecdotes about Feynman goto
\url{http://www.google.com}
\& search for the Feynman Webring.
\paragraph
\noindent
The art of computer programming by Donald Knuth
Classics if you want to learn to write computer programs
again
\url{http://www.amazon.com}
\paragraph
\noindent
For operating system design read
Operating Systems Design and Implementation by Andrew S Tanenbaum
this is where Linus Torvalds got his
initial ideas for Linux.
\paragraph
\noindent
Q is for quantum an excellent book by John Gribbin
\paragraph
\noindent
Introducing quantum Theory by J.P Mc Evoy \& Oscar Zarate
A good guide to the history \& development of quantum physics
\paragraph
\noindent
Asimov's guide to science by Issac Asimov
Gentle introduction to science with a very extensive introduction
to biology, Asimov's specialty.
\paragraph
\noindent
Quantum Physics by Stephen Gasiorwicz, hot Feynman style book .
\paragraph
\noindent
A Unified Grand Tour of Theoretical Physics by Ian D. Lawrie
just a tiny bit beyond me at the moment.
\paragraph
\noindent
Quantum Field Theory by Aron Zee
only for geniuses at mathematics like Dirac
it's away beyond me at the moment,
prerequisites knowledge of Hilbert Spaces,
Lagrangian's \& Hamiltonians.
\paragraph
\noindent
Chemistry for Today published by Folens is good.
\paragraph
\noindent
Guide to LATEX by Helmut Kopka \& Patrick W. Daly
useful book for typesetting \& writing your own
book on a computer.
\paragraph
\noindent
Control Engineering by W.Bolton good for everything
from a rocket scientist to an electronics engineer.
\paragraph
\noindent
Books by John D. Barrow my distant cousin
Theories of Everything \& The constants of physics.
\paragraph
\noindent
The Selfish Gene by Richard Dawkins 
excellent book which give insights
to why creatures behave they way they do in order
that their genes survive.
\paragraph
\noindent
Politics:
\paragraph
\noindent
Stupid white men by Michael Moore entertaining book
about how messed up America really is especially
since Bush became president.
\paragraph
\noindent
The new rulers of the world by John Pilgner
An insightful book about the problems in Iraq, globalization
\& the little spoken about problems of racism against the
aborigine people in Australia. 
\paragraph
\noindent
Books on power:
\paragraph
\noindent
The Art of War by Tsun Tsu,
The Art of the Advantage 36 Strategies to Seize the Competitive Edge
by Kaihan Krippendorf,
The 48 Laws of Power by Robert Greene \& Joost Eleffers,
The Art of Seduction by Robert Greene.
\paragraph
\noindent
Book on success by being content with what you have:
\paragraph
\noindent
Awareness by Anthony De Mello
It covers topics like brainwashing towards craving the American dream
\& how to overcome desires like this.
It also encourages complete independence from other people \&
not to care what other people think,
this advise is correct for some people but as my cousin pointed out
it justifies selfishness \& my cousin knows people have turned into bigger
assholes after reading this book, one mans meat is another
mans poison, all the advise in the book is not for everyone.
\paragraph
\noindent 
Magazines:
\paragraph
\noindent
Homes Worldwide the definitive guide to buying homes abroad.
It has a very useful section at the end which provides legal info
to buying a house in each country \& websites to check.
\paragraph
\noindent
Focus Magazine, slashdot on paper very good.
\paragraph
\noindent
Scientific American \& Nature.
\paragraph
\noindent
Dr. Dobbs Journal, The best all rounder for programmers.
\paragraph
\noindent
Websites:
\paragraph
\noindent
\url{http://www.av.com} click on translate
for your Universal translator.
This can translate the online copy Stuttgarter Zeitung newspaper
to English for me.
\paragraph
\noindent
\url{http://www.suse.com} install Linux on your PC
Stop wasting money on Microsoft Products.
Alternatively run GPL Software on your Windows using
Cygwin.
\paragraph
\noindent
\url{http://www.slashdot.org} News for nerds.
\paragraph
\noindent
\url{http://www.darwinawards.com} if you like this book you'll love this,
it explores some of the stupid side of human nature.
\paragraph
\noindent
\url{http://www.theregister.co.uk}
Biting the hands that feed IT.
\paragraph
\noindent
\url{http://www.freshmeat.net} Interesting free software
\paragraph
\noindent
\url{http://www.lwn.net} For Linux news.
\paragraph
\noindent
\url{http://www.dilbert.com} nerds comedy
\paragraph
\noindent
\url{http://www.paulgraham.com/nerds.html} Paul Graham's views
why nerds are unpopular, everybody is jealous of their brains?
\paragraph
\noindent
\url{http://www.pbs.org/nerds/} Robert X. Cringely's website
author of Triumph of the nerds \& Accidental Empires
\paragraph
\noindent
For more interesting links go to
\url{http:/www.ariasoft.ie/bookmarks.html}
\chapter{Projects}
My software \& hardware projects are available on my website at
\url{http://www.ariasoft.ie/gplcontributions.html}
there are projects there which should be
of interest to people trying to crack RSA \& people 
with an interest in electronics.
I will only waste space in this book on my
most special project Fundamental.
\section{Fundamental}
God is the ``best programmer in the business'' he his masterpiece
being the human brain.
Fundamental is my masterpiece \& I think
God wants me to give away, it is fantastic but I cannot
find any use for it by giving it away
I don't care what happens as long as it's good.
Fundamental is a Stradivarius looking for Vivaldi or Paganini to play it.
It may be of use in
Mathematics, Chemistry, Physics \& Economics for Modeling data
without a known formula.
The program could be enhanced to do automatic algorithm
generation using an open source forth language engine like Paflof 
or else Java bytecode.
however it will be about 20 years before computation speeds
will make this possible.
Here is a description of what it how it works \& what it currently does.
\paragraph
\noindent
Fundamental internally uses reverse polish notation algorithm to search
a solution space for a unknown formula which fits test data supplied,
it can search for formulas for 
sequences of numbers as well as relationships between constants.
To date it was successfully able to find the following by a brute force 
solution space search for...\\\\\
A the maclaurin/taylor series for e(x).\\\\
An estimate formula for the nth prime.\\\\
Design an n bit adder using only boolean logic.\\\\
It could have found out that\\
\begin{math}
\sqrt{permeability of material*permittivity 
of material} = speed of light
\end{math}
 ( one of Maxwell's equations )\\\\
It could have found the formula for the Balmier lines in the hydrogen 
spectrum.\\\\
The Miraculous Bailey-Borwein-Plouffe Pi Algorithm
was found by a similar program.
\paragraph
\noindent
Example:\\
When set up properly you can enter a sequence like\\
5,8,11,14,17 as follows\\
fundamental -h 5 -m 5 -i 5 5 8 11 14 17\\
Setting -h to 5 sets the maximum integer in the solution space to 5.\\
Setting -m to 5 sets the stack depth or the maximum complexity of the
sum to 5 terms.\\
Setting -i to 5 tells fundamental that there are 5 terms following
which contain the sequence.\\
The output of the testrun is:\\
5 3 n[0]  *  +\\
(5 + (3 * n[0]))\\
5 -3 -n[0]  *  +\\
(5 + (-3 * -n[0]))\\
So the sequence formula is 5+(3 x n) n being an integer.\\\\
\chapter{Job offers}
\paragraph
\noindent
I am going to fulfill my destiny \& start my own tribe,
if you are interested in in joining it or hiring some of my tribe
have a look at my website.\\\\
\url{http://www.ariasoft.ie/joboffers.html}
\end{document}
